### 2015-08-17 paper.tex
first pass

\documentclass[fleqn,10pt]{wlpeerj}
\title{Article Title}

\author[1,2]{Alex H Williams}
\author[2]{Cian O'Donnell}
\author[3]{Eve Marder}
\author[2]{Terrence Sejnowski}
\author[3]{Timothy O'Leary}

\affil[1]{Stanford University}
\affil[2]{Salk Institute}
\affil[3]{Brandeis University}

\keywords{Synaptic tagging hypothesis, LTP, Transport, Morphology}

\begin{abstract}
Long lived changes in synaptic strength underlie persistent memories and in many cases require activity dependent transcription of plasticity-related genes.
A well-known problem is to understand how appropriate gene products, such as synaptic proteins and mRNAs, get trafficked to the synapses that require them in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many kinds of neuron.
Using a simple, biophysically-rooted model of microtubule transport we show that rapid delivery of plasticity-related cargo entails loss of specificity in the synapses that eventually receive it.
The model predicts that neurons must balance the biochemical parameters that control trafficking to find a compromise between the precision and speed with which long-lived connectivity patterns are formed.
Conversely, imbalances in transport parameters could lead to hypo-, or hyperconnectivity as well as loss of precision in associative memory, identifying a potential role for transport machinery in brain disorders that exhibit connectivity and plasticity phenotypes.
\end{abstract}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}

Neurons often have complex dendritic trees, reflecting the dense and structured synaptic connectivity that supports nervous system function. In order to maintain appropriate connectivity, or to alter it as a means of encoding memories, numerous enzymes and macromolecules need to be transported along dendrites to the synapses that need them. How is this logistical problem solved at the subcellular level? And how might a biologically plausible solution constrain the behavior of synaptic plasticity `rules' and learning in general?

Transport along dendrites is mediated by motor proteins (kinesins and dyneins) that walk along microtubules, carrying cargo at a rate that far exceeds passive diffusion [REFS]. The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ [REFS]. It is therefore conceivable that synaptic cargo is transported along dendrites in a relatively non-specific way, and synapses that need the cargo at any particular time trigger its release from the motor protein complexes as they pass. This idea is a variant of the well-known synaptic tagging hypothesis \citep{Frey_1997}, which proposes that synapses produce a biochemical `tag' that signals a requirement for synaptic building blocks as part of the plasticity process.

Not all aspects of synaptic plasticity require delivery of cargo from the soma. For example, some forms of long-term potentiation (LTP) depend on local protein synthesis and can function in isolated dendrites [REFS]. However, in the long run, the mRNAs and the machinery that supports such plasticity needs to be replenished. Moreover, many long-lasting forms of synaptic plasticity rely on anterograde transport of mRNAs \citep{Kandel_2001,Puthanveettil_2008} and specific mRNAs are known to be selectively transported to regions of heightened synaptic activity \citep{Steward_1998,Steward_2001,Moga_2004} or to developing synaptic contacts \citep{Lyles_2006}. The interplay between global distribution and local plasticity mechanisms therefore demands attention.

From simple assumptions about the dynamics of active dendritic transport we develop a model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies. In spite of its simplicity, the model is able to develop arbitrarily complex distributions in the concentration of molecular cargo across a dendritic tree. The simplicity of the model allows us to analyze its behavior and show how the relative strength of signals that lead to sequestration and the parameters that determine transport rate can affect the specificity of synaptic plasticity. [MORE DETAILS, rapid sequestration leads to... bottlenecks get caused by....]

\section*{Results}

\subsection*{Model description}

Transport along microtubules is mediated by kinesin and dynein motors, which mediate anterograde and retrograde transport, respectively \citep{Hirokawa_2010,Gagnon_2011}. Cargo is often simultaneously bound to both forms of motor, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Hancock_2014,Buxbaum_2014b} (Fig. 1A). The biophysical mechanisms of intracellular transport is a diverse and active area of research (CITE).

To obtain a general model that can accommodate variations in the biophysical details, we model microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006}. For each time step, the cargo moves left, right, or remains the in the same place. In the simplest model, the probabilities associated with each movement are fixed and independent across each time step (Fig. 1B, top panel). This model can capture the movements of molecular motors that make short movements before changing directions. However, other motors exhibit sustained movements (CITE). This can be captured by incorporating \textit{hysteresis} or history-dependence into the model. In this case, we assume the cargo is more likely to continue in the same direction as the previous time step (Fig. 1B, bottom panel).

While the position of individual cargoes can be highly stochastic, the net movement of a population along a neurite is predictable (Fig. 1C). Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) history-dependence. The average behavior of both of these models can be fit by a mass-action model (Fig. 1E-F).

The rate of molecular transport is locally modulated by calcium, ADP, and other biochemical signals \citep{Wang_2009,Mironov_2007}, and globally modulated by transcriptional control of motor protein expression \citep{Puthanveettil_2008}. This provides a potential mechanism for controlling the distribution of cargo over a dendritic tree using local activity signals.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\columnwidth]{00_stochastic.png}
\caption{A simple mass-action model of dendritic transport}
\end{center}
\end{figure}

\subsection*{Local control over microtubular transport can achieve almost any expression pattern}

As a first step, we model the transport of cargo along the microtubular network; we later extend this model to incorporate production, degradation, and detachment from the microtubules. The following mass-action scheme models transport in a unbranched neurite with $N$ compartments:
$$
u_1 \underset{b_1}{\overset{a_1}{\rightleftharpoons}} u_2 \underset{b_2}{\overset{a_2}{\rightleftharpoons}} u_3 \underset{b_3}{\overset{a_3}{\rightleftharpoons}}~...~\underset{b_{N-1}}{\overset{a_{N-1}}{\rightleftharpoons}}  u_N
$$
where $u_i$ is the mass of cargo in each compartment, and $a_i$ and $b_i$ respectively denote local rate constants for anterograde and retrograde transport. If the compartments have equal volumes, then $u_i$ can equivalently be thought of as the molecule's concentration. Similar mass-action schemes can be constructed to model transport in branched morphologies (Fig. 1A).

This model makes the following assumptions. First, the movement of molecules between neighboring compartments is a stochastic and memoryless process. This assumption is reasonable if the run length of molecular motors is comparable to the size of the compartments; this appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, but not necessarily all \citep{Dynes_2007} circumstances (see Discussion). Second, there are many copies of $u$ in each compartment. This allows us to approximate the mass as a continuous variable, and the dynamics of the system as deterministic. Third, the number of molecular motors and capacity of the microtubules is not saturated by the level of $u$ in any compartment. This means that the rate of transport from compartment A to compartment B linearly increases with the amount of $u$ in compartment A.

In this model, the exchange of $u$ between neighboring compartments approaches an equilibrium/steady-state ($ss$) distribution over time. This occurs precisely when:
$$
\frac{u_i}{u_{i+1}} \Bigg|_{ss} = \frac{b_i}{a_i}
$$
(see Methods). This result allows us to tune the local trafficking rates, $a_i$ and $b_i$, to produce a desired spatial distribution of molecular cargo. Let $\tilde{u}$ denote the desired steady-state level of $u$ in each compartment, we should select trafficking rate constants that satisfy:
$$
\frac{b_i}{a_i} = \frac{\tilde{u}_i}{\tilde{u}_{i+1}}
$$

For example, we can create an linear gradient by specifying $\tilde{u}_i \propto i$. This results in $b_i / a_i =  i / i+1$. Figure 1B shows simulation data confirming that this model converges to a linear gradient at steady-state. Notice that the slope of the resulting linear gradient depends on the total amount of $u$ present in the cable; the transport rule only re-distributes $u$ so that its steady-state levels are \textit{proportional} to the desired levels (Fig. 1C). If the target distribution is normalized such that $\sum_i \tilde{u}_i = 1$, then the steady-state level in each compartment is given by:
$$
u_i \Big|_{ss} = \tilde{u}_i~ u_{\text{total}}
$$
where $u_{\text{total}} = \sum_i u_i$ is the total amount of $u$ in the neuron. The above results extend directly to branched morphologies (see Methods). For any pair of connected compartments:
$$
\frac{u_p}{u_c} \Bigg|_{ss} = \frac{b}{a}
$$
where $u_p$ is the level in the ``parent" compartment (closer to soma) and $u_c$ is the level in the ``child" compartment (closer to periphery); $b$ and $a$ refer to the trafficking rate constants between this pair of compartments.

The above rules could be locally implemented by simple biochemical reaction networks. Consider the cytoplasmic calcium concentration, $[ca]_i$, as a candidate second messenger. Increases in $[ca]_i$ simultaneously arrest anterograde and retrograde microtubular transport \citep{Wang_2009}. That is, for any pair of compartments, the anterograde rate constant is determined by calcium in the parent compartment, $a = f([ca]_p)$,  and the retrograde rate constant is determined by calcium in the child compartment, $b = f([ca]_c)$, where $f$ is a function that describes how calcium alters the transport rates. This satisfies equation (4) and results in $\tilde{u}_i = 1/f([ca]_i)$:
$$
\frac{b}{a} = \frac{f([ca]_c)}{f([ca]_p)} = \frac{\tilde{u}_p}{\tilde{u}_c}
$$

To test the plausibility of this simple model in a complex morphology, we used an existing reconstruction of a CA1 pyramidal neuron \citep{Migliore_2012} that includes complex voltage-dependent conductances and synapses. Excitatory synaptic input was delivered to 120 locations within three dendritic regions (red dots, Fig. 1D), and the average membrane potential in each electrical compartment determined the target level $\tilde{u}_i$ in each compartment (Methods). This models how molecular cargo could be selectively trafficked to active synaptic sites. Figures 1E and 1F confirm that the spatial distribution of $u$ approaches the desired steady-state.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\columnwidth]{01_mass_action.png}
\caption{Delivery of cargo to active synapses in a complex dendritic tree}
\end{center}
\end{figure}

\subsection*{Convergence rate}

Biochemical processes are time-sensitive. For example, newly synthesized proteins must be delivered to synapses within \textasciitilde1 hour to support long-term potentiation in CA1 pyramidal cells \citep{Frey_1997,Frey_1998}. Thus, it is of substantial interest to examine factors that influence the speed of transport in the model. We studied the convergence rate of mass-action models (see Fig. 1); the stochastic model in figure 2 is related to this model by a simple rescaling (see Methods), so this analysis is applicable to both cases.

In equation (5), we implicitly required $\tilde{u}_i > 0$ for all $i$ in order to avoid division by zero. Intuitively, if $\tilde{u}_i = 0$ for some compartment, then the more peripheral compartments become disconnected and inaccessible to the rest of the cell. Similarly, if certain $\tilde{u}_i$ are nearly equal to zero, then transport through these compartments will act as a bottleneck for transport, and convergence to the desired distribution will be slow.

Figure 3 illustrates and analyzes this intuition in a simple three compartment model. The two compartments on the end of the cable have the same desired level, $\tilde{u}_1 = \tilde{u}_3$; the middle compartment acts as a bottleneck when $\tilde{u}_2$ is very small (Fig. 3A). This results in the mass-action model:
$$
u_1 \underset{x}{\overset{\epsilon}{\rightleftharpoons}} u_2 \underset{\epsilon}{\overset{x}{\rightleftharpoons}} u_3
$$
We assume that $u$ begins at one end of the cable, and examine the how taking $\epsilon$ to zero affects the convergence rate. Figure 2B shows that the convergence rate slows dramatically as $\epsilon$ decreases. This can be can be analyzed using basic linear systems theory; the convergence rate is given by the non-zero eigenvalue with smallest magnitude, which can be thought of as a rate-limiting step or process for the system (Methods, Supp. Fig. 1). Simulations confirmed this analysis and showed that the convergence rate diverges to infinity as $\epsilon$ approaches zero (Fig. 2C).

\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\columnwidth]{03_convergence.png}
\caption{Bottlenecks in transport}
\end{center}
\end{figure}

Similar results were obtained in the multi-compartment CA1 neuron model. The model converged to a uniform target distribution more quickly than to a ``bottleneck" target distribution, in which the middle third of the apical dendrite had low steady-state levels of cargo (Fig. 3D). Each pair of anterograde and retrograde rate constants were normalized to sum to one; thus, differences in convergence were not due to the scale of the trafficking rate constants.

In addition to this global view of convergence (Fig. 3D), we considered how the transport bottleneck affected transport to individual dendritic compartments. Consider a scenario where transported cargo produces a local chemical reaction after a critical concentration threshold is reached; for example, a recently potentiated synapse might be stabilized after enough plasticity-related factors are delivered from the soma. Figure 3E plots the transport delay, or duration of time it took for $u_i$ to reach a pre-defined threshold for each compartment. We observed qualitatively similar results for different threshold values (data not shown).

As expected, introducing a bottleneck caused much longer delays to compartments distal to that bottleneck (Fig. 3E, upper right portion of plot). Interestingly, the presence of a bottleneck actually \textit{shortened} the transport delay to proximal compartments, compared to the uniform target distribution (Fig. 3E, lower left portion of plot). This occurs because molecules that were delayed from entering the distal compartments spread throughout the proximal compartments, reaching higher levels earlier in the simulation.

One non-obvious prediction of this analysis is that transport to distal compartments should be quickened by allowing higher levels of $u$ into the proximal compartments at steady-state (Fig. 3E). This might be tested experimentally by characterizing the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\cite{Steward_1998}, see discussion). To illustrate this in the model CA1 cell, we characterized the time course of transport to the distal apical dendrite (stimulating stratum lacunosum/moleculare), proximal apical dendrite (stimulating stratum radiatum), entire apical dendrite (stimulating both layers), and entire cell (seizure). Interestingly, the model converged more slowly to distal input alone, than to paired distal and proximal input, or to an entirely uniform distribution (Fig. 3F).

\subsection*{Microtubular trafficking, detachment and degradation on separated time scales}

The models above present a simple hypothesis for controlling molecular transport along an intricate system of microtubules. While certain types of molecular cargo stay on the microtubule network (e.g. mitocondria), others detach from the microtubules after a reaching a desired location. For example, dendritic mRNAs are transported within densely-packed granules, and can be locally released following granule disassembly \citep{Krichevsky_2001,Buxbaum_2014a}. We model the detachment from the microtubule network as an irreversible process, and include a compartment-specific degradation reaction. This results in the following mass-action model:
$$
\begin{array}{cccccccc}
u_1 & \overset{a_1}{\underset{b_1}{\rightleftharpoons}} &
u_2 & \overset{a_2}{\underset{b_2}{\rightleftharpoons}} &
u_3 & \overset{a_3}{\underset{b_3}{\rightleftharpoons}} &
u_4 & \overset{a_4}{\underset{b_4}{\rightleftharpoons}} ...
\\
c_1 \Bigg\downarrow \phantom{c_1} & &
c_2 \Bigg\downarrow \phantom{c_2} & &
c_3 \Bigg\downarrow \phantom{c_3} & &
c_4 \Bigg\downarrow \phantom{c_4} & 
\\
u_1^\star &  &
u_2^\star &  &
u_3^\star &  &
u_4^\star &   ...
\\
d_1 \Bigg\downarrow \phantom{d_1} & &
d_2 \Bigg\downarrow \phantom{d_2} & &
d_3 \Bigg\downarrow \phantom{d_3} & &
d_4 \Bigg\downarrow \phantom{d_4} & 
\\
\varnothing &  &
\varnothing &  &
\varnothing &  &
\varnothing &  
\end{array}
$$
As before, a molecule $u$ is transported along a network of microtubules (top row, in equation 6). In each compartment, molecules can irreversibly detach from the microtubules in a reaction $u_i \xrightarrow{c_i} u_i^\star$, where $u^\star$ denotes the biochemically active form of $u$, which is assumed to be inactive during transport. The final reaction, $u_i^\star \xrightarrow{d_i} \varnothing$, models degradation in each compartment. Note that only $u^\star$ is subject to degradation; the molecule is assumed to be protected from degradation during transport. This model can be extended to branched morphologies (Fig. 3A).

One way to analyze this system is to assume that these three processes --- trafficking, detachment, and degradation --- occur on separate timescales. If trafficking is sufficiently faster than detachment ($a,b \gg c$), then $u$ approaches a quasi-steady state distribution defined by our previous analysis (equation 5). We then choose detachment rate constants that transform the microtubular distribution into our desired distribution for $u^\star$:
$$
c_i \propto \frac{\tilde{u}^\star_i}{\tilde{u}_i}
$$
Here, $\tilde{u}$ and $\tilde{u}^\star$ respectively denote the quasi-steady state distributions for $u$ and $u^\star$, respectively. Due to the degradation reaction, the system no longer approaches a steady-state; however, as long as degradation is sufficiently slow ($c \gg d$) the desired distribution is transiently achieved.

This model admits multiple strategies for controlling the distribution of molecular cargo (Fig. 4B). One strategy (Fig. 4C) is to choose microtubular trafficking rates such that $\tilde{u}$ exactly matches $\tilde{u}^\star$; detachment from the microtubules is unbiased ($c_i =$ constant). Figure 3C shows that the desired spatial distribution is achieved both along the microtubules (red line) and for the detached/activated cargo (blue line).

A second strategy (Fig. 4D) begins by uniformly distributing cargo along the microtubules, and locally detaches cargo at a rate proportional to the desired level ($c_i \propto \tilde{u}^\star_i$). Unlike the first solution, this strategy avoids the transport bottlenecks examined in Figure 3, and can achieve target patterns with  $\tilde{u}^\star$ equal to zero in certain compartments by setting $c_i = 0$.

We can also interpolate between these two strategies to achieve the target distribution. Let $F$ be a scalar between 0 and 1, and let $\tilde{u}^\star$ be normalized to sum to one. We choose $a_i$ and $b_i$ to achieve:
$$
\tilde{u}_i = F~\tilde{u}_i^\star + (1-F)/N 
$$
along the microtubular network and choose $c_i$ to satisfy
$$
c_i \propto \frac{\tilde{u}_i^\star}{F~\tilde{u}_i^\star + (1-F)/N} 
$$
Here, $N$ is the number of compartments in the model. Setting $F=1$ results in the simulation in figure 4C, while setting $F=0$ results in the simulation in figure 4D. Setting $F=0.3$ results in the simulation shown in figure 4E, which uses an interpolated strategy. Thus, effective trafficking systems can be achieved by a spectrum of strategies, which may be suited to different situations and purposes (see Discussion).

\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\columnwidth]{Fig3.png}
\caption{Multiple strategies for transport in a model including nonuniform microtubular detachment/activation}
\end{center}
\end{figure}

\subsection*{Non-local interactions can occur when time scales aren't separated}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\columnwidth]{05_heterosynaptic.png}
\caption{Heterosynaptic and non-local interactions.
}
\end{center}
\end{figure}

\subsection*{Tradeoff between speed of consolidation and specificity of potentiation}

We sought to understand the general relationship

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\columnwidth]{tradeoff.png}
\caption{Tradeoff between speed of consolidation and specificity of potentiation.
}
\end{center}
\end{figure}

\section*{Discussion}

A microscope image of a typical neuronal dendritic tree hints at the complex logistical task that the neuron must solve to maintain synapses and alter them, as appropriate, during development and learning. Synapses, such as the extensively-studied excitatory synapses of the mammalian nervous system, comprise hundreds of different proteins, including receptors, structural and anchoring proteins, and cytosolic signalling enzymes [REFs]. How do these components find their way to the synapse, and how do synapses that have varying demands for these components receive an appropriate supply?

Local protein synthesis near synaptic sites offers an elegant solution to this problem. Many mRNAs for synaptic proteins are distributed in dendrites, along with ribosomes and translational regulation machinery that can provide new proteins as they are needed [REFs]. However, these components need to be appropriately distributed to begin with and on a long timescale their distribution needs to be maintained. On the other hand, some forms of long-term synaptic plasticity have a transcription-dependent component, suggesting that somatic biosynthesis and dendritic trafficking are important for maintaining and controlling synaptic connectivity in addition to local mechanisms.

We examined simple models of microtubular transport to investigate how such a global network can be organized and controlled in complex neuronal morphologies. Previous models of microtubular-based transport have examined systems with spatially uniform rates of anterograde and retrograde transport \citep{Smith_2001,Bressloff_2006}. We hypothesized that complex spatial patterns could emerge by relaxing this assumption. One might na\"ively expect that elaborately branched morphologies obfuscate the relationship between these local mechanisms and the global distribution of molecular cargo. We showed that the relationship is actually quite simple: the steady-state ratio between neighboring compartments is the reciprocal ratio of the trafficking rate constants connecting those compartments.

Local activity signals provide a means to sequester dendritic cargo as it passes a synapse, providing a way for plasticity-inducing synaptic stimulation to `tag' a synapse. Direct evidence of activity-dependent arrest [REF Elife] and accumulation \citep{Krichevsky_2001,Buxbaum_2014a} of mRNAs and other actively transported biomolecules suggests that the kind of mechanism we studied here is involved in regulating synapses in parallel with local synthesis mechanisms. We are agnostic about the precise identity of the activity signal that controls transport and sequestration, but note that experiments have shown that local calcium \citep{Wang_2009} and ADP \citep{Mironov_2007}, alter anterograde and retrograde transport rates. Similarly, experimental data indicate that degradation of mRNA can be spatially heterogeneous and activity-dependent \citep{Farris_2014}. Incorporating these additional processes into the model created new possibilities for molecular trafficking; the same expression pattern can be achieved by nonuniform microtubular transport followed by uniform release or from uniform transport followed by nonuniform release (Fig. 4).

There is experimental evidence for both strategies. \cite{Kim_2015} identified three mRNAs that were uniformly distributed throughout cultured \textit{Aplysia} sensory neurons, but were targeted to synapses at the level of protein expression by localized translation. In contrast, the nonuniform expression of \textit{Arc} mRNA is closely matched to the pattern of Arc protein \citep{Farris_2014, Steward_2015}.

Each of these transport strategies might be tailored for different constraints or purposes. For example, a uniform mRNA profile could facilitate shifts in the protein expression pattern, since the changing the pattern of local translation is presumably faster than re-distributing the mRNA. In other cases, it might be undesirable to rapidly shift protein expression based on transient changes to the neuron or circuit; controlling expression at the level of mRNA might prevent this. We showed that it is possible to interpolate between these two strategies (Fig. 4E), which might allow neurons to trade off between the relative advantages of each.

FRX - in this disease there is aberrantly high translation of mRNAs. This is like a high sequestration rate. Leads to higher connectivity but perhaps lower specificity.

\section*{Acknowledgements}

\bibliography{transport_refs}

\end{document}

### 2015-08-18 paper.tex
add title

@@
 \documentclass[fleqn,10pt]{wlpeerj}
-\title{Article Title}
+\title{Trafficking synaptic materials in complex morphologies involves tradeoffs in speed and precision}
 
@@
 3E).
-This might be tested experimentally by characterizing the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\cite{Steward_1998}, see discussion).
+This might be tested experimentally by characterizing the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\citet{Steward_1998}, see discussion).
 To illustrate this in the model CA1 cell, we characterized the time course of transport to the distal apical dendrite (stimulating stratum lacunosum/moleculare), proximal apical dendrite (stimulating stratum radiatum), entire apical dendrite (stimulating both layers), and entire cell (seizure).

### 2015-08-18 code/01_steady_state/x86_64/distr.c
restructure

@@ -1,0 +1,274 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define vmax _p[0]
+#define v _p[1]
+#define _g _p[2]
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ /* declaration of user functions */
+ static int _mechtype;
+extern void _nrn_cacheloop_reg(int, int);
+extern void hoc_register_prop_size(int, int, int);
+extern void hoc_register_limits(int, HocParmLimits*);
+extern void hoc_register_units(int, HocParmUnits*);
+extern void nrn_promote(Prop*, int, int);
+extern Memb_func* memb_func;
+ extern void _nrn_setdata_reg(int, void(*)(Prop*));
+ static void _setdata(Prop* _prop) {
[…]

### 2015-08-18 code/01_steady_state/x86_64/h.c

@@ -1,0 +1,552 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define ghdbar _p[0]
+#define vhalfl _p[1]
+#define clk _p[2]
+#define elk _p[3]
+#define i _p[4]
+#define lk _p[5]
+#define glk _p[6]
+#define l _p[7]
+#define Dl _p[8]
+#define ghd _p[9]
+#define v _p[10]
+#define _g _p[11]
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpt(void);
+ static void _hoc_alpl(void);
+ static void _hoc_bett(void);
+ static void _hoc_rate(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/01_steady_state/x86_64/kadist.c

@@ -1,0 +1,635 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkabar _p[0]
+#define gka _p[1]
+#define n _p[2]
+#define l _p[3]
+#define ek _p[4]
+#define Dn _p[5]
+#define Dl _p[6]
+#define ik _p[7]
+#define v _p[8]
+#define _g _p[9]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpl(void);
+ static void _hoc_alpn(void);
+ static void _hoc_betl(void);
[…]

### 2015-08-18 code/01_steady_state/x86_64/km.c

@@ -1,0 +1,541 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gbar _p[0]
+#define ik _p[1]
+#define m _p[2]
+#define ek _p[3]
+#define Dm _p[4]
+#define taua _p[5]
+#define taub _p[6]
+#define v _p[7]
+#define _g _p[8]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpt(void);
+ static void _hoc_bett(void);
+ static void _hoc_rate(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/01_steady_state/x86_64/naxn.c

@@ -1,0 +1,581 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define sh _p[0]
+#define gbar _p[1]
+#define m _p[2]
+#define h _p[3]
+#define ena _p[4]
+#define ina _p[5]
+#define thegna _p[6]
+#define Dm _p[7]
+#define Dh _p[8]
+#define v _p[9]
+#define _g _p[10]
+#define _ion_ena	*_ppvar[0]._pval
+#define _ion_ina	*_ppvar[1]._pval
+#define _ion_dinadv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_trap0(void);
+ static void _hoc_trates(void);
[…]

### 2015-08-18 code/02_stochastic/x86_64/h.c

@@ -1,0 +1,552 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define ghdbar _p[0]
+#define vhalfl _p[1]
+#define clk _p[2]
+#define elk _p[3]
+#define i _p[4]
+#define lk _p[5]
+#define glk _p[6]
+#define l _p[7]
+#define Dl _p[8]
+#define ghd _p[9]
+#define v _p[10]
+#define _g _p[11]
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpt(void);
+ static void _hoc_alpl(void);
+ static void _hoc_bett(void);
+ static void _hoc_rate(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/02_stochastic/x86_64/kadist.c

@@ -1,0 +1,635 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkabar _p[0]
+#define gka _p[1]
+#define n _p[2]
+#define l _p[3]
+#define ek _p[4]
+#define Dn _p[5]
+#define Dl _p[6]
+#define ik _p[7]
+#define v _p[8]
+#define _g _p[9]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpl(void);
+ static void _hoc_alpn(void);
+ static void _hoc_betl(void);
[…]

### 2015-08-18 code/02_stochastic/x86_64/kaprox.c

@@ -1,0 +1,635 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkabar _p[0]
+#define gka _p[1]
+#define n _p[2]
+#define l _p[3]
+#define ek _p[4]
+#define Dn _p[5]
+#define Dl _p[6]
+#define ik _p[7]
+#define v _p[8]
+#define _g _p[9]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpl(void);
+ static void _hoc_alpn(void);
+ static void _hoc_betl(void);
[…]

### 2015-08-18 code/02_stochastic/x86_64/kdrca1.c

@@ -1,0 +1,534 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkdrbar _p[0]
+#define gkdr _p[1]
+#define n _p[2]
+#define ek _p[3]
+#define Dn _p[4]
+#define ik _p[5]
+#define v _p[6]
+#define _g _p[7]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpn(void);
+ static void _hoc_betn(void);
+ static void _hoc_rates(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/02_stochastic/x86_64/km.c

@@ -1,0 +1,541 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gbar _p[0]
+#define ik _p[1]
+#define m _p[2]
+#define ek _p[3]
+#define Dm _p[4]
+#define taua _p[5]
+#define taub _p[6]
+#define v _p[7]
+#define _g _p[8]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpt(void);
+ static void _hoc_bett(void);
+ static void _hoc_rate(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/02_stochastic/x86_64/na3n.c

@@ -1,0 +1,714 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define sh _p[0]
+#define gbar _p[1]
+#define ar _p[2]
+#define m _p[3]
+#define h _p[4]
+#define s _p[5]
+#define ena _p[6]
+#define ina _p[7]
+#define thegna _p[8]
+#define Dm _p[9]
+#define Dh _p[10]
+#define Ds _p[11]
+#define v _p[12]
+#define _g _p[13]
+#define _ion_ena	*_ppvar[0]._pval
+#define _ion_ina	*_ppvar[1]._pval
+#define _ion_dinadv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
[…]

### 2015-08-18 code/02_stochastic/x86_64/naxn.c

@@ -1,0 +1,581 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define sh _p[0]
+#define gbar _p[1]
+#define m _p[2]
+#define h _p[3]
+#define ena _p[4]
+#define ina _p[5]
+#define thegna _p[6]
+#define Dm _p[7]
+#define Dh _p[8]
+#define v _p[9]
+#define _g _p[10]
+#define _ion_ena	*_ppvar[0]._pval
+#define _ion_ina	*_ppvar[1]._pval
+#define _ion_dinadv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_trap0(void);
+ static void _hoc_trates(void);
[…]

### 2015-08-18 code/02_stochastic/x86_64/vecevent.c

@@ -1,0 +1,319 @@
+/* Created by Language version: 6.2.0 */
+/* NOT VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ /**/
+#define _threadargs_ /**/
+ 
+#define _threadargsprotocomma_ /**/
+#define _threadargsproto_ /**/
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ static double *_p; static Datum *_ppvar;
+ 
+#define t nrn_threads->_t
+#define dt nrn_threads->_dt
+#define index _p[0]
+#define etime _p[1]
+#define space _p[2]
+#define _tsav _p[3]
+#define _nd_area  *_ppvar[0]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ /* external NEURON variables */
+ /* declaration of user functions */
+ static double _hoc_element();
+ static double _hoc_play();
+ static int _mechtype;
+extern void _nrn_cacheloop_reg(int, int);
+extern void hoc_register_prop_size(int, int, int);
+extern void hoc_register_limits(int, HocParmLimits*);
+extern void hoc_register_units(int, HocParmUnits*);
+extern void nrn_promote(Prop*, int, int);
+extern Memb_func* memb_func;
+ extern Prop* nrn_point_prop_;
+ static int _pointtype;
+ static void* _hoc_create_pnt(_ho) Object* _ho; { void* create_point_process();
+ return create_point_process(_pointtype, _ho);
+}
+ static void _hoc_destroy_pnt();
[…]

### 2015-08-18 code/03_convergence/x86_64/h.c

@@ -1,0 +1,552 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define ghdbar _p[0]
+#define vhalfl _p[1]
+#define clk _p[2]
+#define elk _p[3]
+#define i _p[4]
+#define lk _p[5]
+#define glk _p[6]
+#define l _p[7]
+#define Dl _p[8]
+#define ghd _p[9]
+#define v _p[10]
+#define _g _p[11]
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpt(void);
+ static void _hoc_alpl(void);
+ static void _hoc_bett(void);
+ static void _hoc_rate(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/03_convergence/x86_64/kadist.c

@@ -1,0 +1,635 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkabar _p[0]
+#define gka _p[1]
+#define n _p[2]
+#define l _p[3]
+#define ek _p[4]
+#define Dn _p[5]
+#define Dl _p[6]
+#define ik _p[7]
+#define v _p[8]
+#define _g _p[9]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpl(void);
+ static void _hoc_alpn(void);
+ static void _hoc_betl(void);
[…]

### 2015-08-18 code/03_convergence/x86_64/kdrca1.c

@@ -1,0 +1,534 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkdrbar _p[0]
+#define gkdr _p[1]
+#define n _p[2]
+#define ek _p[3]
+#define Dn _p[4]
+#define ik _p[5]
+#define v _p[6]
+#define _g _p[7]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpn(void);
+ static void _hoc_betn(void);
+ static void _hoc_rates(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/03_convergence/x86_64/vecevent.c

@@ -1,0 +1,319 @@
+/* Created by Language version: 6.2.0 */
+/* NOT VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ /**/
+#define _threadargs_ /**/
+ 
+#define _threadargsprotocomma_ /**/
+#define _threadargsproto_ /**/
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ static double *_p; static Datum *_ppvar;
+ 
+#define t nrn_threads->_t
+#define dt nrn_threads->_dt
+#define index _p[0]
+#define etime _p[1]
+#define space _p[2]
+#define _tsav _p[3]
+#define _nd_area  *_ppvar[0]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ /* external NEURON variables */
+ /* declaration of user functions */
+ static double _hoc_element();
+ static double _hoc_play();
+ static int _mechtype;
+extern void _nrn_cacheloop_reg(int, int);
+extern void hoc_register_prop_size(int, int, int);
+extern void hoc_register_limits(int, HocParmLimits*);
+extern void hoc_register_units(int, HocParmUnits*);
+extern void nrn_promote(Prop*, int, int);
+extern Memb_func* memb_func;
+ extern Prop* nrn_point_prop_;
+ static int _pointtype;
+ static void* _hoc_create_pnt(_ho) Object* _ho; { void* create_point_process();
+ return create_point_process(_pointtype, _ho);
+}
+ static void _hoc_destroy_pnt();
[…]

### 2015-08-18 code/04_sushi_belt/x86_64/mod_func.c
add more code

@@ -1,0 +1,37 @@
+#include <stdio.h>
+#include "hocdec.h"
+extern int nrnmpi_myid;
+extern int nrn_nobanner_;
+
+extern void _h_reg(void);
+extern void _kadist_reg(void);
+extern void _kaprox_reg(void);
+extern void _kdrca1_reg(void);
+extern void _km_reg(void);
+extern void _na3n_reg(void);
+extern void _naxn_reg(void);
+extern void _vecevent_reg(void);
+
+void modl_reg(){
+  if (!nrn_nobanner_) if (nrnmpi_myid < 1) {
+    fprintf(stderr, "Additional mechanisms from files\n");
+
+    fprintf(stderr," h.mod");
+    fprintf(stderr," kadist.mod");
+    fprintf(stderr," kaprox.mod");
+    fprintf(stderr," kdrca1.mod");
+    fprintf(stderr," km.mod");
+    fprintf(stderr," na3n.mod");
+    fprintf(stderr," naxn.mod");
+    fprintf(stderr," vecevent.mod");
+    fprintf(stderr, "\n");
+  }
+  _h_reg();
+  _kadist_reg();
+  _kaprox_reg();
+  _kdrca1_reg();
+  _km_reg();
+  _na3n_reg();
+  _naxn_reg();
+  _vecevent_reg();
+}

### 2015-08-18 code/05_magee/x86_64/kaprox.c

@@ -1,0 +1,635 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkabar _p[0]
+#define gka _p[1]
+#define n _p[2]
+#define l _p[3]
+#define ek _p[4]
+#define Dn _p[5]
+#define Dl _p[6]
+#define ik _p[7]
+#define v _p[8]
+#define _g _p[9]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpl(void);
+ static void _hoc_alpn(void);
+ static void _hoc_betl(void);
[…]

### 2015-08-18 code/05_magee/x86_64/km.c

@@ -1,0 +1,541 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gbar _p[0]
+#define ik _p[1]
+#define m _p[2]
+#define ek _p[3]
+#define Dm _p[4]
+#define taua _p[5]
+#define taub _p[6]
+#define v _p[7]
+#define _g _p[8]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpt(void);
+ static void _hoc_bett(void);
+ static void _hoc_rate(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/05_magee/x86_64/na3n.c

@@ -1,0 +1,714 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define sh _p[0]
+#define gbar _p[1]
+#define ar _p[2]
+#define m _p[3]
+#define h _p[4]
+#define s _p[5]
+#define ena _p[6]
+#define ina _p[7]
+#define thegna _p[8]
+#define Dm _p[9]
+#define Dh _p[10]
+#define Ds _p[11]
+#define v _p[12]
+#define _g _p[13]
+#define _ion_ena	*_ppvar[0]._pval
+#define _ion_ina	*_ppvar[1]._pval
+#define _ion_dinadv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
[…]

### 2015-08-18 code/05_magee/x86_64/naxn.c

@@ -1,0 +1,581 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define sh _p[0]
+#define gbar _p[1]
+#define m _p[2]
+#define h _p[3]
+#define ena _p[4]
+#define ina _p[5]
+#define thegna _p[6]
+#define Dm _p[7]
+#define Dh _p[8]
+#define v _p[9]
+#define _g _p[10]
+#define _ion_ena	*_ppvar[0]._pval
+#define _ion_ina	*_ppvar[1]._pval
+#define _ion_dinadv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_trap0(void);
+ static void _hoc_trates(void);
[…]

### 2015-08-18 code/06_global_heterosynaptic/x86_64/h.c

@@ -1,0 +1,552 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define ghdbar _p[0]
+#define vhalfl _p[1]
+#define clk _p[2]
+#define elk _p[3]
+#define i _p[4]
+#define lk _p[5]
+#define glk _p[6]
+#define l _p[7]
+#define Dl _p[8]
+#define ghd _p[9]
+#define v _p[10]
+#define _g _p[11]
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpt(void);
+ static void _hoc_alpl(void);
+ static void _hoc_bett(void);
+ static void _hoc_rate(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/06_global_heterosynaptic/x86_64/kadist.c

@@ -1,0 +1,635 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkabar _p[0]
+#define gka _p[1]
+#define n _p[2]
+#define l _p[3]
+#define ek _p[4]
+#define Dn _p[5]
+#define Dl _p[6]
+#define ik _p[7]
+#define v _p[8]
+#define _g _p[9]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpl(void);
+ static void _hoc_alpn(void);
+ static void _hoc_betl(void);
[…]

### 2015-08-18 code/06_global_heterosynaptic/x86_64/kdrca1.c

@@ -1,0 +1,534 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkdrbar _p[0]
+#define gkdr _p[1]
+#define n _p[2]
+#define ek _p[3]
+#define Dn _p[4]
+#define ik _p[5]
+#define v _p[6]
+#define _g _p[7]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpn(void);
+ static void _hoc_betn(void);
+ static void _hoc_rates(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/06_global_heterosynaptic/x86_64/km.c

@@ -1,0 +1,541 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gbar _p[0]
+#define ik _p[1]
+#define m _p[2]
+#define ek _p[3]
+#define Dm _p[4]
+#define taua _p[5]
+#define taub _p[6]
+#define v _p[7]
+#define _g _p[8]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpt(void);
+ static void _hoc_bett(void);
+ static void _hoc_rate(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/06_global_heterosynaptic/x86_64/na3n.c

@@ -1,0 +1,714 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define sh _p[0]
+#define gbar _p[1]
+#define ar _p[2]
+#define m _p[3]
+#define h _p[4]
+#define s _p[5]
+#define ena _p[6]
+#define ina _p[7]
+#define thegna _p[8]
+#define Dm _p[9]
+#define Dh _p[10]
+#define Ds _p[11]
+#define v _p[12]
+#define _g _p[13]
+#define _ion_ena	*_ppvar[0]._pval
+#define _ion_ina	*_ppvar[1]._pval
+#define _ion_dinadv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
[…]

### 2015-08-18 latex/paper.tex
more restructuring, add readme

--- 2015-08-18 paper.tex
@@
 u_3^\star &  &
-u_4^\star &   ...
+u_4^\star &   
 \\
@@
 
-This model admits multiple strategies for controlling the distribution of molecular cargo (Fig.
+This model admits a spectrum of strategies for controlling the distribution of molecular cargo (Fig.
 4B).
@@
 
-A second strategy (Fig.
-4D) begins by uniformly distributing cargo along the microtubules, and locally detaches cargo at a rate proportional to the desired level ($c_i \propto \tilde{u}^\star_i$).
+Figure 4D shows the strategy on the other end of the spectrum.
+It begins by uniformly distributing cargo along the microtubules, and locally detaches cargo at a rate proportional to the desired level ($c_i \propto \tilde{u}^\star_i$).
 Unlike the first solution, this strategy avoids the transport bottlenecks examined in Figure 3, and can achieve target patterns with  $\tilde{u}^\star$ equal to zero in certain compartments by setting $c_i = 0$.
 
-We can also interpolate between these two strategies to achieve the target distribution.
-Let $F$ be a scalar between 0 and 1, and let $\tilde{u}^\star$ be normalized to sum to one.
-We choose $a_i$ and $b_i$ to achieve:
-$$
-\tilde{u}_i = F~\tilde{u}_i^\star + (1-F)/N 
-$$
-along the microtubular network and choose $c_i$ to satisfy
-$$
-c_i \propto \frac{\tilde{u}_i^\star}{F~\tilde{u}_i^\star + (1-F)/N} 
-$$
-Here, $N$ is the number of compartments in the model.
-Setting $F=1$ results in the simulation in figure 4C, while setting $F=0$ results in the simulation in figure 4D.
-Setting $F=0.3$ results in the simulation shown in figure 4E, which uses an interpolated strategy.
+Figure 4E shows the behavior of an intermediate model, whose parameters are a linearly interpolation between the extreme strategies shown in Figure 4C and 4D.
 Thus, effective trafficking systems can be achieved by a spectrum of strategies, which may be suited to different situations and purposes (see Discussion).
@@
 
+\section*{Methods}
+
+\subsection*{Spectrum of Trafficking Strategies}
+
+We can also interpolate between these two strategies to achieve the target distribution.
+Let $F$ be a scalar between 0 and 1, and let $\tilde{u}^\star$ be normalized to sum to one.
+We choose $a_i$ and $b_i$ to achieve:
+$$
+\tilde{u}_i = F~\tilde{u}_i^\star + (1-F)/N 
+$$
+along the microtubular network and choose $c_i$ to satisfy
+$$
+c_i \propto \frac{\tilde{u}_i^\star}{F~\tilde{u}_i^\star + (1-F)/N} 
+$$
+Here, $N$ is the number of compartments in the model.
+Setting $F=1$ results in the simulation in figure 4C, while setting $F=0$ results in the simulation in figure 4D.
+Setting $F=0.3$ results in the simulation shown in figure 4E, which uses an interpolated strategy.
+
 \section*{Acknowledgements}

### 2015-08-18 code/Figure5/x86_64/kaprox.c

@@ -1,0 +1,635 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkabar _p[0]
+#define gka _p[1]
+#define n _p[2]
+#define l _p[3]
+#define ek _p[4]
+#define Dn _p[5]
+#define Dl _p[6]
+#define ik _p[7]
+#define v _p[8]
+#define _g _p[9]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpl(void);
+ static void _hoc_alpn(void);
+ static void _hoc_betl(void);
[…]

### 2015-08-18 code/Figure5/x86_64/kdrca1.c

@@ -1,0 +1,534 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkdrbar _p[0]
+#define gkdr _p[1]
+#define n _p[2]
+#define ek _p[3]
+#define Dn _p[4]
+#define ik _p[5]
+#define v _p[6]
+#define _g _p[7]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpn(void);
+ static void _hoc_betn(void);
+ static void _hoc_rates(void);
+ static int _mechtype;
[…]

### 2015-08-18 code/Figure5/x86_64/na3n.c

@@ -1,0 +1,714 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define sh _p[0]
+#define gbar _p[1]
+#define ar _p[2]
+#define m _p[3]
+#define h _p[4]
+#define s _p[5]
+#define ena _p[6]
+#define ina _p[7]
+#define thegna _p[8]
+#define Dm _p[9]
+#define Dh _p[10]
+#define Ds _p[11]
+#define v _p[12]
+#define _g _p[13]
+#define _ion_ena	*_ppvar[0]._pval
+#define _ion_ina	*_ppvar[1]._pval
+#define _ion_dinadv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
[…]

### 2015-08-18 code/Figure5/x86_64/vecevent.c

@@ -1,0 +1,319 @@
+/* Created by Language version: 6.2.0 */
+/* NOT VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ /**/
+#define _threadargs_ /**/
+ 
+#define _threadargsprotocomma_ /**/
+#define _threadargsproto_ /**/
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ static double *_p; static Datum *_ppvar;
+ 
+#define t nrn_threads->_t
+#define dt nrn_threads->_dt
+#define index _p[0]
+#define etime _p[1]
+#define space _p[2]
+#define _tsav _p[3]
+#define _nd_area  *_ppvar[0]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ /* external NEURON variables */
+ /* declaration of user functions */
+ static double _hoc_element();
+ static double _hoc_play();
+ static int _mechtype;
+extern void _nrn_cacheloop_reg(int, int);
+extern void hoc_register_prop_size(int, int, int);
+extern void hoc_register_limits(int, HocParmLimits*);
+extern void hoc_register_units(int, HocParmUnits*);
+extern void nrn_promote(Prop*, int, int);
+extern Memb_func* memb_func;
+ extern Prop* nrn_point_prop_;
+ static int _pointtype;
+ static void* _hoc_create_pnt(_ho) Object* _ho; { void* create_point_process();
+ return create_point_process(_pointtype, _ho);
+}
+ static void _hoc_destroy_pnt();
[…]

### 2015-08-18 code/heterosynaptic_plasticity/x86_64/kaprox.c

@@ -1,0 +1,635 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define gkabar _p[0]
+#define gka _p[1]
+#define n _p[2]
+#define l _p[3]
+#define ek _p[4]
+#define Dn _p[5]
+#define Dl _p[6]
+#define ik _p[7]
+#define v _p[8]
+#define _g _p[9]
+#define _ion_ek	*_ppvar[0]._pval
+#define _ion_ik	*_ppvar[1]._pval
+#define _ion_dikdv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_alpl(void);
+ static void _hoc_alpn(void);
+ static void _hoc_betl(void);
[…]

### 2015-08-18 code/heterosynaptic_plasticity/x86_64/naxn.c

@@ -1,0 +1,581 @@
+/* Created by Language version: 6.2.0 */
+/* VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ _p, _ppvar, _thread, _nt,
+#define _threadargs_ _p, _ppvar, _thread, _nt
+ 
+#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
+#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ /* Thread safe. No static _p or _ppvar. */
+ 
+#define t _nt->_t
+#define dt _nt->_dt
+#define sh _p[0]
+#define gbar _p[1]
+#define m _p[2]
+#define h _p[3]
+#define ena _p[4]
+#define ina _p[5]
+#define thegna _p[6]
+#define Dm _p[7]
+#define Dh _p[8]
+#define v _p[9]
+#define _g _p[10]
+#define _ion_ena	*_ppvar[0]._pval
+#define _ion_ina	*_ppvar[1]._pval
+#define _ion_dinadv	*_ppvar[2]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ static Datum* _extcall_thread;
+ static Prop* _extcall_prop;
+ /* external NEURON variables */
+ extern double celsius;
+ /* declaration of user functions */
+ static void _hoc_trap0(void);
+ static void _hoc_trates(void);
[…]

### 2015-08-18 code/heterosynaptic_plasticity/x86_64/vecevent.c

@@ -1,0 +1,319 @@
+/* Created by Language version: 6.2.0 */
+/* NOT VECTORIZED */
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include "scoplib_ansi.h"
+#undef PI
+#define nil 0
+#include "md1redef.h"
+#include "section.h"
+#include "nrniv_mf.h"
+#include "md2redef.h"
+ 
+#if METHOD3
+extern int _method3;
+#endif
+
+#if !NRNGPU
+#undef exp
+#define exp hoc_Exp
+extern double hoc_Exp(double);
+#endif
+ 
+#define _threadargscomma_ /**/
+#define _threadargs_ /**/
+ 
+#define _threadargsprotocomma_ /**/
+#define _threadargsproto_ /**/
+ 	/*SUPPRESS 761*/
+	/*SUPPRESS 762*/
+	/*SUPPRESS 763*/
+	/*SUPPRESS 765*/
+	 extern double *getarg();
+ static double *_p; static Datum *_ppvar;
+ 
+#define t nrn_threads->_t
+#define dt nrn_threads->_dt
+#define index _p[0]
+#define etime _p[1]
+#define space _p[2]
+#define _tsav _p[3]
+#define _nd_area  *_ppvar[0]._pval
+ 
+#if MAC
+#if !defined(v)
+#define v _mlhv
+#endif
+#if !defined(h)
+#define h _mlhh
+#endif
+#endif
+ 
+#if defined(__cplusplus)
+extern "C" {
+#endif
+ static int hoc_nrnpointerindex =  -1;
+ /* external NEURON variables */
+ /* declaration of user functions */
+ static double _hoc_element();
+ static double _hoc_play();
+ static int _mechtype;
+extern void _nrn_cacheloop_reg(int, int);
+extern void hoc_register_prop_size(int, int, int);
+extern void hoc_register_limits(int, HocParmLimits*);
+extern void hoc_register_units(int, HocParmUnits*);
+extern void nrn_promote(Prop*, int, int);
+extern Memb_func* memb_func;
+ extern Prop* nrn_point_prop_;
+ static int _pointtype;
+ static void* _hoc_create_pnt(_ho) Object* _ho; { void* create_point_process();
+ return create_point_process(_pointtype, _ho);
+}
+ static void _hoc_destroy_pnt();
[…]

### 2015-08-18 latex/paper.tex
fix equation in fig 1

@@
 Transport along microtubules is mediated by kinesin and dynein motors, which mediate anterograde and retrograde transport, respectively \citep{Hirokawa_2010,Gagnon_2011}.
-Cargo is often simultaneously bound to both forms of motor, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Hancock_2014,Buxbaum_2014b} (Fig.
+Cargo is often simultaneously bound to both forms of motor protein, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Hancock_2014,Buxbaum_2014b} (Fig.
 1A).
@@
 
-To obtain a general model that can accommodate variations in the biophysical details, we model microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006}.
+To obtain a general model that can accommodate variations in the biophysical details, we consider microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006}.
 For each time step, the cargo moves left, right, or remains the in the same place.
@@
 
-While the position of individual cargoes can be highly stochastic, the net movement of a population along a neurite is predictable (Fig.
-1C).
+While the position of individual cargoes can be highly stochastic, the net movement of a population of cargoes (Fig.
+1C) is predictable.
 Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) history-dependence.
-The average behavior of both of these models can be fit by a mass-action model (Fig.
+In both cases, these simulations can be well-fit by a drift-diffusion partial differential equation, which is easier to analyze because it is deterministic and contains fewer variables (\cite{Smith_2001}; Fig.
 1E-F).
-
-The rate of molecular transport is locally modulated by calcium, ADP, and other biochemical signals \citep{Wang_2009,Mironov_2007}, and globally modulated by transcriptional control of motor protein expression \citep{Puthanveettil_2008}.
-This provides a potential mechanism for controlling the distribution of cargo over a dendritic tree using local activity signals.
 
@@
 
-\subsection*{Local control over microtubular transport can achieve almost any expression pattern}
-
-As a first step, we model the transport of cargo along the microtubular network; we later extend this model to incorporate production, degradation, and detachment from the microtubules.
-The following mass-action scheme models transport in a unbranched neurite with $N$ compartments:
-$$
+The partial differential equation in Figure 1E can be approximated by discretizing a dendritic tree into small compartments, and considering the movement of cargo between neighboring compartments as a chemical reaction with first order kinetics.
+In an unbranched cable with $N$ compartments, the mass-action model is:
+\begin{equation}
 u_1 \underset{b_1}{\overset{a_1}{\rightleftharpoons}} u_2 \underset{b_2}{\overset{a_2}{\rightleftharpoons}} u_3 \underset{b_3}{\overset{a_3}{\rightleftharpoons}}~...~\underset{b_{N-1}}{\overset{a_{N-1}}{\rightleftharpoons}}  u_N
-$$
+\end{equation}
 where $u_i$ is the mass of cargo in each compartment, and $a_i$ and $b_i$ respectively denote local rate constants for anterograde and retrograde transport.
@@
 
-This model makes the following assumptions.
-First, the movement of molecules between neighboring compartments is a stochastic and memoryless process.
-This assumption is reasonable if the run length of molecular motors is comparable to the size of the compartments; this appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, but not necessarily all \citep{Dynes_2007} circumstances (see Discussion).
-Second, there are many copies of $u$ in each compartment.
-This allows us to approximate the mass as a continuous variable, and the dynamics of the system as deterministic.
-Third, the number of molecular motors and capacity of the microtubules is not saturated by the level of $u$ in any compartment.
-This means that the rate of transport from compartment A to compartment B linearly increases with the amount of $u$ in compartment A.
+A critical assumption of this model is that the movement of molecules between neighboring compartments is a stochastic and memoryless process.
+This assumption is reasonable if the run length of molecular motors is comparable to the size of the compartments; this appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, thought not necessarily all \citep{Dynes_2007} circumstances (see Discussion).
+In simulations, we observed that this model was not very sensitive to violations of this assumption; the population dynamics of cargoes with substantial run lengths could still be well-fit by this class of models (Fig.
+1F, lower panel; Supp Fig.
+NUMBER).
+[SHOULD THIS BE MOVED TO DISCUSSION?]
 
-In this model, the exchange of $u$ between neighboring compartments approaches an equilibrium/steady-state ($ss$) distribution over time. This occurs precisely when:
+\subsection*{A simple rule achieves desired spatial distributions of cargo}
+
+The exchange of $u$ between neighboring compartments approaches an equilibrium/steady-state ($ss$) distribution over time. In an unbranched cable, this occurs precisely when:
 $$
@@
 This models how molecular cargo could be selectively trafficked to active synaptic sites.
-Figures 1E and 1F confirm that the spatial distribution of $u$ approaches the desired steady-state.
+Figures 2E and 2F confirm that the spatial distribution of $u$ approaches the desired steady-state.
 
@@
 
+; the stochastic model in figure 2 is related to this model by a simple rescaling (see Methods), so this analysis is applicable to both cases
+
 \subsection*{Convergence rate}
@@
 Thus, it is of substantial interest to examine factors that influence the speed of transport in the model.
-We studied the convergence rate of mass-action models (see Fig.
-1); the stochastic model in figure 2 is related to this model by a simple rescaling (see Methods), so this analysis is applicable to both cases.
 
@@
 
+Other assumptions of the mass-action model - Second, the model assumes are many copies of $u$ in each compartment.
+This allows us to approximate the mass as a continuous variable, and the dynamics of the system as deterministic.
+Third, the number of molecular motors and capacity of the microtubules is not saturated by the level of $u$ in any compartment.
+This means that the rate of transport from compartment A to compartment B linearly increases with the amount of $u$ in compartment A.
+
 \section*{Methods}
 
-\subsection*{Spectrum of Trafficking Strategies}
+\subsection*{Microtubule Transport Model (Fig. 1)}
+Transport in an unbranched cable (equation 1) leads to the following system of differential equations:
+$$
+\begin{array}{lcl}
+\dot{u}_1 & = & -a_1 u_1 + b_1 u_2 \\
+\dot{u}_2 & = & a_1 u_1 - (a_2+b_1) u_2 + b_2 u_3 \\
+~ & \vdots & ~ \\
+\dot{u}_i & = & a_{i-1} u_{i-1} - (a_i+b_{i-1}) u_i + b_i u_{i+1} \\
+~ & \vdots & ~ \\
+\dot{u}_N & = & a_{N-1} u_{N-1} - b_{N-1} u_N 
+\end{array}
+$$
+Similar systems result from branched mass-action models. The steady-state relationship in equation 5 can be immediately verified at either end of the cable:
+$$
+\dot{u}_1 = 0 ~\Rightarrow~ -a_{1} u_{1} + b_{1} u_2 = 0 ~\Rightarrow~ \frac{u_1}{u_2} \Bigg |_{ss} = \frac{b_1}{a_1}
+$$
+The same procedure can be iteratively applied down the cable to show that equation 5 holds globally.
+The same result can be shown in a branched tree morphology.
+Here, each compartment has exactly one parent, but can have multiple children at branch points.
+Consider a parent-child pair of compartments, $u_p$ and $u_c$, with anterograde/retrograde transport rate constants $a$ and $b$.
+At steady-state, there is no net flux between $u_c$ and its children:
+$$
+\dot{u}_c = a u_p - b u_c + \underbrace{\sum_j (b_j u_j - a_j u_c)}_{= 0 \text{ , at ss}}
+$$
+Thus, we have:
+$$
+\dot{u}_c = a u_p - b u_c = 0 ~\Rightarrow~ \frac{u_p}{u_c} \Bigg |_{ss} = \frac{b}{a}
+$$
+To study how the system converges to steady-state, we can re-express the model as a matrix differential equation, $\mathbf{\dot{u}} = A \mathbf{u}$, where $\mathbf{u} = \left[ u_1, u_2, ...
+u_N \right]^T$ is the state vector, and $A$ is a matrix.
+For a general branched morphology, the matrix $A$ will be nearly tridiagonal, with off-diagonal elements corresponding to branch points; matrices in this form are called Hines matrices \citep{Hines_1984}.
+For the simpler case of an unbranched cable, $A$ is tridiagonal:
+$$
+A = 
+ \begin{bmatrix}
+  ~-a_1~  & b_1      & 0         &         & ...              & 0        \\
+   a_1    & -b_1-a_2 & b_2       &  0      &                  &          \\
+   0      &  a_2     & -b_2-a_3  & ~~~ b_3~~~  & \ddots     & \vdots   \\
+   \vdots &  0       & a_3       & \ddots  &                  & 0        \\
+          &          & \ddots    &         & -b_{N-2}-a_{N-1} & b_{N-1}  \\
+   0      &          & ...       &  0      & a_{N-1}          & ~-b_{N-1}~
+ \end{bmatrix}
+$$
+For both branched and unbranched morphologies, each column of $A$ sums to zero, which reflects conservation of mass within the system.
+The rank of $A$ is exactly $N-1$ (this can be seen by taking the sum of the first $N-1$ rows, which results in $-1$ times the final row).
+Thus, the nullspace of $A$ is one-dimensional (red lines in Supp.
+Fig.
+1).
+
+The desired distribution, $\mathbf{\tilde{u}}$, is an eigenvector that spans the nullspace of $A$.
+All other eigenvalues $A$ are negative, which can be shown using the Gershgorin circle theorem.
+The convergence rate is determined by the non-zero eigenvalue with smallest magnitude of $A$.
+We can increase the convergence rate (while still maintaining $\mathbf{\tilde{u}}$) by multiplying all rate constants by some common value.
+However, this trivial strategy ignores the fact that there are biophysical limits on how fast molecular motors can move.
+
+\subsection*{Stochastic Model of Transport}
+
+We model the stochastic transport of a single molecule with a discrete-time Markov chain model.
+Let the vector $\mathbf{p}^{(k)} = [p_1^{(k)}, p_2^{(k)}, ..., p_N^{(k)}]^T$ denote the probability of finding the molecule in each of the $N$ compartments on the $k$th time step.
+For example, $p_1^{(0)}$ is the initial probability that the molecule is in the first compartment (which is the soma in our implementation).
+The state-transition matrix $S$ describes the probabilistic anterograde/retrograde transport of the molecule between neighboring compartments in each discrete time step:
+$$
+\mathbf{p}^{(k+1)} = S\mathbf{p}^{(k)}
+$$
+The state-transition matrix is related to the mass-action system matrix $A$ by the following relation:
+$$
+S = \Delta t A + I
+$$
+where $\Delta t$ is the length of a time step (assumed to be very small), and $I$ is the identity matrix.
+The columns of $S$ sum to one, and, since $\Delta t$ is small, all elements of $S$ lie on the interval $[0,1]$.
+This transformation shifts and scales the eigenvalues of $A$ to lie on the interval $(0,1]$, without modifying the eigenvectors of the system.
+The steady-state probability distribution is given by the eigenvector of $S$ with eigenvalue 1 (CITE), which is identical to the vector spanning the nullspace of $A$ and therefore the steady-state concentration distribution of the mass-action model.
+
+\subsection{Transport Model With Detachment and Degradation (Fig. 4)}
 

### 2015-08-18 latex/paper.tex
ignore .ipynb

@@
 Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) history-dependence.
-In both cases, these simulations can be well-fit by a drift-diffusion partial differential equation, which is easier to analyze because it is deterministic and contains fewer variables (\cite{Smith_2001}; Fig.
+In both cases, these simulations can be well-fit by an convection-diffusion partial differential equation, which is easier to analyze because it is deterministic and contains fewer variables (\cite{Smith_2001}; Fig.
 1E-F).

### 2015-08-19 code/06_global_heterosynaptic/x86_64/h.c
first plots for fig6

@@ -1,552 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define ghdbar _p[0]
-#define vhalfl _p[1]
-#define clk _p[2]
-#define elk _p[3]
-#define i _p[4]
-#define lk _p[5]
-#define glk _p[6]
-#define l _p[7]
-#define Dl _p[8]
-#define ghd _p[9]
-#define v _p[10]
-#define _g _p[11]
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpt(void);
- static void _hoc_alpl(void);
- static void _hoc_bett(void);
- static void _hoc_rate(void);
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
[…]

### 2015-08-19 code/06_global_heterosynaptic/x86_64/kadist.c

@@ -1,635 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define gkabar _p[0]
-#define gka _p[1]
-#define n _p[2]
-#define l _p[3]
-#define ek _p[4]
-#define Dn _p[5]
-#define Dl _p[6]
-#define ik _p[7]
-#define v _p[8]
-#define _g _p[9]
-#define _ion_ek	*_ppvar[0]._pval
-#define _ion_ik	*_ppvar[1]._pval
-#define _ion_dikdv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpl(void);
- static void _hoc_alpn(void);
- static void _hoc_betl(void);
- static void _hoc_betn(void);
[…]

### 2015-08-19 code/06_global_heterosynaptic/x86_64/kaprox.c

@@ -1,635 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define gkabar _p[0]
-#define gka _p[1]
-#define n _p[2]
-#define l _p[3]
-#define ek _p[4]
-#define Dn _p[5]
-#define Dl _p[6]
-#define ik _p[7]
-#define v _p[8]
-#define _g _p[9]
-#define _ion_ek	*_ppvar[0]._pval
-#define _ion_ik	*_ppvar[1]._pval
-#define _ion_dikdv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpl(void);
- static void _hoc_alpn(void);
- static void _hoc_betl(void);
- static void _hoc_betn(void);
[…]

### 2015-08-19 code/06_global_heterosynaptic/x86_64/kdrca1.c

@@ -1,534 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define gkdrbar _p[0]
-#define gkdr _p[1]
-#define n _p[2]
-#define ek _p[3]
-#define Dn _p[4]
-#define ik _p[5]
-#define v _p[6]
-#define _g _p[7]
-#define _ion_ek	*_ppvar[0]._pval
-#define _ion_ik	*_ppvar[1]._pval
-#define _ion_dikdv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpn(void);
- static void _hoc_betn(void);
- static void _hoc_rates(void);
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
[…]

### 2015-08-19 code/06_global_heterosynaptic/x86_64/km.c

@@ -1,541 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define gbar _p[0]
-#define ik _p[1]
-#define m _p[2]
-#define ek _p[3]
-#define Dm _p[4]
-#define taua _p[5]
-#define taub _p[6]
-#define v _p[7]
-#define _g _p[8]
-#define _ion_ek	*_ppvar[0]._pval
-#define _ion_ik	*_ppvar[1]._pval
-#define _ion_dikdv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpt(void);
- static void _hoc_bett(void);
- static void _hoc_rate(void);
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
[…]

### 2015-08-19 code/06_global_heterosynaptic/x86_64/na3n.c

@@ -1,714 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define sh _p[0]
-#define gbar _p[1]
-#define ar _p[2]
-#define m _p[3]
-#define h _p[4]
-#define s _p[5]
-#define ena _p[6]
-#define ina _p[7]
-#define thegna _p[8]
-#define Dm _p[9]
-#define Dh _p[10]
-#define Ds _p[11]
-#define v _p[12]
-#define _g _p[13]
-#define _ion_ena	*_ppvar[0]._pval
-#define _ion_ina	*_ppvar[1]._pval
-#define _ion_dinadv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alps(void);
- static void _hoc_alpv(void);
[…]

### 2015-08-19 code/06_global_heterosynaptic/x86_64/naxn.c

@@ -1,581 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define sh _p[0]
-#define gbar _p[1]
-#define m _p[2]
-#define h _p[3]
-#define ena _p[4]
-#define ina _p[5]
-#define thegna _p[6]
-#define Dm _p[7]
-#define Dh _p[8]
-#define v _p[9]
-#define _g _p[10]
-#define _ion_ena	*_ppvar[0]._pval
-#define _ion_ina	*_ppvar[1]._pval
-#define _ion_dinadv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_trap0(void);
- static void _hoc_trates(void);
- static int _mechtype;
[…]

### 2015-08-19 code/06_global_heterosynaptic/x86_64/vecevent.c

@@ -1,319 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* NOT VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ /**/
-#define _threadargs_ /**/
- 
-#define _threadargsprotocomma_ /**/
-#define _threadargsproto_ /**/
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- static double *_p; static Datum *_ppvar;
- 
-#define t nrn_threads->_t
-#define dt nrn_threads->_dt
-#define index _p[0]
-#define etime _p[1]
-#define space _p[2]
-#define _tsav _p[3]
-#define _nd_area  *_ppvar[0]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- /* external NEURON variables */
- /* declaration of user functions */
- static double _hoc_element();
- static double _hoc_play();
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
-extern void hoc_register_prop_size(int, int, int);
-extern void hoc_register_limits(int, HocParmLimits*);
-extern void hoc_register_units(int, HocParmUnits*);
-extern void nrn_promote(Prop*, int, int);
-extern Memb_func* memb_func;
- extern Prop* nrn_point_prop_;
- static int _pointtype;
- static void* _hoc_create_pnt(_ho) Object* _ho; { void* create_point_process();
- return create_point_process(_pointtype, _ho);
-}
- static void _hoc_destroy_pnt();
[…]

### 2015-08-19 code/Figure5/x86_64/distr.c

@@ -1,274 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define vmax _p[0]
-#define v _p[1]
-#define _g _p[2]
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- /* declaration of user functions */
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
-extern void hoc_register_prop_size(int, int, int);
-extern void hoc_register_limits(int, HocParmLimits*);
-extern void hoc_register_units(int, HocParmUnits*);
-extern void nrn_promote(Prop*, int, int);
-extern Memb_func* memb_func;
- extern void _nrn_setdata_reg(int, void(*)(Prop*));
- static void _setdata(Prop* _prop) {
- _extcall_prop = _prop;
- }
[…]

### 2015-08-19 code/Figure5/x86_64/h.c

@@ -1,552 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define ghdbar _p[0]
-#define vhalfl _p[1]
-#define clk _p[2]
-#define elk _p[3]
-#define i _p[4]
-#define lk _p[5]
-#define glk _p[6]
-#define l _p[7]
-#define Dl _p[8]
-#define ghd _p[9]
-#define v _p[10]
-#define _g _p[11]
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpt(void);
- static void _hoc_alpl(void);
- static void _hoc_bett(void);
- static void _hoc_rate(void);
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
[…]

### 2015-08-19 code/Figure5/x86_64/kadist.c

@@ -1,635 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define gkabar _p[0]
-#define gka _p[1]
-#define n _p[2]
-#define l _p[3]
-#define ek _p[4]
-#define Dn _p[5]
-#define Dl _p[6]
-#define ik _p[7]
-#define v _p[8]
-#define _g _p[9]
-#define _ion_ek	*_ppvar[0]._pval
-#define _ion_ik	*_ppvar[1]._pval
-#define _ion_dikdv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpl(void);
- static void _hoc_alpn(void);
- static void _hoc_betl(void);
- static void _hoc_betn(void);
[…]

### 2015-08-19 code/Figure5/x86_64/kaprox.c

@@ -1,635 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define gkabar _p[0]
-#define gka _p[1]
-#define n _p[2]
-#define l _p[3]
-#define ek _p[4]
-#define Dn _p[5]
-#define Dl _p[6]
-#define ik _p[7]
-#define v _p[8]
-#define _g _p[9]
-#define _ion_ek	*_ppvar[0]._pval
-#define _ion_ik	*_ppvar[1]._pval
-#define _ion_dikdv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpl(void);
- static void _hoc_alpn(void);
- static void _hoc_betl(void);
- static void _hoc_betn(void);
[…]

### 2015-08-19 code/Figure5/x86_64/kdrca1.c

@@ -1,534 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define gkdrbar _p[0]
-#define gkdr _p[1]
-#define n _p[2]
-#define ek _p[3]
-#define Dn _p[4]
-#define ik _p[5]
-#define v _p[6]
-#define _g _p[7]
-#define _ion_ek	*_ppvar[0]._pval
-#define _ion_ik	*_ppvar[1]._pval
-#define _ion_dikdv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpn(void);
- static void _hoc_betn(void);
- static void _hoc_rates(void);
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
[…]

### 2015-08-19 code/Figure5/x86_64/km.c

@@ -1,541 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define gbar _p[0]
-#define ik _p[1]
-#define m _p[2]
-#define ek _p[3]
-#define Dm _p[4]
-#define taua _p[5]
-#define taub _p[6]
-#define v _p[7]
-#define _g _p[8]
-#define _ion_ek	*_ppvar[0]._pval
-#define _ion_ik	*_ppvar[1]._pval
-#define _ion_dikdv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alpt(void);
- static void _hoc_bett(void);
- static void _hoc_rate(void);
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
[…]

### 2015-08-19 code/Figure5/x86_64/mod_func.c

@@ -1,37 +1,0 @@
-#include <stdio.h>
-#include "hocdec.h"
-extern int nrnmpi_myid;
-extern int nrn_nobanner_;
-
-extern void _h_reg(void);
-extern void _kadist_reg(void);
-extern void _kaprox_reg(void);
-extern void _kdrca1_reg(void);
-extern void _km_reg(void);
-extern void _na3n_reg(void);
-extern void _naxn_reg(void);
-extern void _vecevent_reg(void);
-
-void modl_reg(){
-  if (!nrn_nobanner_) if (nrnmpi_myid < 1) {
-    fprintf(stderr, "Additional mechanisms from files\n");
-
-    fprintf(stderr," h.mod");
-    fprintf(stderr," kadist.mod");
-    fprintf(stderr," kaprox.mod");
-    fprintf(stderr," kdrca1.mod");
-    fprintf(stderr," km.mod");
-    fprintf(stderr," na3n.mod");
-    fprintf(stderr," naxn.mod");
-    fprintf(stderr," vecevent.mod");
-    fprintf(stderr, "\n");
-  }
-  _h_reg();
-  _kadist_reg();
-  _kaprox_reg();
-  _kdrca1_reg();
-  _km_reg();
-  _na3n_reg();
-  _naxn_reg();
-  _vecevent_reg();
-}

### 2015-08-19 code/Figure5/x86_64/na3n.c

@@ -1,714 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define sh _p[0]
-#define gbar _p[1]
-#define ar _p[2]
-#define m _p[3]
-#define h _p[4]
-#define s _p[5]
-#define ena _p[6]
-#define ina _p[7]
-#define thegna _p[8]
-#define Dm _p[9]
-#define Dh _p[10]
-#define Ds _p[11]
-#define v _p[12]
-#define _g _p[13]
-#define _ion_ena	*_ppvar[0]._pval
-#define _ion_ina	*_ppvar[1]._pval
-#define _ion_dinadv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_alps(void);
- static void _hoc_alpv(void);
[…]

### 2015-08-19 code/Figure5/x86_64/naxn.c

@@ -1,581 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ _p, _ppvar, _thread, _nt,
-#define _threadargs_ _p, _ppvar, _thread, _nt
- 
-#define _threadargsprotocomma_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt,
-#define _threadargsproto_ double* _p, Datum* _ppvar, Datum* _thread, _NrnThread* _nt
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- /* Thread safe. No static _p or _ppvar. */
- 
-#define t _nt->_t
-#define dt _nt->_dt
-#define sh _p[0]
-#define gbar _p[1]
-#define m _p[2]
-#define h _p[3]
-#define ena _p[4]
-#define ina _p[5]
-#define thegna _p[6]
-#define Dm _p[7]
-#define Dh _p[8]
-#define v _p[9]
-#define _g _p[10]
-#define _ion_ena	*_ppvar[0]._pval
-#define _ion_ina	*_ppvar[1]._pval
-#define _ion_dinadv	*_ppvar[2]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- static Datum* _extcall_thread;
- static Prop* _extcall_prop;
- /* external NEURON variables */
- extern double celsius;
- /* declaration of user functions */
- static void _hoc_trap0(void);
- static void _hoc_trates(void);
- static int _mechtype;
[…]

### 2015-08-19 code/Figure5/x86_64/vecevent.c

@@ -1,319 +1,0 @@
-/* Created by Language version: 6.2.0 */
-/* NOT VECTORIZED */
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include "scoplib_ansi.h"
-#undef PI
-#define nil 0
-#include "md1redef.h"
-#include "section.h"
-#include "nrniv_mf.h"
-#include "md2redef.h"
- 
-#if METHOD3
-extern int _method3;
-#endif
-
-#if !NRNGPU
-#undef exp
-#define exp hoc_Exp
-extern double hoc_Exp(double);
-#endif
- 
-#define _threadargscomma_ /**/
-#define _threadargs_ /**/
- 
-#define _threadargsprotocomma_ /**/
-#define _threadargsproto_ /**/
- 	/*SUPPRESS 761*/
-	/*SUPPRESS 762*/
-	/*SUPPRESS 763*/
-	/*SUPPRESS 765*/
-	 extern double *getarg();
- static double *_p; static Datum *_ppvar;
- 
-#define t nrn_threads->_t
-#define dt nrn_threads->_dt
-#define index _p[0]
-#define etime _p[1]
-#define space _p[2]
-#define _tsav _p[3]
-#define _nd_area  *_ppvar[0]._pval
- 
-#if MAC
-#if !defined(v)
-#define v _mlhv
-#endif
-#if !defined(h)
-#define h _mlhh
-#endif
-#endif
- 
-#if defined(__cplusplus)
-extern "C" {
-#endif
- static int hoc_nrnpointerindex =  -1;
- /* external NEURON variables */
- /* declaration of user functions */
- static double _hoc_element();
- static double _hoc_play();
- static int _mechtype;
-extern void _nrn_cacheloop_reg(int, int);
-extern void hoc_register_prop_size(int, int, int);
-extern void hoc_register_limits(int, HocParmLimits*);
-extern void hoc_register_units(int, HocParmUnits*);
-extern void nrn_promote(Prop*, int, int);
-extern Memb_func* memb_func;
- extern Prop* nrn_point_prop_;
- static int _pointtype;
- static void* _hoc_create_pnt(_ho) Object* _ho; { void* create_point_process();
- return create_point_process(_pointtype, _ho);
-}
- static void _hoc_destroy_pnt();
[…]

### 2015-08-20 latex/paper.tex
finish final 2 figs

--- 2015-08-18 latex/paper.tex
@@
-\documentclass[fleqn,10pt]{wlpeerj}
+\documentclass[10pt]{wlpeerj}
+\usepackage{mathtools}
+
 \title{Trafficking synaptic materials in complex morphologies involves tradeoffs in speed and precision}
@@
 Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) history-dependence.
-In both cases, these simulations can be well-fit by a drift-diffusion partial differential equation, which is easier to analyze because it is deterministic and contains fewer variables (\cite{Smith_2001}; Fig.
-1E-F).
+In both cases, these simulations can be well-fit by an convection-diffusion partial differential equation (Fig.
+1E-F), which is easier to analyze because it is deterministic and contains fewer variables \citep{Smith_2001}.
 
-\begin{figure}[h!]
+\begin{figure}[!htbp]
 \begin{center}
-\includegraphics[width=1\columnwidth]{00_stochastic.png}
+\includegraphics[width=0.9\columnwidth]{00_stochastic.png}
 \caption{A simple mass-action model of dendritic transport}
@@
 \begin{equation}
-u_1 \underset{b_1}{\overset{a_1}{\rightleftharpoons}} u_2 \underset{b_2}{\overset{a_2}{\rightleftharpoons}} u_3 \underset{b_3}{\overset{a_3}{\rightleftharpoons}}~...~\underset{b_{N-1}}{\overset{a_{N-1}}{\rightleftharpoons}}  u_N
+u_1 \xrightleftharpoons[b_1]{a_1} u_2 \xrightleftharpoons[b_2]{a_2} u_3 \xrightleftharpoons[b_3]{a_3} ~...~ \xrightleftharpoons[b_{N-1}]{a_{N-1}} u_N
 \end{equation}
-where $u_i$ is the mass of cargo in each compartment, and $a_i$ and $b_i$ respectively denote local rate constants for anterograde and retrograde transport.
-If the compartments have equal volumes, then $u_i$ can equivalently be thought of as the molecule's concentration.
+where $u_i$ is the amount of cargo in each compartment, and $a_i$ and $b_i$ respectively denote local rate constants for anterograde and retrograde transport; these parameters determine the local diffusion and drift coefficients as shown in figure 1E (see Methods).
 Similar mass-action schemes can be constructed to model transport in branched morphologies (Fig.
-1A).
+2A).
 
-A critical assumption of this model is that the movement of molecules between neighboring compartments is a stochastic and memoryless process.
+A central assumption of this model is that the movement of molecules between neighboring compartments is a stochastic and memoryless process.
 This assumption is reasonable if the run length of molecular motors is comparable to the size of the compartments; this appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, thought not necessarily all \citep{Dynes_2007} circumstances (see Discussion).
@@
 (see Methods).
-This result allows us to tune the local trafficking rates, $a_i$ and $b_i$, to produce a desired spatial distribution of molecular cargo.
-Let $\tilde{u}$ denote the desired steady-state level of $u$ in each compartment, we should select trafficking rate constants that satisfy:
+Thus, the local trafficking rates, $a_i$ and $b_i$, can be tuned to produce a desired spatial distribution of cargo.
+Let $\tilde{u}$ denote the desired steady-state level of $u$ in each compartment.
+For example, $\tilde{u}_i$ might refer to the local concentration of biochemical signal that ``tags'' synapses for plasticity (CITE); such a tag might be positively correlated to the desired level of delivered cargo.
+To match this desired distribution, the ratio of local trafficking rates should satisfy:
 $$
@@
 
-For example, we can create an linear gradient by specifying $\tilde{u}_i \propto i$.
-This results in $b_i / a_i =  i / i+1$.
-Figure 1B shows simulation data confirming that this model converges to a linear gradient at steady-state.
-Notice that the slope of the resulting linear gradient depends on the total amount of $u$ present in the cable; the transport rule only re-distributes $u$ so that its steady-state levels are \textit{proportional} to the desired levels (Fig.
+For example, we can create an linear gradient by specifying $\tilde{u}_i \propto i$ (Fig.
+1B-C).
+The transport rule only determines the steady-state ratios of cargo in neighboring compartments; it cannot control the slope of the linear profile.
+Instead, the slope is controlled by tuning the total amount of cargo in the cable (Fig.
 1C).
-If the target distribution is normalized such that $\sum_i \tilde{u}_i = 1$, then the steady-state level in each compartment is given by:
-$$
-u_i \Big|_{ss} = \tilde{u}_i~ u_{\text{total}}
-$$
-where $u_{\text{total}} = \sum_i u_i$ is the total amount of $u$ in the neuron. The above results extend directly to branched morphologies (see Methods). For any pair of connected compartments:
-$$
-\frac{u_p}{u_c} \Bigg|_{ss} = \frac{b}{a}
-$$
-where $u_p$ is the level in the ``parent" compartment (closer to soma) and $u_c$ is the level in the ``child" compartment (closer to periphery); $b$ and $a$ refer to the trafficking rate constants between this pair of compartments.
+These results extend directly to branched morphologies (see Methods).
 
-The above rules could be locally implemented by simple biochemical reaction networks.
+%For any pair of connected compartments:
+%$$
+%\frac{u_p}{u_c} \Bigg|_{ss} = \frac{b}{a}
+%$$
+%where $u_p$ is the level in the ``parent" compartment (closer to soma) and $u_c$ is the level in the ``child" compartment (closer to periphery); $b$ and $a$ refer to the local transport rate constants between this pair of compartments.
+
+These rules could be locally implemented by simple biochemical reaction networks.
 Consider the cytoplasmic calcium concentration, $[ca]_i$, as a candidate second messenger.
@@
 
-To test the plausibility of this simple model in a complex morphology, we used an existing reconstruction of a CA1 pyramidal neuron \citep{Migliore_2012} that includes complex voltage-dependent conductances and synapses.
+To test the plausibility of this model in a complex morphology, we used an existing reconstruction of a CA1 pyramidal neuron \citep{Migliore_2012} that includes complex voltage-dependent conductances and synapses.
 Excitatory synaptic input was delivered to 120 locations within three dendritic regions (red dots, Fig.
@@
 
-\begin{figure}[h!]
+\begin{figure}[!htbp]
 \begin{center}
-\includegraphics[width=1\columnwidth]{01_mass_action.png}
+\includegraphics[width=0.9\columnwidth]{01_mass_action.png}
 \caption{Delivery of cargo to active synapses in a complex dendritic tree}
@@
 \end{figure}
-
-; the stochastic model in figure 2 is related to this model by a simple rescaling (see Methods), so this analysis is applicable to both cases
 
@@
 
-\begin{figure}[h!]
+\begin{figure}[!htbp]
 \begin{center}
-\includegraphics[width=1\columnwidth]{03_convergence.png}
+\includegraphics[width=0.9\columnwidth]{03_convergence.png}
 \caption{Bottlenecks in transport}
@@
 
+\begin{figure}[!htbp]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{04_sushi_belt.png}
+\caption{Multiple strategies for transport in a model including nonuniform microtubular detachment/activation}
+\end{center}
+\end{figure}
+
 One way to analyze this system is to assume that these three processes --- trafficking, detachment, and degradation --- occur on separate timescales.
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=1\columnwidth]{Fig3.png}
-\caption{Multiple strategies for transport in a model including nonuniform microtubular detachment/activation}
-\end{center}
-\end{figure}
-
 \subsection*{Non-local interactions can occur when time scales aren't separated}
 
-\begin{figure}[h!]
+\begin{figure}[!htbp]
 \begin{center}
-\includegraphics[width=0.7\columnwidth]{05_heterosynaptic.png}
+\includegraphics[width=0.9\columnwidth]{05_heterosynaptic_ca1.png}
 \caption{Heterosynaptic and non-local interactions.
@@
 
-\begin{figure}[h!]
+\begin{figure}[!htbp]
 \begin{center}
-\includegraphics[width=0.5\columnwidth]{tradeoff.png}
-\caption{Tradeoff between speed of consolidation and specificity of potentiation.
-}
+\includegraphics[width=0.9\columnwidth]{06_heterosynaptic_cable.png}
+\caption{Tradeoff between speed of consolidation and specificity of potentiation.}
 \end{center}

### 2015-08-20 latex/paper.tex
working through writing the results

@@
 \usepackage{mathtools}
+\usepackage{soul}
 
@@
 
-\author[1,2]{Alex H Williams}
+\author[1,2,3]{Alex H. Williams}
 \author[2]{Cian O'Donnell}
-\author[3]{Eve Marder}
-\author[2]{Terrence Sejnowski}
-\author[3]{Timothy O'Leary}
+\author[4]{Eve Marder}
+\author[2,5]{Terrence Sejnowski}
+\author[4]{Timothy O'Leary}
 
-\affil[1]{Stanford University}
-\affil[2]{Salk Institute}
-\affil[3]{Brandeis University}
+\affil[1]{Department of Neurosciences, University of California, San Diego, La Jolla, CA 92093, USA}
+\affil[2]{Howard Hughes Medical Institute, Salk Institute for Biological Studies, La Jolla, CA 92037, USA}
+\affil[3]{Department of Neurobiology, Stanford University, Stanford, CA 94305, USA}
+\affil[4]{Volen Center and Biology Department, Brandeis University, Waltham, MA 02454, USA}
+\affil[5]{Division of Biological Sciences, University of California at San Diego, La Jolla, CA 92093, USA}
 
@@
 In order to maintain appropriate connectivity, or to alter it as a means of encoding memories, numerous enzymes and macromolecules need to be transported along dendrites to the synapses that need them.
-How is this logistical problem solved at the subcellular level?
-And how might a biologically plausible solution constrain the behavior of synaptic plasticity `rules' and learning in general?
+How is this logistical problem solved at the subcellular level? And how might a biologically plausible solution constrain the behavior of synaptic plasticity `rules' and learning in general?
 
 Transport along dendrites is mediated by motor proteins (kinesins and dyneins) that walk along microtubules, carrying cargo at a rate that far exceeds passive diffusion [REFS].
-The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ [REFS].
-It is therefore conceivable that synaptic cargo is transported along dendrites in a relatively non-specific way, and synapses that need the cargo at any particular time trigger its release from the motor protein complexes as they pass.
+The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \cite{Mironov_2007,Wang_2009}.
+It is therefore conceivable that synaptic cargo transport is controlled in a distributed fashion, in which synapses that require cargo trigger its release from the motor protein complexes as they pass.
 This idea is a variant of the well-known synaptic tagging hypothesis \citep{Frey_1997}, which proposes that synapses produce a biochemical `tag' that signals a requirement for synaptic building blocks as part of the plasticity process.
@@
 From simple assumptions about the dynamics of active dendritic transport we develop a model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies.
-In spite of its simplicity, the model is able to develop arbitrarily complex distributions in the concentration of molecular cargo across a dendritic tree.
-The simplicity of the model allows us to analyze its behavior and show how the relative strength of signals that lead to sequestration and the parameters that determine transport rate can affect the specificity of synaptic plasticity.
-[MORE DETAILS, rapid sequestration leads to...
-bottlenecks get caused by....]
+Within this framework, we identify several ways in which local biochemical mechanisms can be orchestrated to produce arbitrarily complex distributions of molecular cargo.
+In addition to addressing the logistical challenges of dendritic transport, we identify several constraints the precision, flexibility, and speed of cargo delivery inherent to this model.
 
@@
 
-Transport along microtubules is mediated by kinesin and dynein motors, which mediate anterograde and retrograde transport, respectively \citep{Hirokawa_2010,Gagnon_2011}.
-Cargo is often simultaneously bound to both forms of motor protein, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Hancock_2014,Buxbaum_2014b} (Fig.
-1A).
-The biophysical mechanisms of intracellular transport is a diverse and active area of research (CITE).
-
-To obtain a general model that can accommodate variations in the biophysical details, we consider microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006}.
-For each time step, the cargo moves left, right, or remains the in the same place.
-In the simplest model, the probabilities associated with each movement are fixed and independent across each time step (Fig.
-1B, top panel).
-This model can capture the movements of molecular motors that make short movements before changing directions.
-However, other motors exhibit sustained movements (CITE).
-This can be captured by incorporating \textit{hysteresis} or history-dependence into the model.
-In this case, we assume the cargo is more likely to continue in the same direction as the previous time step (Fig.
-1B, bottom panel).
-
-While the position of individual cargoes can be highly stochastic, the net movement of a population of cargoes (Fig.
-1C) is predictable.
-Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) history-dependence.
-In both cases, these simulations can be well-fit by an convection-diffusion partial differential equation (Fig.
-1E-F), which is easier to analyze because it is deterministic and contains fewer variables \citep{Smith_2001}.
-
-\begin{figure}[!htbp]
+\begin{figure}[!b]
 \begin{center}
@@
 
-The partial differential equation in Figure 1E can be approximated by discretizing a dendritic tree into small compartments, and considering the movement of cargo between neighboring compartments as a chemical reaction with first order kinetics.
+Transport along microtubules is mediated by kinesin and dynein motors, which mediate anterograde and retrograde transport, respectively \citep{Hirokawa_2010,Gagnon_2011}.
+Cargo is often simultaneously bound to both forms of motor protein, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Hancock_2014,Buxbaum_2014b} (Fig.
+1A).
+
+To obtain a general model that can accommodate variations in the biophysical details, we consider microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006,Newby_2010,Bressloff_2009}.
+For each time step, the cargo moves left, right, or remains the in the same place.
+In the simplest model, the probabilities associated with each movement are fixed and independent across each time step (Fig. 1B, top panel).
+A potentially more realistic model incorporates \textit{hysteresis} into the biased walk (see Methods).
+In this case, the cargo is more likely to continue in the same direction as it moved on the previous time step (Fig.
+1B, bottom panel; see, e.g., \cite{Soundararajan_2014}).
+
+While the position of individual cargoes can be highly stochastic, the net movement of a population of cargoes (Fig. 1C) is predictable.
+Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) hysteresis.
+In both cases, these simulations can be well-fit by an convection-diffusion partial differential equation (Fig.
+1E-F), which is easier to analyze because it is deterministic and contains fewer variables \citep{Smith_2001}.
+
+The convection-diffusion equation can be numerically simulated by discretizing a dendritic tree into small compartments, and considering the movement of cargo between neighboring compartments as a chemical reaction with first order kinetics.
 In an unbranched cable with $N$ compartments, the mass-action model is:
@@
 
-A central assumption of this model is that the movement of molecules between neighboring compartments is a stochastic and memoryless process.
+\hl{MOVE THIS PARAGRAPH TO METHODS/DISCUSSION?} A central assumption of this model is that the movement of molecules between neighboring compartments is a stochastic and memoryless process.
 This assumption is reasonable if the run length of molecular motors is comparable to the size of the compartments; this appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, thought not necessarily all \citep{Dynes_2007} circumstances (see Discussion).
 In simulations, we observed that this model was not very sensitive to violations of this assumption; the population dynamics of cargoes with substantial run lengths could still be well-fit by this class of models (Fig.
-1F, lower panel; Supp Fig.
-NUMBER).
-[SHOULD THIS BE MOVED TO DISCUSSION?]
+1F, lower panel; Supplementary Fig?).
 
@@
 The exchange of $u$ between neighboring compartments approaches an equilibrium/steady-state ($ss$) distribution over time. In an unbranched cable, this occurs precisely when:
-$$
+\begin{equation}
 \frac{u_i}{u_{i+1}} \Bigg|_{ss} = \frac{b_i}{a_i}
-$$
+\end{equation}
 (see Methods).
@@
 Let $\tilde{u}$ denote the desired steady-state level of $u$ in each compartment.
-For example, $\tilde{u}_i$ might refer to the local concentration of biochemical signal that ``tags'' synapses for plasticity (CITE); such a tag might be positively correlated to the desired level of delivered cargo.
+For example, $\tilde{u}_i$ might refer to the local concentration of biochemical signal that ``tags'' synapses for plasticity \citep{Frey_1997}; such a tag might be positively correlated to the desired level of delivered cargo.
 To match this desired distribution, the ratio of local trafficking rates should satisfy:
-$$
+\begin{equation}
 \frac{b_i}{a_i} = \frac{\tilde{u}_i}{\tilde{u}_{i+1}}
-$$
-
-For example, we can create an linear gradient by specifying $\tilde{u}_i \propto i$ (Fig.
-1B-C).
-The transport rule only determines the steady-state ratios of cargo in neighboring compartments; it cannot control the slope of the linear profile.
-Instead, the slope is controlled by tuning the total amount of cargo in the cable (Fig.
-1C).
-These results extend directly to branched morphologies (see Methods).
-
-%For any pair of connected compartments:
-%$$
-%\frac{u_p}{u_c} \Bigg|_{ss} = \frac{b}{a}
-%$$
-%where $u_p$ is the level in the ``parent" compartment (closer to soma) and $u_c$ is the level in the ``child" compartment (closer to periphery); $b$ and $a$ refer to the local transport rate constants between this pair of compartments.
-
-These rules could be locally implemented by simple biochemical reaction networks.
-Consider the cytoplasmic calcium concentration, $[ca]_i$, as a candidate second messenger.
-Increases in $[ca]_i$ simultaneously arrest anterograde and retrograde microtubular transport \citep{Wang_2009}.
-That is, for any pair of compartments, the anterograde rate constant is determined by calcium in the parent compartment, $a = f([ca]_p)$,  and the retrograde rate constant is determined by calcium in the child compartment, $b = f([ca]_c)$, where $f$ is a function that describes how calcium alters the transport rates.
-This satisfies equation (4) and results in $\tilde{u}_i = 1/f([ca]_i)$:
-$$
-\frac{b}{a} = \frac{f([ca]_c)}{f([ca]_p)} = \frac{\tilde{u}_p}{\tilde{u}_c}
-$$
-
-To test the plausibility of this model in a complex morphology, we used an existing reconstruction of a CA1 pyramidal neuron \citep{Migliore_2012} that includes complex voltage-dependent conductances and synapses.
-Excitatory synaptic input was delivered to 120 locations within three dendritic regions (red dots, Fig.
-1D), and the average membrane potential in each electrical compartment determined the target level $\tilde{u}_i$ in each compartment (Methods).
-This models how molecular cargo could be selectively trafficked to active synaptic sites.
-Figures 2E and 2F confirm that the spatial distribution of $u$ approaches the desired steady-state.
+\end{equation}
 
@@
 
+For example, a linear expression pattern emerges when $\tilde{u}_i \propto i$, resulting in $b_i / a_i = i / i + 1$ (Fig. 2B).
+This rule produces the expected linear expression gradient with the slope controlled by tuning the total amount of cargo in the cable (Fig. 2C).
+
+These results extend directly to branched morphologies (see Methods). For any pair of connected compartments:
+\begin{equation}
+%\frac{u_p}{u_c} \Bigg|_{ss} = \frac{b}{a}
+\frac{b}{a} = \frac{\tilde{u}_p}{\tilde{u}_c}
+\end{equation}
+where $u_p$ is the level in the ``parent" compartment (closer to soma) and $u_c$ is the level in the ``child" compartment (closer to periphery); $b$ and $a$ refer to the local transport rate constants between this pair of compartments.
+
+\hl{MOVE THIS PARAGRAPH TO DISCUSSION OR DELETE?} These rules could be locally implemented by simple biochemical reaction networks.
+Consider the cytoplasmic calcium concentration, $[ca]_i$, as a candidate second messenger.
+Increases in $[ca]_i$ simultaneously arrest anterograde and retrograde microtubular transport \citep{Wang_2009}.
+That is, for any pair of compartments, the anterograde rate constant is determined by calcium in the parent compartment, $a = f([ca]_p)$,  and the retrograde rate constant is determined by calcium in the child compartment, $b = f([ca]_c)$, where $f$ is a function that describes how calcium alters the transport rates.
+This results in:
+\begin{equation}
+\frac{b}{a} = \frac{f([ca]_c)}{f([ca]_p)} = \frac{\tilde{u}_p}{\tilde{u}_c}
+\end{equation}
+where $\tilde{u}_i = 1/f([ca]_i)$.
+
+To test the plausibility of this model in a complex morphology, we extended an existing multi-compartment model of a CA1 pyramidal neuron \citep{Migliore_2012}.
+Excitatory synaptic input was delivered to 120 locations within three dendritic regions (red dots, Fig.
+2D), and the average membrane potential in each electrical compartment determined the target level $\tilde{u}_i$ in each compartment (Methods).
+This models how molecular cargo could be selectively trafficked to active synaptic sites.
+Figures 2E and 2F confirm that the spatial distribution of $u$ approaches the desired steady-state.
+
 \subsection*{Convergence rate}
@@
 Biochemical processes are time-sensitive.
-For example, newly synthesized proteins must be delivered to synapses within \textasciitilde1 hour to support long-term potentiation in CA1 pyramidal cells \citep{Frey_1997,Frey_1998}.
-Thus, it is of substantial interest to examine factors that influence the speed of transport in the model.
+For example, newly synthesized proteins must be delivered to synapses within $\sim$1 hour to support long-term potentiation in CA1 pyramidal cells \citep{Frey_1997,Frey_1998}.
+It is therefore of substantial interest to examine factors that influence the speed of transport in the model.
 
-In equation (5), we implicitly required $\tilde{u}_i > 0$ for all $i$ in order to avoid division by zero.
-Intuitively, if $\tilde{u}_i = 0$ for some compartment, then the more peripheral compartments become disconnected and inaccessible to the rest of the cell.
+In equations (4) and (5), we implicitly required each $\tilde{u}_i > 0$ in order to avoid division by zero.
+Intuitively, if $\tilde{u}_i = 0$ for some compartment, then no cargo can flow through that compartment, cutting of more peripheral compartments from the transport system.
 Similarly, if certain $\tilde{u}_i$ are nearly equal to zero, then transport through these compartments will act as a bottleneck for transport, and convergence to the desired distribution will be slow.
@@
 This results in the mass-action model:
-$$
+\begin{equation}
 u_1 \underset{x}{\overset{\epsilon}{\rightleftharpoons}} u_2 \underset{\epsilon}{\overset{x}{\rightleftharpoons}} u_3
-$$
+\end{equation}
 We assume that $u$ begins at one end of the cable, and examine the how taking $\epsilon$ to zero affects the convergence rate.
-Figure 2B shows that the convergence rate slows dramatically as $\epsilon$ decreases.
+Figure 3B shows that the convergence rate slows dramatically as $\epsilon$ decreases.
 This can be can be analyzed using basic linear systems theory; the convergence rate is given by the non-zero eigenvalue with smallest magnitude, which can be thought of as a rate-limiting step or process for the system (Methods, Supp.
@@
 Simulations confirmed this analysis and showed that the convergence rate diverges to infinity as $\epsilon$ approaches zero (Fig.
-2C).
+3C).
 
@@
 
-Similar results were obtained in the multi-compartment CA1 neuron model.
+Qualitatively similar results were obtained in the multi-compartment CA1 neuron model.
 The model converged to a uniform target distribution more quickly than to a ``bottleneck" target distribution, in which the middle third of the apical dendrite had low steady-state levels of cargo (Fig.
@@
 
-In addition to this global view of convergence (Fig.
-3D), we considered how the transport bottleneck affected transport to individual dendritic compartments.
+In addition to this global view of convergence (Fig. 3D), we considered how the transport bottleneck affected transport to individual dendritic compartments.
 Consider a scenario where transported cargo produces a local chemical reaction after a critical concentration threshold is reached; for example, a recently potentiated synapse might be stabilized after enough plasticity-related factors are delivered from the soma.
@@
 This results in the following mass-action model:
-$$
+\begin{equation}
 \begin{array}{cccccccc}
@@
 \end{array}
-$$
+\end{equation}
 As before, a molecule $u$ is transported along a network of microtubules (top row, in equation 6).
@@
 We then choose detachment rate constants that transform the microtubular distribution into our desired distribution for $u^\star$:
-$$
+\begin{equation}
 c_i \propto \frac{\tilde{u}^\star_i}{\tilde{u}_i}
-$$
+\end{equation}
 Here, $\tilde{u}$ and $\tilde{u}^\star$ respectively denote the quasi-steady state distributions for $u$ and $u^\star$, respectively.
@@
 One strategy (Fig.
-4C) is to choose microtubular trafficking rates such that $\tilde{u}$ exactly matches $\tilde{u}^\star$; detachment from the microtubules is unbiased ($c_i =$ constant).
-Figure 3C shows that the desired spatial distribution is achieved both along the microtubules (red line) and for the detached/activated cargo (blue line).
+4C) is to choose microtubular trafficking rates such that $\tilde{u}$ exactly matches $\tilde{u}^\star$, and choose the detachment rate constants to be spatially uniform ($c_i =$ constant).
+Figure 4C shows that the desired spatial distribution is achieved both along the microtubules (red line) and for the detached/activated cargo (blue line).
 
@@
 
-Figure 4E shows the behavior of an intermediate model, whose parameters are a linearly interpolation between the extreme strategies shown in Figure 4C and 4D.
+Figure 4E shows the behavior of an intermediate model, whose parameters are a linear interpolation between the extreme strategies shown in Figure 4C and 4D.
 Thus, effective trafficking systems can be achieved by a spectrum of strategies, which may be suited to different situations and purposes (see Discussion).
 
-\subsection*{Non-local interactions can occur when time scales aren't separated}
+\subsection*{Non-specific cargo delivery occurs when time scales aren't separated}
+
+We have thusfar considered models that produce a desired distribution of cargo to arbitrary precision.
+However, real neurons might tolerate some sloppiness in synaptic trafficking (or even utilize it as a substrate for complex plasticity rules).
+Thus, we examined the consequences of relaxing the separation of time scales between transport and detachment.
+In general, this improves the speed at which cargoes are delivered to synapses, but decreases the accuracy or specificity of delivery.
+
+To illustrate this, we considered an experiment in which cargo is delivered to recently activated synaptic sites.
 
@@
 Local activity signals provide a means to sequester dendritic cargo as it passes a synapse, providing a way for plasticity-inducing synaptic stimulation to `tag' a synapse.
-Direct evidence of activity-dependent arrest [REF Elife] and accumulation \citep{Krichevsky_2001,Buxbaum_2014a} of mRNAs and other actively transported biomolecules suggests that the kind of mechanism we studied here is involved in regulating synapses in parallel with local synthesis mechanisms.
+Direct evidence of activity-dependent arrest \citep{Soundararajan_2014} and accumulation \citep{Krichevsky_2001,Buxbaum_2014a} of mRNAs and other actively transported biomolecules suggests that the kind of mechanism we studied here is involved in regulating synapses in parallel with local synthesis mechanisms.
 We are agnostic about the precise identity of the activity signal that controls transport and sequestration, but note that experiments have shown that local calcium \citep{Wang_2009} and ADP \citep{Mironov_2007}, alter anterograde and retrograde transport rates.

### 2015-08-20 latex/paper.tex
finishing results...

@@
 3E, upper right portion of plot).
-Interestingly, the presence of a bottleneck actually \textit{shortened} the transport delay to proximal compartments, compared to the uniform target distribution (Fig.
+Interestingly, the presence of a bottleneck also \textit{shortens} the transport delay to proximal compartments, compared to the uniform target distribution (Fig.
 3E, lower left portion of plot).
-This occurs because molecules that were delayed from entering the distal compartments spread throughout the proximal compartments, reaching higher levels earlier in the simulation.
+This occurs because cargo delayed by the bottleneck spreads throughout the proximal compartments, reaching higher levels earlier in the simulation.
 
-One non-obvious prediction of this analysis is that transport to distal compartments should be quickened by allowing higher levels of $u$ into the proximal compartments at steady-state (Fig.
+One experimentally testable prediction of this analysis is that transport to distal compartments should be quickened by allowing higher levels of $u$ into the proximal compartments at steady-state (Fig.
 3E).
@@
 
-We have thusfar considered models that produce a desired distribution of cargo to arbitrary precision.
-However, real neurons might tolerate some sloppiness in synaptic trafficking (or even utilize it as a substrate for complex plasticity rules).
+We have thusfar considered models that produce a desired distribution of cargo to arbitrarily high precision.
+However, real neurons probably tolerate some sloppiness in synaptic trafficking (or even utilize it as a substrate for complex plasticity rules).
 Thus, we examined the consequences of relaxing the separation of time scales between transport and detachment.
@@
 
-To illustrate this, we considered an experiment in which cargo is delivered to recently activated synaptic sites.
+To appreciate this, consider an experiment where distal synaptic inputs on the apical tuft are stimulated (Fig.
+5A).
+If the average detachment rate constants are sufficiently slow, then, as before, cargo is delivered selectively to the stimulated region (Fig.
+5A, left).
+If we increase the detachment rates by a uniformly scaling, some cargo ``leaks off'' the microtubule path on its way to the distal synapses (Fig.
+5A, right).
+We refer to this as a ``non-specific'' delivery of cargo, since cargo is not selectively delivered to the stimulated sites.
+\hl{In this case, non-specificity might induce on-the-path synaptic plasticity; a possibility that has some experimental evidence} \citep{Han_2013}.
+
+Tradeoff curves between the average detachment rate constant and the non-specificity of transport for this stimulation pattern are shown in figure 5B.
+Importantly, this tradeoff exists for both trafficking strategies we examined in figure 4.
+In this case, the uniform trafficking strategy (blue line in Fig.
+5B; see Fig.
+4D) outperforms the specific trafficking strategy (red line in Fig.
+5B; see Fig.
+4C) since the latter suffers from bottleneck in the proximal apical zone.
+
+Different patterns of non-specificity occur for other stimulation patterns.
+When the entire apical tree is stimulated, fast detachment can result in a complete occlusion of cargo delivery to distal synaptic sites (Fig.
+5C).
+As before, a tradeoff between specificity and delivery speed is present for both transport strategies (Fig.
+5D).
+Interestingly, the specific trafficking strategy outperforms the uniform trafficking strategy in this case (in contrast to Fig.
+5A-B).
+This is due to the lack of a bottleneck, and the fact that the uniform trafficking strategy initially sends cargo to the basal dendrites where it is not released.
 
@@
 
-\subsection*{Tradeoff between speed of consolidation and specificity of potentiation}
+\subsection*{Transport can be optimized for both speed and precision for a given stimulation pattern}
 
-We sought to understand the general relationship
+In figure 5, we showed that scaling the detachment rates ($c_i$), and leaving the transport rates ($a_i$,$b_i$) fixed produces a proximal bias in cargo delivery.
+That is, synapses closer to the soma are more likely to capture cargo at the expense of distal synapses.
+We reasoned that increasing the anterograde transport rate of cargo could correct for this bias, producing transport rules that are both fast and precise.
+
+We examined this possibility in a reduced model --- an unbranched cable --- so that we could develop simple heuristics that precisely achieve a desired distribution of cargo (more complex, \textit{ad hoc}, heuristics could be developed for complex morphologies).
+In the reduced model, cargo begins on the left end of the cable and is transported to a number of synaptic sites, each of which is modeled as a double-exponential curve.
+
+As before, cargo can be precisely delivered to a variety of stimulation patterns when the detachment rate is sufficiently slow (Fig.
+6A); when the detachment rate is n\"iavely increased to speed up the rate of delivery, a proximal bias develops for all stimulation patterns (Fig.
+6B).
+This bias is qualitatively exponential.
+
+We then hand-tuned the transport rate constants to deliver equal cargo to six evenly spaced synaptic sites (top row of Fig.
+6C).
+Specifically, we increased the anterograde rate constants ($a_i$) and decreased the retrograde rate constants ($b_i$) by a decreasing linear function of position so that $a_N = b_N$ at the right side of the cable (see Methods).
+Intuitively, this pushes cargo past the proximal synaptic sites more quickly, canceling out the exponential delivery bias induced by fast detachment.
+
+However, this tuned transport model does not precisely deliver cargo for other stimulation patterns.
+When the number of synapses on the cable is decreased, a distal delivery bias is observed because too little cargo is released on the proximal portion of the cable (middle row, Fig.
+6C).
+Even when the number of synapses is held constant, changing the position of the synapses can disrupt equal distribution of cargo.
+This is shown in the bottom row of figure 6C, where a distal bias again develops when the majority of activated synapses are positioned proximally.
+Thus, within the simple framework we've developed, the delivery of cargo can be tuned to achieve both precision and speed for a specified target distribution.
+However, non-specific cargo delivery occurs when different stimulation patterns are applied (assuming the transport parameters are not re-tuned).
 

### 2015-08-21 latex/paper.tex
first pass at results done...ish

@@
 
-\author[1,2,3]{Alex H. Williams}
+\author[1,2,3,*]{Alex H. Williams}
 \author[2]{Cian O'Donnell}
@@
 \affil[5]{Division of Biological Sciences, University of California at San Diego, La Jolla, CA 92093, USA}
+\affil[*]{Address correspondence to: ahwillia@stanford.edu}
 
@@
 Figure 3 illustrates and analyzes this intuition in a simple three compartment model.
-The two compartments on the end of the cable have the same desired level, $\tilde{u}_1 = \tilde{u}_3$; the middle compartment acts as a bottleneck when $\tilde{u}_2$ is very small (Fig.
-3A).
+The two compartments on the end of the cable have the same desired level, $\tilde{u}_1 = \tilde{u}_3$; the middle compartment acts as a bottleneck when $\tilde{u}_2$ is very small (Fig. 3A).
 This results in the mass-action model:
@@
 1).
-Simulations confirmed this analysis and showed that the convergence rate diverges to infinity as $\epsilon$ approaches zero (Fig.
-3C).
+Simulations confirmed this analysis and showed that the convergence rate diverges to infinity as $\epsilon$ approaches zero (Fig. 3C).
 
@@
 
-As expected, introducing a bottleneck caused much longer delays to compartments distal to that bottleneck (Fig.
-3E, upper right portion of plot).
-Interestingly, the presence of a bottleneck also \textit{shortens} the transport delay to proximal compartments, compared to the uniform target distribution (Fig.
-3E, lower left portion of plot).
+As expected, introducing a bottleneck caused much longer delays to compartments distal to that bottleneck (Fig. 3E, upper right portion of plot).
+Interestingly, the presence of a bottleneck also \textit{shortens} the transport delay to proximal compartments, compared to the uniform target distribution (Fig. 3E, lower left portion of plot).
 This occurs because cargo delayed by the bottleneck spreads throughout the proximal compartments, reaching higher levels earlier in the simulation.
@@
 The models above present a simple hypothesis for controlling molecular transport along an intricate system of microtubules.
-While certain types of molecular cargo stay on the microtubule network (e.g.
-mitocondria), others detach from the microtubules after a reaching a desired location.
+While certain types of molecular cargo stay on the microtubule network (e.g. mitocondria), others detach from the microtubules after a reaching a desired location.
 For example, dendritic mRNAs are transported within densely-packed granules, and can be locally released following granule disassembly \citep{Krichevsky_2001,Buxbaum_2014a}.
-We model the detachment from the microtubule network as an irreversible process, and include a compartment-specific degradation reaction.
-This results in the following mass-action model:
+We model the detachment from the microtubule network as an irreversible process, and include a compartment-specific degradation reaction. This results in the following mass-action model:
 \begin{equation}
@@
 Note that only $u^\star$ is subject to degradation; the molecule is assumed to be protected from degradation during transport.
-This model can be extended to branched morphologies (Fig.
-3A).
+This model can be extended to branched morphologies (Fig. 3A).
 
@@
 
-This model admits a spectrum of strategies for controlling the distribution of molecular cargo (Fig.
-4B).
+This model admits a spectrum of strategies for controlling the distribution of molecular cargo (Fig. 4B).
 One strategy (Fig.
@@
 Thus, we examined the consequences of relaxing the separation of time scales between transport and detachment.
-In general, this improves the speed at which cargoes are delivered to synapses, but decreases the accuracy or specificity of delivery.
-
-To appreciate this, consider an experiment where distal synaptic inputs on the apical tuft are stimulated (Fig.
-5A).
-If the average detachment rate constants are sufficiently slow, then, as before, cargo is delivered selectively to the stimulated region (Fig.
-5A, left).
-If we increase the detachment rates by a uniformly scaling, some cargo ``leaks off'' the microtubule path on its way to the distal synapses (Fig.
-5A, right).
-We refer to this as a ``non-specific'' delivery of cargo, since cargo is not selectively delivered to the stimulated sites.
-\hl{In this case, non-specificity might induce on-the-path synaptic plasticity; a possibility that has some experimental evidence} \citep{Han_2013}.
-
-Tradeoff curves between the average detachment rate constant and the non-specificity of transport for this stimulation pattern are shown in figure 5B.
-Importantly, this tradeoff exists for both trafficking strategies we examined in figure 4.
-In this case, the uniform trafficking strategy (blue line in Fig.
-5B; see Fig.
-4D) outperforms the specific trafficking strategy (red line in Fig.
-5B; see Fig.
-4C) since the latter suffers from bottleneck in the proximal apical zone.
-
-Different patterns of non-specificity occur for other stimulation patterns.
-When the entire apical tree is stimulated, fast detachment can result in a complete occlusion of cargo delivery to distal synaptic sites (Fig.
-5C).
-As before, a tradeoff between specificity and delivery speed is present for both transport strategies (Fig.
-5D).
-Interestingly, the specific trafficking strategy outperforms the uniform trafficking strategy in this case (in contrast to Fig.
-5A-B).
-This is due to the lack of a bottleneck, and the fact that the uniform trafficking strategy initially sends cargo to the basal dendrites where it is not released.
+In general, this improves the speed at which cargoes are delivered to synapses, but decreases the accuracy of delivery.
 
@@
 \end{figure}
+
+To appreciate this, consider an experiment where distal synaptic inputs on the apical tuft are stimulated (Fig. 5A).
+If the average detachment rate constants are sufficiently slow, then, as before, cargo is delivered selectively to the stimulated region (Fig. 5A, left).
+If we increase the detachment rates by a uniformly scaling, some cargo ``leaks off'' the microtubule path on its way to the distal synapses (Fig. 5A, right).
+We refer to this as a ``non-specific'' delivery of cargo, since cargo is not selectively delivered to the stimulated sites.
+\hl{For this stimulation pattern, non-specificity might induce on-the-path synaptic plasticity; a possibility that has some experimental evidence} \citep{Han_2013}.
+
+Tradeoff curves between the average detachment rate constant and the non-specificity of transport for this stimulation pattern are shown in figure 5B.
+Importantly, this tradeoff exists for both trafficking strategies we examined in figure 4 --- the selective transport strategy (see Fig 4D) and uniform transport strategy (see Fig. 4C).
+The uniform trafficking strategy (Fig. 5B, blue line) outperforms the specific trafficking strategy (Fig. 5B, red line) since the latter suffers from bottleneck in the proximal apical zone.
+
+Different patterns of non-specificity occur for other stimulation patterns.
+When the entire apical tree is stimulated, fast detachment can result in a complete occlusion of cargo delivery to distal synaptic sites (Fig. 5C).
+As before, a tradeoff between specificity and delivery speed is present for both transport strategies (Fig. 5D).
+Interestingly, the specific trafficking strategy outperforms the uniform trafficking strategy in this case (in contrast to Fig. 5A-B).
+This is due to the lack of a bottleneck, and the fact that the uniform trafficking strategy initially sends cargo to the basal dendrites where it is not released.
 
@@
 
-As before, cargo can be precisely delivered to a variety of stimulation patterns when the detachment rate is sufficiently slow (Fig.
-6A); when the detachment rate is n\"iavely increased to speed up the rate of delivery, a proximal bias develops for all stimulation patterns (Fig.
-6B).
-This bias is qualitatively exponential.
-
-We then hand-tuned the transport rate constants to deliver equal cargo to six evenly spaced synaptic sites (top row of Fig.
-6C).
-Specifically, we increased the anterograde rate constants ($a_i$) and decreased the retrograde rate constants ($b_i$) by a decreasing linear function of position so that $a_N = b_N$ at the right side of the cable (see Methods).
-Intuitively, this pushes cargo past the proximal synaptic sites more quickly, canceling out the exponential delivery bias induced by fast detachment.
-
-However, this tuned transport model does not precisely deliver cargo for other stimulation patterns.
-When the number of synapses on the cable is decreased, a distal delivery bias is observed because too little cargo is released on the proximal portion of the cable (middle row, Fig.
-6C).
-Even when the number of synapses is held constant, changing the position of the synapses can disrupt equal distribution of cargo.
-This is shown in the bottom row of figure 6C, where a distal bias again develops when the majority of activated synapses are positioned proximally.
-Thus, within the simple framework we've developed, the delivery of cargo can be tuned to achieve both precision and speed for a specified target distribution.
-However, non-specific cargo delivery occurs when different stimulation patterns are applied (assuming the transport parameters are not re-tuned).
-
 \begin{figure}[!htbp]
@@
 \end{figure}
+
+As before, cargo can be precisely delivered to a variety of stimulation patterns when the detachment rate is sufficiently slow (Fig.
+6A); when the detachment rate is n\"iavely increased to speed up the rate of delivery, a proximal bias develops for all stimulation patterns (Fig.
+6B).
+This bias is qualitatively exponential.
+
+We then hand-tuned the transport rate constants to deliver equal cargo to six evenly spaced synaptic sites (top row of Fig. 6C).
+Specifically, we increased the anterograde rate constants ($a_i$) and decreased the retrograde rate constants ($b_i$) by a decreasing linear function of position so that $a_N = b_N$ at the right side of the cable (see Methods).
+Intuitively, this pushes cargo past the proximal synaptic sites more quickly, canceling out the exponential delivery bias induced by fast detachment.
+
+However, this tuned transport model does not precisely deliver cargo for other stimulation patterns.
+When the number of synapses on the cable is decreased, a distal delivery bias is observed because too little cargo is released on the proximal portion of the cable (middle row, Fig. 6C).
+Even when the number of synapses is held constant, changing the position of the synapses can disrupt equal distribution of cargo.
+This is shown in the bottom row of figure 6C, where a distal bias again develops when the majority of activated synapses are positioned proximally.
+Thus, within the simple framework we've developed, the delivery of cargo can be tuned to achieve both precision and speed for a specified target distribution.
+However, non-specific cargo delivery occurs when different stimulation patterns are applied (assuming the transport parameters are not re-tuned).
+
+To examine these observations over a larger range of stimulation patterns and transport parameters, we plotted tradeoff curves between delivery precision and speed.
+We first examined a cable with six evenly spaced delivery sites (same as top row of Fig. 6A-C).
+As before, a hard tradeoff between specifity and delivery speed exists for the untuned model (blue line in Fig. 6D, same transport rate constants as Fig. 6A and 6B).
+As the transport rate constants are tuned to increase anterograde movement, the optimal points along the tradeoff curve move to the left, representing faster transport times.
+However, the tradeoff curves also become nonmonotonic: the error (non-specificity) initially decreases as the detachment rate decreases, but begins to increase after a certain well-matched point.
+Points on the descending left branch of the curve represent cargo distributions with proximal bias (detachment is too fast); points on the ascending right branch correspond to distal bias (detachment is too slow).
+
+We observed qualitatively similar tradeoff curves for randomly positioned synapses (Fig.
+6E), and for randomizing the number and position of synapses (Fig.
+6F).
+There is substantial variability in the tradeoff curves in both cases, but particularly when randomizing the number of synaptic inputs.
+Notably, the untuned transport model (blue curves) always converge to zero error as the detachment rate decreases.
+Thus, for this model, it appears that the only way to achieve very precise and flexible transport is to have a slow detachment rate.
 
@@
 In other cases, it might be undesirable to rapidly shift protein expression based on transient changes to the neuron or circuit; controlling expression at the level of mRNA might prevent this.
-We showed that it is possible to interpolate between these two strategies (Fig.
-4E), which might allow neurons to trade off between the relative advantages of each.
+We showed that it is possible to interpolate between these two strategies (Fig. 4E), which might allow neurons to trade off between the relative advantages of each.
 
@@
 
-Other assumptions of the mass-action model - Second, the model assumes are many copies of $u$ in each compartment.
-This allows us to approximate the mass as a continuous variable, and the dynamics of the system as deterministic.
-Third, the number of molecular motors and capacity of the microtubules is not saturated by the level of $u$ in any compartment.
+Other assumptions of the mass-action model - Second, the model assumes are many copies of $u$ in each compartment.This allows us to approximate the mass as a continuous variable, and the dynamics of the system as deterministic.Third, the number of molecular motors and capacity of the microtubules is not saturated by the level of $u$ in any compartment.
 This means that the rate of transport from compartment A to compartment B linearly increases with the amount of $u$ in compartment A.

### 2015-08-21 latex/paper.tex
change abstract, include more stuff on logistical problem of transport

@@
 
-\title{Trafficking synaptic materials in complex morphologies involves tradeoffs in speed and precision}
+\title{Trafficking synaptic cargo in complex morphologies involves tradeoffs in speed and precision}
 
@@
 Long lived changes in synaptic strength underlie persistent memories and in many cases require activity dependent transcription of plasticity-related genes.
-A well-known problem is to understand how appropriate gene products, such as synaptic proteins and mRNAs, get trafficked to the synapses that require them in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many kinds of neuron.
-Using a simple, biophysically-rooted model of microtubule transport we show that rapid delivery of plasticity-related cargo entails loss of specificity in the synapses that eventually receive it.
-The model predicts that neurons must balance the biochemical parameters that control trafficking to find a compromise between the precision and speed with which long-lived connectivity patterns are formed.
-Conversely, imbalances in transport parameters could lead to hypo-, or hyperconnectivity as well as loss of precision in associative memory, identifying a potential role for transport machinery in brain disorders that exhibit connectivity and plasticity phenotypes.
+A well-known problem is to understand how appropriate gene products, such as synaptic proteins and mRNAs, get trafficked to the synapses that require them in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many neurons.
+We develop a biophysically-rooted model of microtubule transport, and identify procedures that produce desired distributions of cargo to arbitrarily high precision.
+Importantly, these transport systems can be plausibly encoded by simple, localized biochemical reactions.
+The model predicts that the precise and flexible delivery of synaptic cargo requires the capture of synaptic cargo to occur on a slower timescale than the movement of cargo across the microtubule network.
+Thus, neurons must find a compromise between the specificity and speed with which synaptic materials are delivered and long-lived connectivity patterns are formed.
 \end{abstract}
+
+% OLD ABSTRACT:
+%Long lived changes in synaptic strength underlie persistent memories and in many cases require activity dependent transcription of plasticity-related genes.
+%A well-known problem is to understand how appropriate gene products, such as synaptic proteins and mRNAs, get trafficked to the synapses that require them in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many kinds of neuron.
+%Using a simple, biophysically-rooted model of microtubule transport we show that rapid delivery of plasticity-related cargo entails loss of specificity in the synapses that eventually receive it.
+%The model predicts that neurons must balance the biochemical parameters that control trafficking to find a compromise between the precision and speed with which long-lived connectivity patterns are formed.
+%Conversely, imbalances in transport parameters could lead to hypo-, or hyperconnectivity as well as loss of precision in associative memory, identifying a potential role for transport machinery in brain disorders that exhibit connectivity and plasticity phenotypes.
 

### 2015-08-22 latex/paper.tex
fix typos, add some figure legends

@@
 \author[2,5]{Terrence Sejnowski}
-\author[4]{Timothy O'Leary}
+\author[4,*]{Timothy O'Leary}
 
@@
 \affil[5]{Division of Biological Sciences, University of California at San Diego, La Jolla, CA 92093, USA}
-\affil[*]{Address correspondence to: ahwillia@stanford.edu}
+\affil[*]{Address correspondence to: ahwillia@stanford.edu, toleary@brandeis.edu}
 
@@
 
+\hl{}
+
 \section*{Results}
@@
 
-\begin{figure}[!b]
+\begin{figure}[!tb]
 \begin{center}
@@
 To obtain a general model that can accommodate variations in the biophysical details, we consider microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006,Newby_2010,Bressloff_2009}.
-For each time step, the cargo moves left, right, or remains the in the same place.
+For each time step, the cargo moves left, right, or remains in the same place.
 In the simplest model, the probabilities associated with each movement are fixed and independent across each time step (Fig. 1B, top panel).
@@
 \hl{MOVE THIS PARAGRAPH TO METHODS/DISCUSSION?} A central assumption of this model is that the movement of molecules between neighboring compartments is a stochastic and memoryless process.
-This assumption is reasonable if the run length of molecular motors is comparable to the size of the compartments; this appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, thought not necessarily all \citep{Dynes_2007} circumstances (see Discussion).
+This assumption is reasonable if the \hl{run length (jargon?)} of molecular motors is comparable to the size of the compartments; this appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, thought not necessarily all \citep{Dynes_2007} circumstances (see Discussion).
 In simulations, we observed that this model was not very sensitive to violations of this assumption; the population dynamics of cargoes with substantial run lengths could still be well-fit by this class of models (Fig.
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[!tb]
 \begin{center}
 \includegraphics[width=0.9\columnwidth]{01_mass_action.png}
-\caption{Delivery of cargo to active synapses in a complex dendritic tree}
+\caption{Local trafficking parameters determine the spatial distribution of biomolecules by a simple rule.
+\textbf{(A)} Diagram of the mass action transport model for a simple branched morphology.
+%The steady-state ratio of $u$ between any two neighboring compartments is equal to the reciprocal ratio of the trafficking rate constants between those compartments.
+\textbf{(B)} A simulation of a nine compartment cable, with trafficking rate constants set to produce a linear gradient using the steady-state relation shown in panel A.
+%The initial distribution of $u$ is uniform (t=0); over time the system achieves the desired linear gradient (steady-state occurs around t=5, in this example).
+\textbf{(C)} The slope of the linear gradient shown in panel B is determined by the total amount of $u$ present in the model; the slope increases as more of $u$ is present, but the linear profile is preserved.
+\textbf{(D)} A model of a CA1 pyramidal cell with 742 compartments based on \cite{Migliore_2012}; excitatory synapses were added at the locations marked by red dots. 
+\textbf{(E)} The average membrane potential in each compartment of the CA1 model cell was used to define a desired spatial distribution, and transport rate constants were chosen according to equation (4).
+The desired spatial distribution of cargo emerges over time, after starting in the soma.
+\textbf{(F)} The desired and steady-state profile of $u$ for each compartment in the simulation shown in panel E.
+}
 \end{center}
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[!tb]
 \begin{center}
 \includegraphics[width=0.9\columnwidth]{03_convergence.png}
-\caption{Bottlenecks in transport}
+\caption{ Convergence to steady-state is slow when molecules must be transported across bottlenecks ---compartments with low target levels.
+\textbf{(A)} A three-compartment transport model, with the middle compartment acting as a bottleneck.
+The vertical bars represent the desired steady-state level of $u$ in each compartment.
+The rate of transport into the middle compartment is small ($\epsilon$, dashed harpoons) relative to transport out of the middle compartment.
+\textbf{(B)} As $\epsilon$ decreases, the model converges more slowly and the steady-state level decreases in the middle compartment.
+\textbf{(C)} Simulations (black dots) confirm that the time to convergence is given by the smallest non-zero eigenvalue of the system (analytically calculated line).
+This eigenvalue can be thought of as the rate-limiting step of the system.
+\textbf{(D)} Convergence ($L_1$ distance) to a uniform target distribution (red line) is faster than a target distribution containing a bottleneck (blue line) in the CA1 model.
+\textbf{(E)} For all compartments that reach a threshold level ($u_i = 0.001$), the simulated time it takes to reach threshold is plotted against the distance of that compartment to the soma.
+\textbf{(F)} Predicted convergence times for various target distributions (str. rad., stratum radiatum; str. lac., stratum lacunosum/moleculare).}
 \end{center}
@@
 3E).
-This might be tested experimentally by characterizing the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\citet{Steward_1998}, see discussion).
+This might be tested by characterizing the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\citet{Steward_1998}, see discussion).
 To illustrate this in the model CA1 cell, we characterized the time course of transport to the distal apical dendrite (stimulating stratum lacunosum/moleculare), proximal apical dendrite (stimulating stratum radiatum), entire apical dendrite (stimulating both layers), and entire cell (seizure).
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[!tb]
 \begin{center}
@@
 One way to analyze this system is to assume that these three processes --- trafficking, detachment, and degradation --- occur on separate timescales.
-If trafficking is sufficiently faster than detachment ($a,b \gg c$), then $u$ approaches a quasi-steady state distribution defined by our previous analysis (equation 5).
+If trafficking is sufficiently faster than detachment ($a,b \gg c$), then $u$ approaches a quasi-steady state distribution defined by our previous analysis (equation 4).
 We then choose detachment rate constants that transform the microtubular distribution into our desired distribution for $u^\star$:
@@
 
-In figure 5, we showed that scaling the detachment rates ($c_i$), and leaving the transport rates ($a_i$,$b_i$) fixed produces a proximal bias in cargo delivery.
+\hl{have detachment rate be tunable by amount of stuff present???}
+
+In figure 5, we showed that scaling the detachment rates ($c_i$), while leaving the transport rates ($a_i$, $b_i$) fixed produces a proximal bias in cargo delivery.
 That is, synapses closer to the soma are more likely to capture cargo at the expense of distal synapses.

### 2015-08-25 latex/paper.tex
Tuning result in intro/abstract
rearranged intro/abstract and emphasized the fragility of tuning

@@
 A well-known problem is to understand how appropriate gene products, such as synaptic proteins and mRNAs, get trafficked to the synapses that require them in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many neurons.
-We develop a biophysically-rooted model of microtubule transport, and identify procedures that produce desired distributions of cargo to arbitrarily high precision.
-Importantly, these transport systems can be plausibly encoded by simple, localized biochemical reactions.
+We develop a biophysically-rooted model of microtubule transport, and show how it can sustain arbitrarily complex distributions of cargo using simple, localized biochemical processes.
 The model predicts that the precise and flexible delivery of synaptic cargo requires the capture of synaptic cargo to occur on a slower timescale than the movement of cargo across the microtubule network.
-Thus, neurons must find a compromise between the specificity and speed with which synaptic materials are delivered and long-lived connectivity patterns are formed.
+Tuning the transport parameters reveals that optimal solutions exist, but sensitively depend on the location as well as the number of synapses, suggesting that biological neurons face a compromise between flexibility in connectivity and efficacy in regulating synaptic function.
+% final sentence is the same as that of the intro. Should paraphrase, but this could be the most important finding so it should be in both.
+
 \end{abstract}
@@
 Neurons often have complex dendritic trees, reflecting the dense and structured synaptic connectivity that supports nervous system function.
-In order to maintain appropriate connectivity, or to alter it as a means of encoding memories, numerous enzymes and macromolecules need to be transported along dendrites to the synapses that need them.
-How is this logistical problem solved at the subcellular level? And how might a biologically plausible solution constrain the behavior of synaptic plasticity `rules' and learning in general?
+In order to establish and maintain appropriate connectivity, or to alter it as a means of encoding memories, numerous enzymes and macromolecules, including mRNAs and receptor proteins need to be transported along dendrites to the synapses that need them.
+How is this logistical problem solved at the subcellular level?
+And how might a biologically plausible solution constrain the macroscopic behavior of synaptic plasticity `rules' and learning in general?
 
@@
 The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \cite{Mironov_2007,Wang_2009}.
-It is therefore conceivable that synaptic cargo transport is controlled in a distributed fashion, in which synapses that require cargo trigger its release from the motor protein complexes as they pass.
-This idea is a variant of the well-known synaptic tagging hypothesis \citep{Frey_1997}, which proposes that synapses produce a biochemical `tag' that signals a requirement for synaptic building blocks as part of the plasticity process.
-
 Not all aspects of synaptic plasticity require delivery of cargo from the soma.
 For example, some forms of long-term potentiation (LTP) depend on local protein synthesis and can function in isolated dendrites [REFS].
-However, in the long run, the mRNAs and the machinery that supports such plasticity needs to be replenished.
-Moreover, many long-lasting forms of synaptic plasticity rely on anterograde transport of mRNAs \citep{Kandel_2001,Puthanveettil_2008} and specific mRNAs are known to be selectively transported to regions of heightened synaptic activity \citep{Steward_1998,Steward_2001,Moga_2004} or to developing synaptic contacts \citep{Lyles_2006}.
-The interplay between global distribution and local plasticity mechanisms therefore demands attention.
+Nonetheless, components originating in the soma need to find their way to synapses in the first place and in the long run, the mRNAs and the machinery that supports local biosynthesis needs to be replenished.
+Moreover, many long-lasting forms of synaptic plasticity are known to depend on anterograde transport of mRNAs \citep{Kandel_2001,Puthanveettil_2008} and specific mRNAs are known to be selectively transported to regions of heightened synaptic activity \citep{Steward_1998,Steward_2001,Moga_2004} or to developing synaptic contacts \citep{Lyles_2006}.
 
-From simple assumptions about the dynamics of active dendritic transport we develop a model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies.
-Within this framework, we identify several ways in which local biochemical mechanisms can be orchestrated to produce arbitrarily complex distributions of molecular cargo.
-In addition to addressing the logistical challenges of dendritic transport, we identify several constraints the precision, flexibility, and speed of cargo delivery inherent to this model.
+These observations suggest that synaptic cargo transport is controlled in a distributed fashion, in which synapses that require cargo can trigger its release from motor protein complexes as they pass.
+This idea is a variant of the well-known synaptic tagging hypothesis \citep{Frey_1997}, which proposes that synapses produce a biochemical `tag' that signals a requirement for synaptic building blocks as part of the plasticity process.
+However, for molecular cargo to be distributed throughout a complex dendritic tree in a way that matches supply with local demand, the rates of sequestration of cargo need to approximately balance the rates of transport and production.
+Large imbalances in distribution rates of molecular cargo could conceivably lead to wasteful overproduction, harmful accumulation or depletion, or to severe delays in its delivery. 
+Although much is known about the molecular details of active transport and the coupling of synaptic activity to metabolism and trafficking of subcellular components, there is no general theory of how these details might fit together, nor how they affect higher-level neuronal functions such as synaptic plasticity neural circuit development.
+
+From simple, experimentally verifiable assumptions about the dynamics of active dendritic transport we develop a minimal model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies.
+Local biochemical signals are shown to be capable of producing arbitrarily complex distributions of molecular cargo, but there is an unavoidable tradeoff between the precision of cargo distribution and the rate of its delivery.
+Tuning the transport parameters reveals that optimal solutions exist, but sensitively depend on the location as well as the number of synapses, suggesting that biological neurons face a compromise between flexibility in connectivity and efficacy in regulating synaptic function.
 
@@
 \end{figure}
+
+Activation of synaptic receptors triggers downstream signalling cascades that can alter global gene expression [ref Greenberg, Bading, others] as well as modulating the trafficking and metabolism of molecular cargo locally [REFS].
+[more on this]
 

### 2015-08-28 latex/paper.tex
Technical question
long run lengths might have an effect on the convergence to a target
distribution (intuitively they should…)
add figure legends

--- 2015-08-22 latex/paper.tex
@@
 \includegraphics[width=0.9\columnwidth]{00_stochastic.png}
-\caption{A simple mass-action model of dendritic transport}
+\caption{Model of microtubular transport.
+\textbf{(A)} Synaptic cargo, $u$, undergoes stochastic back-and-forth movements driven by opposing motor proteins.
+\textbf{(B)} Three example random walks on a cable representing the movement of individual cargoes.
+In a simple random walk, each movement is independent of previous movements (top panel); longer run lengths result from adding history-dependence to the model, such that each movement is likely to continue in the same direction as the previous step (bottom panel).
+\textbf{(C)} An ensemble of synaptic cargoes transported along the length of a neurite.
+\textbf{(D)} The concentration profile of transported cargo along a cable over time, simulated as 1,000 independent random walks. Simulations with (bottom) and without (top) history-dependence.
+\textbf{(E)} In the limit of many individual particles, the concentration of $u$ is modeled by the convection-diffusion partial differential equation.
+The parameters, $a$ and $b$, respectively scale the anterograde and retrograde rate of transport (see equation 1).
+\textbf{(F)} The convection-diffusion model provides a good fit for the simulations in panel D.
+}
 \end{center}
@@
 \includegraphics[width=0.9\columnwidth]{04_sushi_belt.png}
-\caption{Multiple strategies for transport in a model including nonuniform microtubular detachment/activation}
+\caption{Multiple strategies for transport in a model including nonuniform microtubular detachment/activation.
+\textbf{(A)} Schematic of microtubular transport model with irreversible detachment in a branched morphology.
+The localized degradation reactions ($u^{\star}_i \xrightarrow{d_i} \varnothing$) is omitted.
+\textbf{(B)} Multiple strategies for producing a desired distribution of activated biomolecules ($\tilde{u}^{\star}$).
+When the timescale of detachment/delivery is sufficiently slow, the distribution of cargo on the microtubules approaches a quasi-steady-state (transport step).
+This known distribution can then be transformed into the desired distribution for $\tilde{u}$ (detachment step).
+As long as these two steps are appropriately matched (blends of blue), then the desired distribution will be achieved (CA1 cell, right).
+\textbf{(C-E)} Normalized distributions of $u$ (red), $u^\star$ (blue), and $\tilde{u}^\star$ (black) as $t \rightarrow \infty$ for various strategies diagrammed in panel B (see circled red numbers).
+}
 \end{center}
@@
 \includegraphics[width=0.9\columnwidth]{05_heterosynaptic_ca1.png}
-\caption{Heterosynaptic and non-local interactions.
+\caption{Proximal synapses capture more cargo at the expense of distal synapses when detachment rates are n\"iavely increased.
+\textbf{(A)} Delivery of cargo to the distal apical zone with slow \textit{(left)} and fast detachment rates \textit{(right)}.
+The steady-state cargo distribution does not match the stimulated pattern when detachment is fast.
+\textbf{(B)} Tradeoff curves between non-specificity and convergence rate for two trafficking strategies (blue line, see Fig 4D; red line, see Fig 4C).
+\textbf{(C-D)} Same as \textbf{(A-B)} but for cargo delivery to the entire apical tuft.
 }
@@
 \includegraphics[width=0.9\columnwidth]{06_heterosynaptic_cable.png}
-\caption{Tradeoff between speed of consolidation and specificity of potentiation.}
+\caption{Producing speed and specificity for particular stimulation patterns does not extend to other patterns. Cargo begins on the left end and is transported to the right.
+\textbf{(A-C)} Steady-state cargo profiles (red) for three stimulation patterns (black arrows) along an unbranched cable.
+\textbf{(A)} When the timescale of detachment is sufficiently slow, cargo can be evenly distributed to the synapses regardless of their number and position.
+Transport parameters were set according to the procedure shown in figure 4D.
+\textbf{(B)} When detachment is n\"iavely increased (all rates multiplicatively scaled) a proximal bias in the steady-state distribution of cargo across all stimulation patterns.
+\textbf{(C)} Transport rate constants, $a_i$ and $b_i$, were tuned to optimize the distribution of cargo to six equally spaced synapses (top row); detachment rate constants were the same as in panel B.
+Changing the number of synapses (middle row) or the position of the synapses (bottom row) causes the unequal distribution of cargo to synapses.
+}
 \end{center}

### 2015-09-02 latex/paper.tex
new intro paragraph

@@
 Neurons often have complex dendritic trees, reflecting the dense and structured synaptic connectivity that supports nervous system function.
-In order to maintain appropriate connectivity, or to alter it as a means of encoding memories, numerous enzymes and macromolecules need to be transported along dendrites to the synapses that need them.
-How is this logistical problem solved at the subcellular level? And how might a biologically plausible solution constrain the behavior of synaptic plasticity `rules' and learning in general?
+In order to maintain appropriate connectivity, or to alter it in response to external events, numerous enzymes and macromolecules must be repeatedly replenished and distributed amongst a staggering number of synaptic contacts.
+A human might draw inspiration from FedEx to design a solution based on transport hubs and an addressing system.
+However, it is unclear how such a sophisticated scheme could be implemented on a microscopic scale in a flexible and robust manner.
+Futhermore, other biological transport systems (e.g. in ant colonies; \cite{Deneubourg_1990}) utilize more decentralized strategies based on simple local cues and decisions.
+Is it possible to achieve reliable transport in dendrites without an addressing system?
+What are the limitations and potential advantages of a decentralized transport system, and how might these constrain the behavior of synaptic plasticity `rules' and, by extension, circuit connectivity?
 
 Transport along dendrites is mediated by motor proteins (kinesins and dyneins) that walk along microtubules, carrying cargo at a rate that far exceeds passive diffusion [REFS].
-The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \cite{Mironov_2007,Wang_2009}.
+The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \citep{Mironov_2007,Wang_2009}.
 It is therefore conceivable that synaptic cargo transport is controlled in a distributed fashion, in which synapses that require cargo trigger its release from the motor protein complexes as they pass.

### 2015-09-23 latex/paper.tex
small paper edits

@@
 \usepackage{soul}
+\usepackage[utf8]{inputenc}
 
@@
 Neurons often have complex dendritic trees, reflecting the dense and structured synaptic connectivity that supports nervous system function.
-In order to maintain appropriate connectivity, or to alter it in response to external events, numerous enzymes and macromolecules must be repeatedly replenished and distributed amongst a staggering number of synaptic contacts.
-A human might draw inspiration from FedEx to design a solution based on transport hubs and an addressing system.
-However, it is unclear how such a sophisticated scheme could be implemented on a microscopic scale in a flexible and robust manner.
-Futhermore, other biological transport systems (e.g. in ant colonies; \cite{Deneubourg_1990}) utilize more decentralized strategies based on simple local cues and decisions.
-Is it possible to achieve reliable transport in dendrites without an addressing system?
-What are the limitations and potential advantages of a decentralized transport system, and how might these constrain the behavior of synaptic plasticity `rules' and, by extension, circuit connectivity?
+In order to maintain appropriate connectivity, or to alter it in response to external events, numerous enzymes and macromolecules must be repeatedly replenished and redistributed amongst a staggering number of synaptic contacts.
+Many human-designed transport and communication networks solve analogous problems by enumerating all possible destinations in an addressing system.
+A coarse addressing system might be implemented by localization sequences in the 3$'$-untranslated regions of mRNAs -- which, for example, control whether mRNA is sequestered in the nucleus or into dendrites \citep{Andreassi2009}.
+However, it is unclear whether a fine-scale dendritic addressing system is feasible or even desirable given the diversity of neural morphologies, the stochastic formation of synaptic contacts, and the changing demands of the system.
+
+Other biological systems (e.g. ant colonies) utilize decentralized transport strategies, which emerge from simple, local decisions made by a distributed population of agents \citep{Deneubourg_1990}.
+Such self-organizing systems often enjoy a number of advantageous properties -- including scalability, flexibility, and fault-tolerance -- and are therefore a topic of substantial current interest to roboticists and engineers \citep{Werfel2014,Rubenstein2014}.
+We asked how a decentralized transport system for synaptic cargo might be organized, ?
+How would a decentralized transport system be expected to behave, and how might constrain the behavior of synaptic plasticity `rules' and, by extension, circuit connectivity?
 
@@
 
-\subsection*{Microtubule Transport Model (Fig. 1)}
+\subsection*{Model of single-particle transport}
+
+Let $x_n$ denote the position of a particle along a 1-dimensional cable at timestep $n$.
+Let $v_n$ denote the velocity of the particle at timestep $n$; for simplicity, we assume the velocity can take on three discrete values, $v_n = \{-1,0,1\}$, corresponding to a discrete retrograde movement, pause, or anterograde movement.
+As a result, $x_n$ is constrained to take on integer values.
+In the simplest model, we assume that $v_n$ is drawn with fixed probabilities $\mathbf{p} = \{p_{-},p_0,p_+\}$.
+The update rule for position is:
+$$x_{n+1} = x_n + v_n$$
+$$v_{n+1} = \left\{\begin{matrix}
+-1 & \text{with probability } p_-\\ 
+0 & \text{with probability } p_0\\  
+1 & \text{with probability } p_+
+\end{matrix}\right.$$
+
+Another possibility is that the velocity is updated in a history-dependent manner.
+For example, if the motor was moving in an anterograde direction on the previous timestep, then it may be more likely to continue to moving in that direction in the next time step.
+To incorporate this possibility, we change the velocity update rule to follow \textit{conditional} probabilities:
+$$v_{n+1} = \left\{\begin{matrix}
+-1 & \text{with probability } p(-|v_n)\\ 
+0 & \text{with probability } p(0|v_n)\\  
+1 & \text{with probability } p(+|v_n)
+\end{matrix}\right.$$
+We can summarize all of these conditional probabilities in a table:
+\begin{center}
+  \begin{tabular}{ l | c  c  c }
+    & $v_n=-1$ & $v_n=0$ & $v_n=1$ \\
+    \hline
+    $v_{n+1} = -1$ & $p(-|-)$ & $p(-|0)$ & $p(-|+)$ \\ 
+    $v_{n+1} = 0$  & $p(0|-)$ & $p(0|0)$ & $p(0|+)$ \\ 
+    $v_{n+1} = 1$  & $p(+|-)$ & $p(+|0)$ & $p(+|+)$ \\
+    \hline
+  \end{tabular}
+\end{center}
+The extreme case of this model occurs when the velocity never changes: 
+\begin{center}
+  \begin{tabular}{ l | c  c  c }
+    & $v_n=-1$ & $v_n=0$ & $v_n=1$ \\
+    \hline
+    $v_{n+1} = -1$ & $1$ & $0$ & $0$ \\ 
+    $v_{n+1} = 0$  & $0$ & $1$ & $0$ \\ 
+    $v_{n+1} = 1$  & $0$ & $0$ & $1$ \\
+    \hline
+  \end{tabular}
+\end{center}
+We introduce a parameter $k \in [0,1]$ to linearly interpolate between this extreme case and the first model (i.e.
+with each column given by $\mathbf{p} = \{0.20,0.35,0.45\}$).
+The rest of the panels in the figure show individual runs, 5000 molecule simulations, and mass action approximations for $k=0.25$ and $k=0.5$.
+All particles start at $x_0 = 0$ with $v_{-1}$ chosen randomly.
+
+\subsection*{Model of bulk/mass-action transport}
 Transport in an unbranched cable (equation 1) leads to the following system of differential equations:
@@
 $$
-Similar systems result from branched mass-action models. The steady-state relationship in equation 5 can be immediately verified at either end of the cable:
+Similar systems result from branched mass-action models.
+The steady-state ratio of cargo in two neighboring compartments equals the ratio of transport rate constants (equation 2).
+This can be immediately verified at either end of the cable:
 $$
@@
 $$
-The same procedure can be iteratively applied down the cable to show that equation 5 holds globally.
-The same result can be shown in a branched tree morphology.
+Successively applying the same logic down the cable confirms the condition in equation 2 holds globally.
+A similar procedure (starting at the tips and moving in) can be applied to branched morphologies to prove the more general condition (equation 4).
+
+% The same result can be shown in a branched tree morphology.
 Here, each compartment has exactly one parent, but can have multiple children at branch points.
@@
 At steady-state, there is no net flux between $u_c$ and its children:
-$$
-\dot{u}_c = a u_p - b u_c + \underbrace{\sum_j (b_j u_j - a_j u_c)}_{= 0 \text{ , at ss}}
-$$
-Thus, we have:
-$$
-\dot{u}_c = a u_p - b u_c = 0 ~\Rightarrow~ \frac{u_p}{u_c} \Bigg |_{ss} = \frac{b}{a}
-$$
-To study how the system converges to steady-state, we can re-express the model as a matrix differential equation, $\mathbf{\dot{u}} = A \mathbf{u}$, where $\mathbf{u} = \left[ u_1, u_2, ...
-u_N \right]^T$ is the state vector, and $A$ is a matrix.
-For a general branched morphology, the matrix $A$ will be nearly tridiagonal, with off-diagonal elements corresponding to branch points; matrices in this form are called Hines matrices \citep{Hines_1984}.
+% $$
+% \dot{u}_c = a u_p - b u_c + \underbrace{\sum_j (b_j u_j - a_j u_c)}_{= 0 \text{ , at ss}}
+% $$
+% Thus, we have:
+% $$
+% \dot{u}_c = a u_p - b u_c = 0 ~\Rightarrow~ \frac{u_p}{u_c} \Bigg |_{ss} = \frac{b}{a}
+% $$
+
+It is helpful to re-express the model as a matrix differential equation, $\mathbf{\dot{u}} = A \mathbf{u}$, where $\mathbf{u} = \left[ u_1, u_2, ...
+u_N \right]^T$ is the state vector, and $A$ is the state-transition matrix.
+For a general branched morphology, $A$ will be nearly tridiagonal, with off-diagonal elements corresponding to branch points; matrices in this form are called Hines matrices \citep{Hines_1984}.
 For the simpler case of an unbranched cable, $A$ is tridiagonal:
@@
 
-The desired distribution, $\mathbf{\tilde{u}}$, is an eigenvector that spans the nullspace of $A$.
-All other eigenvalues $A$ are negative, which can be shown using the Gershgorin circle theorem.
+The desired steady-state distribution, $\mathbf{\tilde{u}}$, is an eigenvector that spans the nullspace of $A$.
+It is simple to show that all other eigenvalues $A$ are negative using the Gershgorin circle theorem; thus, the fixed point described by equations 2 and 4 is stable.
 The convergence rate is determined by the non-zero eigenvalue with smallest magnitude of $A$.
-We can increase the convergence rate (while still maintaining $\mathbf{\tilde{u}}$) by multiplying all rate constants by some common value.
+We can increase the convergence rate (while still achieving $\mathbf{\tilde{u}}$) by multiplying all rate constants by some common value.
 However, this trivial strategy ignores the fact that there are biophysical limits on how fast molecular motors can move.

### 2015-10-20 latex/paper-v3.tex
v5

--- 2015-09-23 latex/paper.tex
@@
-\documentclass[10pt]{wlpeerj}
+\documentclass[11pt]{wlpeerj}
 \usepackage{mathtools}
 \usepackage{soul}
-\usepackage[utf8]{inputenc}
+\usepackage{setspace}
+\doublespacing
 
-\title{Trafficking synaptic cargo in complex morphologies involves tradeoffs in speed and precision}
+\title{Trafficking synaptic cargo involves tradeoffs in speed and precision}
 
@@
 \begin{abstract}
-Long lived changes in synaptic strength underlie persistent memories and in many cases require activity dependent transcription of plasticity-related genes.
-A well-known problem is to understand how appropriate gene products, such as synaptic proteins and mRNAs, get trafficked to the synapses that require them in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many neurons.
-We develop a biophysically-rooted model of microtubule transport, and identify procedures that produce desired distributions of cargo to arbitrarily high precision.
-Importantly, these transport systems can be plausibly encoded by simple, localized biochemical reactions.
-The model predicts that the precise and flexible delivery of synaptic cargo requires the capture of synaptic cargo to occur on a slower timescale than the movement of cargo across the microtubule network.
-Thus, neurons must find a compromise between the specificity and speed with which synaptic materials are delivered and long-lived connectivity patterns are formed.
+Nervous system function depends on the appropriate development, maintenance, and plasticity of synaptic connectivity.
+In order to form and modify synaptic connections, organelles and molecular cargo need to be trafficked from the site of synthesis to the vicinity of the synapse.
+An open question is how synaptic cargo can be delivered to appropriate synapses in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many neurons.
+We develop a biophysically-rooted yet general model of microtubule transport that captures known mechanistic properties of intracellular transport.
+In spite of the assumption that molecular transport responds only to local chemical cues, we show that arbitrarily complex distributions of cargo can be achieved.
+However, the model reveals important tradeoffs that can be tested experimentally.
+We find that precise and flexible delivery of synaptic cargo requires the capture of synaptic cargo to occur on a slower timescale than the movement of cargo across the microtubule network.
+Tuning the transport parameters reveals that optimal solutions exist for specific distributions of synapses, but these solutions sensitively depend on the location as well as the number of synapses, suggesting that biological neurons face a compromise between flexibility of connectivity and efficacy in regulating synaptic function.
+
 \end{abstract}
-
-% OLD ABSTRACT:
-%Long lived changes in synaptic strength underlie persistent memories and in many cases require activity dependent transcription of plasticity-related genes.
-%A well-known problem is to understand how appropriate gene products, such as synaptic proteins and mRNAs, get trafficked to the synapses that require them in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many kinds of neuron.
-%Using a simple, biophysically-rooted model of microtubule transport we show that rapid delivery of plasticity-related cargo entails loss of specificity in the synapses that eventually receive it.
-%The model predicts that neurons must balance the biochemical parameters that control trafficking to find a compromise between the precision and speed with which long-lived connectivity patterns are formed.
-%Conversely, imbalances in transport parameters could lead to hypo-, or hyperconnectivity as well as loss of precision in associative memory, identifying a potential role for transport machinery in brain disorders that exhibit connectivity and plasticity phenotypes.
 
@@
 Neurons often have complex dendritic trees, reflecting the dense and structured synaptic connectivity that supports nervous system function.
-In order to maintain appropriate connectivity, or to alter it in response to external events, numerous enzymes and macromolecules must be repeatedly replenished and redistributed amongst a staggering number of synaptic contacts.
-Many human-designed transport and communication networks solve analogous problems by enumerating all possible destinations in an addressing system.
-A coarse addressing system might be implemented by localization sequences in the 3$'$-untranslated regions of mRNAs -- which, for example, control whether mRNA is sequestered in the nucleus or into dendrites \citep{Andreassi2009}.
-However, it is unclear whether a fine-scale dendritic addressing system is feasible or even desirable given the diversity of neural morphologies, the stochastic formation of synaptic contacts, and the changing demands of the system.
+In order to maintain appropriate connectivity, or to alter it in response to changes in circuit activity, numerous enzymes and macromolecules must be repeatedly replenished and redistributed amongst a staggering number of synaptic contacts.
+Although the molecular machinery that solves this logistical problem is known in increasing detail [REFS], there are few attempts to quantify broadly how subcellular transport processes might constrain a neuron's ability to regulate its connectivity and synaptic function.
 
-Other biological systems (e.g. ant colonies) utilize decentralized transport strategies, which emerge from simple, local decisions made by a distributed population of agents \citep{Deneubourg_1990}.
-Such self-organizing systems often enjoy a number of advantageous properties -- including scalability, flexibility, and fault-tolerance -- and are therefore a topic of substantial current interest to roboticists and engineers \citep{Werfel2014,Rubenstein2014}.
-We asked how a decentralized transport system for synaptic cargo might be organized, ?
-How would a decentralized transport system be expected to behave, and how might constrain the behavior of synaptic plasticity `rules' and, by extension, circuit connectivity?
-
-Transport along dendrites is mediated by motor proteins (kinesins and dyneins) that walk along microtubules, carrying cargo at a rate that far exceeds passive diffusion [REFS].
-The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \citep{Mironov_2007,Wang_2009}.
-It is therefore conceivable that synaptic cargo transport is controlled in a distributed fashion, in which synapses that require cargo trigger its release from the motor protein complexes as they pass.
-This idea is a variant of the well-known synaptic tagging hypothesis \citep{Frey_1997}, which proposes that synapses produce a biochemical `tag' that signals a requirement for synaptic building blocks as part of the plasticity process.
-
+Transport along dendrites is mediated by motor proteins (kinesins and dyneins) that walk along microtubules, carrying cargo at a rate that far exceeds passive diffusion \citep{Smith_2001}\hl{Others?}.
+The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \citep{Mironov_2007,Wang_2009}, that are caused by synaptic activity or locally released growth factors from other cells.
+In this way, the proteins, scaffolding molecules and receptors that make up a postsynaptic site can be made available to alter an existing synapse or assemble a new synapse in the vicinity of a presynaptic partner.
 Not all aspects of synaptic plasticity require delivery of cargo from the soma.
 For example, some forms of long-term potentiation (LTP) depend on local protein synthesis and can function in isolated dendrites [REFS].
-However, in the long run, the mRNAs and the machinery that supports such plasticity needs to be replenished.
-Moreover, many long-lasting forms of synaptic plasticity rely on anterograde transport of mRNAs \citep{Kandel_2001,Puthanveettil_2008} and specific mRNAs are known to be selectively transported to regions of heightened synaptic activity \citep{Steward_1998,Steward_2001,Moga_2004} or to developing synaptic contacts \citep{Lyles_2006}.
-The interplay between global distribution and local plasticity mechanisms therefore demands attention.
+Nonetheless, components originating in the soma need to find their way to synapses in the first place, and in the long run, the mRNAs and the machinery that supports local biosynthesis needs to be replenished.
+Moreover, many long-lasting forms of synaptic plasticity are known to depend on anterograde transport of mRNAs \citep{Kandel_2001,Puthanveettil_2008} and specific mRNAs are known to be selectively transported to regions of heightened synaptic activity \citep{Steward_1998,Steward_2001,Moga_2004} or to developing synaptic contacts \citep{Lyles_2006}.
+These observations fit with the well-known synaptic tagging hypothesis \citep{Frey_1997}, which proposes that synapses produce a biochemical `tag' that signals a requirement for synaptic building blocks as part of the plasticity process.
 
-From simple assumptions about the dynamics of active dendritic transport we develop a model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies.
-Within this framework, we identify several ways in which local biochemical mechanisms can be orchestrated to produce arbitrarily complex distributions of molecular cargo.
-In addition to addressing the logistical challenges of dendritic transport, we identify several constraints the precision, flexibility, and speed of cargo delivery inherent to this model.
+The distribution of molecular cargo is partially controlled by a coarse addressing system in the localization sequences of 3$'$-untranslated regions of mRNAs -- which, for example, control whether mRNA is sequestered in the nucleus or into dendrites \citep{Andreassi2009}.
+However, it is unclear whether a fine-scale, centralized addressing system, as exemplified by human-designed transport systems, is feasible or even desirable for neurons to implement.
+Other biological systems (e.g. ant colonies) utilize decentralized transport strategies, which emerge from simple, local decisions made by a distributed population of agents \citep{Deneubourg_1990}.
+Such self-organizing systems often enjoy a number of advantageous properties -- including scalability, flexibility, and fault-tolerance -- and are therefore a current topic of substantial interest to engineers \citep{Werfel2014,Rubenstein2014}.
 
-\hl{}
+%From simple, experimentally verifiable assumptions about the dynamics of active dendritic transport we develop a minimal biophysical model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies.
+We develop a minimal biophysical model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies, and show how local biochemical signals can modify the movement and/or release of cargo to produce complex spatial patterns in a self-organizing fashion.
+However, the decentralized transport strategies we explore face unavoidable tradeoffs between the speed and precision of cargo delivery.
+Tuning the transport parameters reveals that while optimal solutions exist to balance this tradeoff, these solutions sensitively depend on the location as well as the number of synapses, suggesting that biological neurons must compromise between flexibility in connectivity and their ability to precisely regulate synaptic function.
 
@@
 
-\begin{figure}[!tb]
+\hl{Activation of synaptic receptors triggers downstream signalling cascades that can alter global gene expression [ref Greenberg, Bading, others] as well as modulating the trafficking and metabolism of molecular cargo locally [REFS].
+[more on this] \textbf{move to intro?}}
+
+Transport along microtubules is mediated by kinesin and dynein motors, which mediate anterograde and retrograde transport, respectively \citep{Hirokawa_2010,Gagnon_2011}.
+Cargo is often simultaneously bound to both forms of motor protein, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Hancock_2014,Buxbaum_2014b} (Fig.
+1A).
+
+To obtain a general model that can accommodate variations in the biophysical details, we consider microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006,Bressloff_2009,Newby_2010}.
+For each time step, the cargo moves forwards, backwards, or remains in the same place with different probabilities that together sum to 1.
+In the simplest model, the probabilities associated with each movement are fixed and independent across each time step, with the forward jump more probable than a reverse jump, leading to a biased random walk (Fig.
+1B, top panel).
+A potentially more realistic model (see, e.g., \cite{Soundararajan_2014}) incorporates hysteresis into the biased random walk (see Methods).
+In this case, the cargo is more likely to continue in the same direction as it moved during the previous time step, leading to extended runs in one direction along the microtubule (Fig.
+1B, bottom panel).
+
+\begin{figure}[!t]
 \begin{center}
@@
 
-Transport along microtubules is mediated by kinesin and dynein motors, which mediate anterograde and retrograde transport, respectively \citep{Hirokawa_2010,Gagnon_2011}.
-Cargo is often simultaneously bound to both forms of motor protein, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Hancock_2014,Buxbaum_2014b} (Fig.
-1A).
-
-To obtain a general model that can accommodate variations in the biophysical details, we consider microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006,Newby_2010,Bressloff_2009}.
-For each time step, the cargo moves left, right, or remains in the same place.
-In the simplest model, the probabilities associated with each movement are fixed and independent across each time step (Fig. 1B, top panel).
-A potentially more realistic model incorporates \textit{hysteresis} into the biased walk (see Methods).
-In this case, the cargo is more likely to continue in the same direction as it moved on the previous time step (Fig.
-1B, bottom panel; see, e.g., \cite{Soundararajan_2014}).
-
 While the position of individual cargoes can be highly stochastic, the net movement of a population of cargoes (Fig. 1C) is predictable.
 Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) hysteresis.
-In both cases, these simulations can be well-fit by an convection-diffusion partial differential equation (Fig.
+For the simple biased random walk and for the random walk with hysteresis, these simulations can be well-fit by an advection-diffusion equation (Fig.
 1E-F), which is easier to analyze because it is deterministic and contains fewer variables \citep{Smith_2001}.
 
-The convection-diffusion equation can be numerically simulated by discretizing a dendritic tree into small compartments, and considering the movement of cargo between neighboring compartments as a chemical reaction with first order kinetics.
+We model transport using the advection-diffusion equation with spatially non-uniform drift and diffusion coefficients.
+As an approximation, we discretized a dendritic tree into small compartments, and modeled the movement of cargo between neighboring compartments as reactions with first order kinetics.
 In an unbranched cable with $N$ compartments, the mass-action model is:
@@
 2A).
+The mass-action scheme provides a flexible way to model local changes in transport rates, and is very tractable to mathematical analysis and numerical simulation.
 
-\hl{MOVE THIS PARAGRAPH TO METHODS/DISCUSSION?} A central assumption of this model is that the movement of molecules between neighboring compartments is a stochastic and memoryless process.
-This assumption is reasonable if the \hl{run length (jargon?)} of molecular motors is comparable to the size of the compartments; this appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, thought not necessarily all \citep{Dynes_2007} circumstances (see Discussion).
+A central assumption of mass-action description of this model is that the net movement of molecules between neighboring compartments is a stochastic and memoryless process.
+This assumption is reasonable for cargoes that change direction often; specifically, on a length scale comparable to the size of the compartments.
+This appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, though not necessarily all \citep{Dynes_2007,Soundararajan_2014} circumstances.
 In simulations, we observed that this model was not very sensitive to violations of this assumption; the population dynamics of cargoes with substantial run lengths could still be well-fit by this class of models (Fig.
@@
 
-\subsection*{A simple rule achieves desired spatial distributions of cargo}
+\subsection*{A simple transport mechanism distributes cargo according to demand}
 
-The exchange of $u$ between neighboring compartments approaches an equilibrium/steady-state ($ss$) distribution over time. In an unbranched cable, this occurs precisely when:
+We next show how the mass-action model can be easily solved to produce complex distributions in the concentration of cargo along a dendrite
+The exchange of $u$ between neighboring compartments approaches an equilibrium/steady-state ($ss$) distribution over time. In an unbranched dendrite, this occurs precisely when:
 \begin{equation}
@@
 
-\hl{MOVE THIS PARAGRAPH TO DISCUSSION OR DELETE?} These rules could be locally implemented by simple biochemical reaction networks.
-Consider the cytoplasmic calcium concentration, $[ca]_i$, as a candidate second messenger.
+Together, this analysis shows that by slowing or biasing local trafficking rates, arbitrary distributions of cargo can be achieved over time.
+Local trafficking rates, in turn, can be modulated by a simple biochemical reaction resulting from synaptic activation or local release of a growth factor.
+We can consider the local cytoplasmic calcium concentration, $[ca]_i$, as an candidate second messenger.
 Increases in $[ca]_i$ simultaneously arrest anterograde and retrograde microtubular transport \citep{Wang_2009}.
@@
 
+Thus, in principle, local calcium transients that serve to arrest transport could provide a mechanism for matching cargo concentration to an arbitrarily complicated distirbution over a dendritic tree.
 To test the plausibility of this model in a complex morphology, we extended an existing multi-compartment model of a CA1 pyramidal neuron \citep{Migliore_2012}.
@@
 For example, newly synthesized proteins must be delivered to synapses within $\sim$1 hour to support long-term potentiation in CA1 pyramidal cells \citep{Frey_1997,Frey_1998}.
-It is therefore of substantial interest to examine factors that influence the speed of transport in the model.
+It is therefore important to know what factors influence the rate at which the distribution of cargo matches its demand profile across the whole dendritic tree.
 
@@
 
-Figure 3 illustrates and analyzes this intuition in a simple three compartment model.
+Figure 3 illustrates and analyzes a bottleneck in a simple three compartment model.
 The two compartments on the end of the cable have the same desired level, $\tilde{u}_1 = \tilde{u}_3$; the middle compartment acts as a bottleneck when $\tilde{u}_2$ is very small (Fig. 3A).
@@
 Figure 3B shows that the convergence rate slows dramatically as $\epsilon$ decreases.
-This can be can be analyzed using basic linear systems theory; the convergence rate is given by the non-zero eigenvalue with smallest magnitude, which can be thought of as a rate-limiting step or process for the system (Methods, Supp.
+This can be can be solved by analysing the corresponding system of ordinary differential equations.
+The convergence rate is determined by the non-zero eigenvalue with smallest magnitude, which can be thought of as a rate-limiting step or process for the system (Methods, Supp.
 Fig.
@@
 Simulations confirmed this analysis and showed that the convergence rate diverges to infinity as $\epsilon$ approaches zero (Fig. 3C).
+\hl{I think the epsilon goes to zero stuff can be omitted, or at the very least stated more tersely - if the transport rate is zero anywhere it is obvious that it takes forever to converge}
 
@@
 To illustrate this in the model CA1 cell, we characterized the time course of transport to the distal apical dendrite (stimulating stratum lacunosum/moleculare), proximal apical dendrite (stimulating stratum radiatum), entire apical dendrite (stimulating both layers), and entire cell (seizure).
-Interestingly, the model converged more slowly to distal input alone, than to paired distal and proximal input, or to an entirely uniform distribution (Fig.
+Notably, the model converges more slowly to distal input alone, than to paired distal and proximal input, or to an entirely uniform input distribution (Fig.
 3F).
@@
 
-The models above present a simple hypothesis for controlling molecular transport along an intricate system of microtubules.
-While certain types of molecular cargo stay on the microtubule network (e.g. mitocondria), others detach from the microtubules after a reaching a desired location.
-For example, dendritic mRNAs are transported within densely-packed granules, and can be locally released following granule disassembly \citep{Krichevsky_2001,Buxbaum_2014a}.
-We model the detachment from the microtubule network as an irreversible process, and include a compartment-specific degradation reaction. This results in the following mass-action model:
+So far we have considered how local signals can generate a specific distribution of molecular cargo along a dendrite by modulating the rate of molecular motors. However,
+while certain types of molecular cargo stay on the microtubule network (e.g. mitocondria), many kinds of cargo must detach from the microtubules in order to be used at their final location.
+For example, dendritic mRNAs are transported along microtubules within densely-packed granules, and are released following granule disassembly \citep{Krichevsky_2001,Buxbaum_2014a}.
+In this case, and in others where the cargo is disassembled or sequestered, it is reasonable to model detachment from the microtubule as an irreversible process, followed by an eventual degradation.
+We therefore model the detachment from the microtubule in the mass-action scheme as having a unidirectional rate constant, and include a compartment-specific degradation reaction.
+This results in the following scheme:
 \begin{equation}
@@
 
-This model admits a spectrum of strategies for controlling the distribution of molecular cargo (Fig. 4B).
-One strategy (Fig.
-4C) is to choose microtubular trafficking rates such that $\tilde{u}$ exactly matches $\tilde{u}^\star$, and choose the detachment rate constants to be spatially uniform ($c_i =$ constant).
-Figure 4C shows that the desired spatial distribution is achieved both along the microtubules (red line) and for the detached/activated cargo (blue line).
+This model has a continuum of strategies for controlling the eventual distribution of molecular cargo (Fig. 4B).
+At one extreme of this continuum (Fig.
+4C), microtubular trafficking rates are constrained such that $\tilde{u}$ exactly matches $\tilde{u}^\star$, and the detachment rate constants are spatially uniform ($c_i =$ constant).
+In this case, Figure 4C shows that the desired spatial distribution is achieved both along the microtubules (red line) and for the detached/activated cargo (blue line).
 
-Figure 4D shows the strategy on the other end of the spectrum.
-It begins by uniformly distributing cargo along the microtubules, and locally detaches cargo at a rate proportional to the desired level ($c_i \propto \tilde{u}^\star_i$).
+The other extreme case is where trafficking rates are fixed along the microtubules, but cargo detaches in response to local signals at a rate proportional ($c_i \propto \tilde{u}^\star_i$).
+Figure 4D shows this strategy.
 Unlike the first solution, this strategy avoids the transport bottlenecks examined in Figure 3, and can achieve target patterns with  $\tilde{u}^\star$ equal to zero in certain compartments by setting $c_i = 0$.
@@
 
-\subsection*{Non-specific cargo delivery occurs when time scales aren't separated}
+\subsection*{Non-specific cargo delivery occurs when trafficking and detachment occur on similar timescales}
 
-We have thusfar considered models that produce a desired distribution of cargo to arbitrarily high precision.
-However, real neurons probably tolerate some sloppiness in synaptic trafficking (or even utilize it as a substrate for complex plasticity rules).
-Thus, we examined the consequences of relaxing the separation of time scales between transport and detachment.
-In general, this improves the speed at which cargoes are delivered to synapses, but decreases the accuracy of delivery.
+So far we have considered models that distribute cargo to high precision across a dendritic tree and found that high precision can be achieved when detachment is sufficiently slow relative to trafficking.
+However, biological neurons are unlikely to require perfect matching between demand and distribution of cargo and may therefore tolerate loss of precision in order to speed up delivery globally.
+We therefore examined the consequences of relaxing the separation of time scales between transport and detachment.
+%In general, this improves the speed at which cargoes are delivered to synapses, but decreases the accuracy of delivery.
 
@@
 
-To appreciate this, consider an experiment where distal synaptic inputs on the apical tuft are stimulated (Fig. 5A).
+Returning to the model of Figure 4, we consider a scenario where distal synaptic inputs on the apical tuft are stimulated (Fig. 5A).
 If the average detachment rate constants are sufficiently slow, then, as before, cargo is delivered selectively to the stimulated region (Fig. 5A, left).
@@
 We refer to this as a ``non-specific'' delivery of cargo, since cargo is not selectively delivered to the stimulated sites.
+Thus, although speeding up detachment relative to transport improves the overall rate at which cargoes are delivered to synapses, but this comes at the cost of decreased accuracy of delivery.
 \hl{For this stimulation pattern, non-specificity might induce on-the-path synaptic plasticity; a possibility that has some experimental evidence} \citep{Han_2013}.
@@
 
-Different patterns of non-specificity occur for other stimulation patterns.
+The pattern of non-specific delivery is stimulation-dependent.
 When the entire apical tree is stimulated, fast detachment can result in a complete occlusion of cargo delivery to distal synaptic sites (Fig. 5C).
@@
 This is due to the lack of a bottleneck, and the fact that the uniform trafficking strategy initially sends cargo to the basal dendrites where it is not released.
+Together, these results show that an increase in the efficiency of synaptic cargo delivery comes at the cost of loss of specificity and that the final destination of mis-trafficked cargo depends on the pattern of stimulation.
+We next asked whether we can tune the kinetic parameters of the transport mechanism to find an ideal compromise between precision and trafficking efficiency.
 
 \subsection*{Transport can be optimized for both speed and precision for a given stimulation pattern}
-
-\hl{have detachment rate be tunable by amount of stuff present???}
 
@@
 
-We examined this possibility in a reduced model --- an unbranched cable --- so that we could develop simple heuristics that precisely achieve a desired distribution of cargo (more complex, \textit{ad hoc}, heuristics could be developed for complex morphologies).
+We examined this possibility in a simpler model --- an unbranched cable --- so that we could develop simple heuristics that precisely achieve a desired distribution of cargo while minimizing the convergence time.
 In the reduced model, cargo begins on the left end of the cable and is transported to a number of synaptic sites, each of which is modeled as a double-exponential curve.
@@
 \textbf{(A-C)} Steady-state cargo profiles (red) for three stimulation patterns (black arrows) along an unbranched cable.
+The dotted black line corresponds to the `target' steady-state level at each synapse.
 \textbf{(A)} When the timescale of detachment is sufficiently slow, cargo can be evenly distributed to the synapses regardless of their number and position.
@@
 Changing the number of synapses (middle row) or the position of the synapses (bottom row) causes the unequal distribution of cargo to synapses.
+\textbf{(D)} Tradeoff curves between non-specificity and convergence rate for six evenly spaced synapses (top row of A-C).
+The curve shifts to the left and becomes non-monotonic as the anterograde bias ($\beta$) increases.
+\textbf{(E)} Tradeoff curves for two levels of anterograde bias on multiple simulations; for each simulation six synapse positions were drawn from random uniform distribution over the length of the cable.
+\textbf{(F)} Same as panel E, except each the number of synapses was randomly chosen between 3 to 9 for each simulation.
 }
@@
 We then hand-tuned the transport rate constants to deliver equal cargo to six evenly spaced synaptic sites (top row of Fig. 6C).
-Specifically, we increased the anterograde rate constants ($a_i$) and decreased the retrograde rate constants ($b_i$) by a decreasing linear function of position so that $a_N = b_N$ at the right side of the cable (see Methods).
+Specifically, we increased the anterograde rate constants ($a_i$) and decreased the retrograde rate constants ($b_i$) by a decreasing linear function of position so that $a_{N-1} = b_{N-1}$ at the right side of the cable.
+On the left end of the cable, we set $a_1 = 0.5 + \beta$ and $b_1 = 0.5 - \beta$, where $\beta$ is the parameter controlling anterograde bias
 Intuitively, this pushes cargo past the proximal synaptic sites more quickly, canceling out the exponential delivery bias induced by fast detachment.
@@
 A microscope image of a typical neuronal dendritic tree hints at the complex logistical task that the neuron must solve to maintain synapses and alter them, as appropriate, during development and learning.
-Synapses, such as the extensively-studied excitatory synapses of the mammalian nervous system, comprise hundreds of different proteins, including receptors, structural and anchoring proteins, and cytosolic signalling enzymes [REFs].
+Synapses, such as the extensively-studied excitatory synapses of the mammalian nervous system, comprise hundreds of different proteins, including receptors, structural and anchoring proteins, and cytosolic signaling enzymes \citep{Liu2014,Lassek2015}.
 How do these components find their way to the synapse, and how do synapses that have varying demands for these components receive an appropriate supply?
 
-Local protein synthesis near synaptic sites offers an elegant solution to this problem.
-Many mRNAs for synaptic proteins are distributed in dendrites, along with ribosomes and translational regulation machinery that can provide new proteins as they are needed [REFs].
-However, these components need to be appropriately distributed to begin with and on a long timescale their distribution needs to be maintained.
-On the other hand, some forms of long-term synaptic plasticity have a transcription-dependent component, suggesting that somatic biosynthesis and dendritic trafficking are important for maintaining and controlling synaptic connectivity in addition to local mechanisms.
+A large and diverse corpus of research speaks to this question, and many reviews have crystallized, in words, a two-step model in which molecular cargo first samples the dendritic arbor by a noisy walk, before its eventual release or capture \citep{Welte2004,Doyle_2011,Buxbaum_2014b,Buxbaum2015}.
+Both stages of transport are thought to be influenced by localized signaling pathways, rather than being pre-determined by a precise molecular address tagged in the soma.
+The signaling pathways affecting transport require further characterization and discovery; candidate second-messengers include calcium \citep{Wang_2009}, ADP \citep{Mironov_2007}, and microtubule-associated proteins \citep{Soundararajan_2014}.
 
-We examined simple models of microtubular transport to investigate how such a global network can be organized and controlled in complex neuronal morphologies.
-Previous models of microtubular-based transport have examined systems with spatially uniform rates of anterograde and retrograde transport \citep{Smith_2001,Bressloff_2006}.
-We hypothesized that complex spatial patterns could emerge by relaxing this assumption.
-One might na\"ively expect that elaborately branched morphologies obfuscate the relationship between these local mechanisms and the global distribution of molecular cargo.
-We showed that the relationship is actually quite simple: the steady-state ratio between neighboring compartments is the reciprocal ratio of the trafficking rate constants connecting those compartments.
+We aimed to examine the validity and biological consequences of these conceptual models in computational and theoretical detail, while remaining agnostic to biophysical parameters that require further study.
+A primary question we asked was whether a transport system based on purely local rules was feasible, or whether a complex global addressing system was required.
+One might na\"ively expect that elaborately branched dendritic morphologies obfuscate the relationship between local mechanisms and the global distribution of molecular cargo.
+However, we showed that local rules can produce arbitrarily precise and flexible cargo delivery provided that the release of cargo occurs on a slow enough timescale.
+Intuitively, this requirement means that the cargo have time to sample the dendritic tree for potential delivery sites \citep{Welte2004}.
 
-Local activity signals provide a means to sequester dendritic cargo as it passes a synapse, providing a way for plasticity-inducing synaptic stimulation to `tag' a synapse.
-Direct evidence of activity-dependent arrest \citep{Soundararajan_2014} and accumulation \citep{Krichevsky_2001,Buxbaum_2014a} of mRNAs and other actively transported biomolecules suggests that the kind of mechanism we studied here is involved in regulating synapses in parallel with local synthesis mechanisms.
-We are agnostic about the precise identity of the activity signal that controls transport and sequestration, but note that experiments have shown that local calcium \citep{Wang_2009} and ADP \citep{Mironov_2007}, alter anterograde and retrograde transport rates.
-Similarly, experimental data indicate that degradation of mRNA can be spatially heterogeneous and activity-dependent \citep{Farris_2014}.
-Incorporating these additional processes into the model created new possibilities for molecular trafficking; the same expression pattern can be achieved by nonuniform microtubular transport followed by uniform release or from uniform transport followed by nonuniform release (Fig.
+Importantly, the spatial sampling of cargo need not occur in a uniform or unbiased manner.
+We showed that the same distribution of cargo could be achieved by (a) nonuniform microtubular transport followed by uniform release, (b) from uniform transport followed by nonuniform release, or (c) a combination of these strategies (Fig.
 4).
+Biologists should consider that dendritic transport may be better understood as a family of strategies, rather than a single mechanism or procedure.
+For example, \cite{Kim_2015} identified three mRNAs that were uniformly distributed throughout cultured \textit{Aplysia} sensory neurons, but were targeted to synapses at the level of protein expression by localized translation.
+In contrast, the nonuniform expression of \textit{Arc} mRNA is closely matched to the pattern of Arc protein \citep{Farris_2014, Steward_2015}.
+Even the same molecular cargo can show diverse movement statistics in single-particle tracking experiments \citep{Dynes_2007} \hl{Others?}.
 
-There is experimental evidence for both strategies.
-\cite{Kim_2015} identified three mRNAs that were uniformly distributed throughout cultured \textit{Aplysia} sensory neurons, but were targeted to synapses at the level of protein expression by localized translation.
-In contrast, the nonuniform expression of \textit{Arc} mRNA is closely matched to the pattern of Arc protein \citep{Farris_2014, Steward_2015}.
+Different transport strategies might be tailored for different constraints or purposes.
+One experimentally testable prediction of the model is that bottlenecks can arise when cargo is transported nonuniformly; specifically when distal regions require high levels of cargo, while proximal regions require low levels (Fig.
+3).
+Uniformly distributing cargo and relying on local capture circumvents this problem, leading to faster convergence for certain target distributions of cargo.
+An additional consideration, not examined in detail here, is whether the distribution of cargo needs to be stable over long time periods or be dynamic and responsive to changes in synaptic input.
+We also focused our analysis on the transport of transiently expressed cargo (e.g.
+factors produced in response to high synaptic input), rather than cargo that is constitutively expressed and, in some cases, differentially captured or synthesized across the dendritic tree \hl{(CITE)}.
+However, much of our analysis would extend to this case.
 
-Each of these transport strategies might be tailored for different constraints or purposes.
-For example, a uniform mRNA profile could facilitate shifts in the protein expression pattern, since the changing the pattern of local translation is presumably faster than re-distributing the mRNA.
-In other cases, it might be undesirable to rapidly shift protein expression based on transient changes to the neuron or circuit; controlling expression at the level of mRNA might prevent this.
-We showed that it is possible to interpolate between these two strategies (Fig. 4E), which might allow neurons to trade off between the relative advantages of each.
+The slow delivery/capture of cargo can produce a well-behaved and predictable transport system that can be flexibly tuned by simple local mechanisms and is not sensitive to the complex geometry of the neuron.
+Mathematically, this regime occurs when the system contains two separated timescales, and the distribution of cargo along the microtubules approaches a quasi-steady-state.
+However, because the transport of certain cargoes is time-sensitive \citep{Frey_1997,Frey_1998}, we asked whether the model could maintain precise delivery while relaxing the restriction of slow detachment.
+We found that increasing the rate of detachment produces a proximal bias in the delivery of cargo; this behavior, while intuitive at a high level, is complex and difficult to analytically characterize in complex morphologies.
+Thus, the family of models based on quasi-steady-state approximation predicts a tradeoff between the speed of cargo delivery and the specificity of transport.
 
-FRX - in this disease there is aberrantly high translation of mRNAs. This is like a high sequestration rate. Leads to higher connectivity but perhaps lower specificity.
+We then asked whether a different family of models might circumvent this tradeoff by globally tuning the anterograde and retrograde movement rates.
+Inspired by studies showing that a directional bias in transport can be induced by changing the complement of motor proteins \citep{Kanai2004,Amrute2012}, and that such a change might be induced at the soma in response to synaptic activity \citep{Puthanveettil_2008}, we increased the anterograde transport rates in a simple model to precisely overcome the proximal bias in cargo delivery, and therefore provide both fast and precise transport for a particular target distribution of cargo (Fig.
+6).
 
-Other assumptions of the mass-action model - Second, the model assumes are many copies of $u$ in each compartment.This allows us to approximate the mass as a continuous variable, and the dynamics of the system as deterministic.Third, the number of molecular motors and capacity of the microtubules is not saturated by the level of $u$ in any compartment.
-This means that the rate of transport from compartment A to compartment B linearly increases with the amount of $u$ in compartment A.
+There are three important facts to emphasize about this globally tuned solution.
+First, we achieved precise delivery when the anterograde rate constants were tuned non-uniformly over the cable; specifically, we used a linearly decreasing profile (see \textit{Methods}).
+Simply changing the composition of motor proteins \citep{Amrute2012} may be insufficient to induce a spatial profile in transport bias; non-uniform modulation of the microtubule network or expression of microtubule-associated proteins provide potential mechanisms \citep{Kwan2008,Soundararajan_2014}.
+While these biophysical details remain speculative, single-particle tracking studies could empirically test the existence of spatial gradients in anterograde movement bias.
+
+Secondly, it should be emphasized that the linear, decreasing gradient in anterograde bias used in figure 6 is not a general prediction for all neuronal morphologies or detachment/capture profiles.
+Introducing an anterograde bias can cause the accumulation of cargo at the tips of short branches, proximal to the soma (data not shown).
+While the optimal re-tuning of transport rate constants is be morphology-dependent, the qualitative prediction that anterograde bias should decrease as a function of distance to the soma is likely general.
+Intuitively, the anterograde bias should be low near the tips of the dendritic branches to prevent the accumulation of cargo.
+However, other mechanisms, not modeled in this study, might prevent this accumulation \citep{Soundararajan_2014}.
+
+Finally, and perhaps most importantly, the optimal re-tuning of anterograde transport bias depends on the number and pattern of delivery sites (see Fig.
+6).
+If neurons are able to consistently circumvent the tradeoff between delivery speed and precision, then the model predicts that they must globally re-tune transport rates in a pattern-specific manner.
+
+\hl{Need a nice final paragraph to tie it all together}
 
 \section*{Methods}
+
+All simulation code is available on: https://github.com/ahwillia/Williams-etal-Synaptic-Transport
 
@@
 As a result, $x_n$ is constrained to take on integer values.
-In the simplest model, we assume that $v_n$ is drawn with fixed probabilities $\mathbf{p} = \{p_{-},p_0,p_+\}$.
+In the memoryless transport model (top plots in Fig.
+1B, 1D, and 1F), we assume that $v_n$ is drawn with fixed probabilities on each step.
 The update rule for position is:
@@
 
-Another possibility is that the velocity is updated in a history-dependent manner.
-For example, if the motor was moving in an anterograde direction on the previous timestep, then it may be more likely to continue to moving in that direction in the next time step.
-To incorporate this possibility, we change the velocity update rule to follow \textit{conditional} probabilities:
+We chose $p_- = 0.2$, $p_0 = 0.35$ and $p_+ = 0.45$ for the illustration shown in Figure 1.
+For the model with history-dependence (bottom plots in Fig.
+1B, 1D, and 1F), the movement probabilites at each step depend on the previous movement.
+For example, if the motor was moving in an anterograde direction on the previous timestep, then it is more likely to continue to moving in that direction in the next time step.
+In this case the update rule utilizes \textit{conditional} probabilities:
 $$v_{n+1} = \left\{\begin{matrix}
@@
 \end{matrix}\right.$$
-We can summarize all of these conditional probabilities in a table:
+
+In the extreme case of history-dependence, the particle always steps in the same direction as the previous time step.
 \begin{center}
@@
     \hline
-    $v_{n+1} = -1$ & $p(-|-)$ & $p(-|0)$ & $p(-|+)$ \\ 
-    $v_{n+1} = 0$  & $p(0|-)$ & $p(0|0)$ & $p(0|+)$ \\ 
-    $v_{n+1} = 1$  & $p(+|-)$ & $p(+|0)$ & $p(+|+)$ \\
+    $p(v_{n+1} = -1)$ & $1$ & $0$ & $0$ \\ 
+    $p(v_{n+1} = 0)$  & $0$ & $1$ & $0$ \\ 
+    $p(v_{n+1} = 1)$  & $0$ & $0$ & $1$ \\
     \hline
@@
 \end{center}
-The extreme case of this model occurs when the velocity never changes: 
-\begin{center}
-  \begin{tabular}{ l | c  c  c }
-    & $v_n=-1$ & $v_n=0$ & $v_n=1$ \\
-    \hline
-    $v_{n+1} = -1$ & $1$ & $0$ & $0$ \\ 
-    $v_{n+1} = 0$  & $0$ & $1$ & $0$ \\ 
-    $v_{n+1} = 1$  & $0$ & $0$ & $1$ \\
-    \hline
-  \end{tabular}
-\end{center}
-We introduce a parameter $k \in [0,1]$ to linearly interpolate between this extreme case and the first model (i.e.
-with each column given by $\mathbf{p} = \{0.20,0.35,0.45\}$).
-The rest of the panels in the figure show individual runs, 5000 molecule simulations, and mass action approximations for $k=0.25$ and $k=0.5$.
-All particles start at $x_0 = 0$ with $v_{-1}$ chosen randomly.
+We introduce a parameter $k \in [0,1]$ to linearly interpolate between this extreme case and the memoryless model.
+The rest of the panels in the figure show individual runs, 5000 molecule simulations, and mass action approximations for $k=0.5$.
 
@@
 The convergence rate is determined by the non-zero eigenvalue with smallest magnitude of $A$.
-We can increase the convergence rate (while still achieving $\mathbf{\tilde{u}}$) by multiplying all rate constants by some common value.
+%We can increase the convergence rate (while still achieving $\mathbf{\tilde{u}}$) by multiplying all rate constants by some common value.
 However, this trivial strategy ignores the fact that there are biophysical limits on how fast molecular motors can move.
 
-\subsection*{Stochastic Model of Transport}
+\subsection*{Stochastic Interpretation of Mass-Action Model}
 
-We model the stochastic transport of a single molecule with a discrete-time Markov chain model.
-Let the vector $\mathbf{p}^{(k)} = [p_1^{(k)}, p_2^{(k)}, ..., p_N^{(k)}]^T$ denote the probability of finding the molecule in each of the $N$ compartments on the $k$th time step.
-For example, $p_1^{(0)}$ is the initial probability that the molecule is in the first compartment (which is the soma in our implementation).
-The state-transition matrix $S$ describes the probabilistic anterograde/retrograde transport of the molecule between neighboring compartments in each discrete time step:
+The mass-action model described in figure 2 is a deterministic dynamical system.
+However, this determinism only holds in the limit of having a very large number of transported particles.
+Cargoes with small copy numbers (e.g.
+mitocondria) will operate in a stochastic regime.
+We evoke a standard assumption that the system is \textit{ergodic}, meaning that position of one particle averaged over very long time intervals is the same as the ensemble steady-state distribution.
+
+Thus, in addition to modeling how the spatial distribution of cargo changes over time, the mass-action model equivalently models the spatial probability distribution of a single cargo.
+That is, imagine we track a single cargo and ask its position after a long period of transport.
+The probability ratio between of finding this particle in any parent-child pair of compartments converges to:
 $$
-\mathbf{p}^{(k+1)} = S\mathbf{p}^{(k)}
+\frac{p_p}{p_c} \bigg|_{ss} = \frac{b}{a}
 $$
-The state-transition matrix is related to the mass-action system matrix $A$ by the following relation:
+which mirrors our analysis of the deterministic model.
+
+At steady-state, the number of molecules in any single compartment follows a binomial distribution; the coefficient of variation in each compartment is given by:
 $$
-S = \Delta t A + I
+\sqrt{\frac{1-p_i^{(ss)}}{n~p_i^{(ss)}}}
 $$
-where $\Delta t$ is the length of a time step (assumed to be very small), and $I$ is the identity matrix.
-The columns of $S$ sum to one, and, since $\Delta t$ is small, all elements of $S$ lie on the interval $[0,1]$.
-This transformation shifts and scales the eigenvalues of $A$ to lie on the interval $(0,1]$, without modifying the eigenvectors of the system.
-The steady-state probability distribution is given by the eigenvector of $S$ with eigenvalue 1 (CITE), which is identical to the vector spanning the nullspace of $A$ and therefore the steady-state concentration distribution of the mass-action model.
+This suggests that there are two ways of decreasing noise in the system.
+First, increasing the number of transported molecules, $n$, decreases the noise by a factor of $1/\sqrt{n}$.
+Additionally, transport is more reliable to compartments with a high steady-state occupation probability.
 
-\subsection{Transport Model With Detachment and Degradation (Fig. 4)}
+\subsection*{Detachment and Degradation Reactions and Quasi-Steady-State Approximation}
 
-We can also interpolate between these two strategies to achieve the target distribution.
-Let $F$ be a scalar between 0 and 1, and let $\tilde{u}^\star$ be normalized to sum to one.
+Introducing detachment and degradation reactions into the transport model is straightforward. For an arbitrary compartment in a cable, the differential equations become:
+$$
+\begin{array}{lcl}
+\dot{u}_i & = & a_{i-1} u_{i-1} - (a_i+b_{i-1}+c_i) u_i + b_i u_{i+1} \\
+\dot{u}_i^\star & = & c_i u_i - d_i u_i^\star
+\end{array}
+$$
+
+When $a_i,b_i \gg c_i \gg d_i$, then the variables $u_i$ and $u_i^\star$ approach a quasi-steady-state, which we denote $\tilde{u}_i$ and $\tilde{u}_i^\star$.
+For simplicity we assume $d_i = 0$ in our simulations.
+We present two strategies for achieving a desired distribution for $\tilde{u}_i^\star$ in figure 4C and 4D.
+To interpolate between these strategies, let $F$ be a scalar between 0 and 1, and let $\tilde{u}^\star$ be normalized to sum to one.
 We choose $a_i$ and $b_i$ to achieve:
@@
 Setting $F=1$ results in the simulation in figure 4C, while setting $F=0$ results in the simulation in figure 4D.
-Setting $F=0.3$ results in the simulation shown in figure 4E, which uses an interpolated strategy.
+An interpolated strategy is shown in figure 4E ($F=0.3$).
 

### 2015-10-20 latex/paper.tex
v5

@@
 
-To test the plausibility of this model in a complex morphology, we extended an existing multi-compartment model of a CA1 pyramidal neuron \citep{Migliore_2012}.
+To test the plausibility of this model in a complex morphology, we incorporated it into an existing multi-compartment model of a CA1 pyramidal neuron \citep{Migliore_2012}.
 Excitatory synaptic input was delivered to 120 locations within three dendritic regions (red dots, Fig.
@@
 
+This work was supported by Howard Hughes Medical Institute (T.S.), NIH Grant 1P01NS079419 (E.M and T.O.), NIH Grant P41GM103712 (A.H.W., C.O.
+and T.S.), Charles A.
+King Trust (T.O.), and the Deptartment of Energy Computational Science Graduate Fellowship (A.H.W.).
+
 \bibliography{transport_refs}

### 2015-12-09 latex/paper-v2.tex

--- 2015-10-20 latex/paper-v3.tex
@@
 \includegraphics[width=0.9\columnwidth]{04_sushi_belt.png}
-\caption{Multiple strategies for transport in a model including nonuniform microtubular detachment/activation.
-\textbf{(A)} Schematic of microtubular transport model with irreversible detachment in a branched morphology.
-The localized degradation reactions ($u^{\star}_i \xrightarrow{d_i} \varnothing$) is omitted.
-\textbf{(B)} Multiple strategies for producing a desired distribution of activated biomolecules ($\tilde{u}^{\star}$).
-When the timescale of detachment/delivery is sufficiently slow, the distribution of cargo on the microtubules approaches a quasi-steady-state (transport step).
-This known distribution can then be transformed into the desired distribution for $\tilde{u}$ (detachment step).
-As long as these two steps are appropriately matched (blends of blue), then the desired distribution will be achieved (CA1 cell, right).
-\textbf{(C-E)} Normalized distributions of $u$ (red), $u^\star$ (blue), and $\tilde{u}^\star$ (black) as $t \rightarrow \infty$ for various strategies diagrammed in panel B (see circled red numbers).
-}
+\caption{Multiple strategies for transport in a model including nonuniform microtubular detachment/activation}
 \end{center}
@@
 We examined this possibility in a simpler model --- an unbranched cable --- so that we could develop simple heuristics that precisely achieve a desired distribution of cargo while minimizing the convergence time.
+%(more complex, \textit{ad hoc}, heuristics could be developed for complex morphologies).
 In the reduced model, cargo begins on the left end of the cable and is transported to a number of synaptic sites, each of which is modeled as a double-exponential curve.
@@
 \textbf{(A-C)} Steady-state cargo profiles (red) for three stimulation patterns (black arrows) along an unbranched cable.
-The dotted black line corresponds to the `target' steady-state level at each synapse.
 \textbf{(A)} When the timescale of detachment is sufficiently slow, cargo can be evenly distributed to the synapses regardless of their number and position.
@@
 Changing the number of synapses (middle row) or the position of the synapses (bottom row) causes the unequal distribution of cargo to synapses.
-\textbf{(D)} Tradeoff curves between non-specificity and convergence rate for six evenly spaced synapses (top row of A-C).
-The curve shifts to the left and becomes non-monotonic as the anterograde bias ($\beta$) increases.
-\textbf{(E)} Tradeoff curves for two levels of anterograde bias on multiple simulations; for each simulation six synapse positions were drawn from random uniform distribution over the length of the cable.
-\textbf{(F)} Same as panel E, except each the number of synapses was randomly chosen between 3 to 9 for each simulation.
 }
@@
 We then hand-tuned the transport rate constants to deliver equal cargo to six evenly spaced synaptic sites (top row of Fig. 6C).
-Specifically, we increased the anterograde rate constants ($a_i$) and decreased the retrograde rate constants ($b_i$) by a decreasing linear function of position so that $a_{N-1} = b_{N-1}$ at the right side of the cable.
-On the left end of the cable, we set $a_1 = 0.5 + \beta$ and $b_1 = 0.5 - \beta$, where $\beta$ is the parameter controlling anterograde bias
+Specifically, we increased the anterograde rate constants ($a_i$) and decreased the retrograde rate constants ($b_i$) by a decreasing linear function of position so that $a_N = b_N$ at the right side of the cable (see Methods).
 Intuitively, this pushes cargo past the proximal synaptic sites more quickly, canceling out the exponential delivery bias induced by fast detachment.
@@
 
-All simulation code is available on: https://github.com/ahwillia/Williams-etal-Synaptic-Transport
-
-\subsection*{Model of single-particle transport}
-
-Let $x_n$ denote the position of a particle along a 1-dimensional cable at timestep $n$.
-Let $v_n$ denote the velocity of the particle at timestep $n$; for simplicity, we assume the velocity can take on three discrete values, $v_n = \{-1,0,1\}$, corresponding to a discrete retrograde movement, pause, or anterograde movement.
-As a result, $x_n$ is constrained to take on integer values.
-In the memoryless transport model (top plots in Fig.
-1B, 1D, and 1F), we assume that $v_n$ is drawn with fixed probabilities on each step.
-The update rule for position is:
-$$x_{n+1} = x_n + v_n$$
-$$v_{n+1} = \left\{\begin{matrix}
--1 & \text{with probability } p_-\\ 
-0 & \text{with probability } p_0\\  
-1 & \text{with probability } p_+
-\end{matrix}\right.$$
-
-We chose $p_- = 0.2$, $p_0 = 0.35$ and $p_+ = 0.45$ for the illustration shown in Figure 1.
-For the model with history-dependence (bottom plots in Fig.
-1B, 1D, and 1F), the movement probabilites at each step depend on the previous movement.
-For example, if the motor was moving in an anterograde direction on the previous timestep, then it is more likely to continue to moving in that direction in the next time step.
-In this case the update rule utilizes \textit{conditional} probabilities:
-$$v_{n+1} = \left\{\begin{matrix}
--1 & \text{with probability } p(-|v_n)\\ 
-0 & \text{with probability } p(0|v_n)\\  
-1 & \text{with probability } p(+|v_n)
-\end{matrix}\right.$$
-
-In the extreme case of history-dependence, the particle always steps in the same direction as the previous time step.
-\begin{center}
-  \begin{tabular}{ l | c  c  c }
-    & $v_n=-1$ & $v_n=0$ & $v_n=1$ \\
-    \hline
-    $p(v_{n+1} = -1)$ & $1$ & $0$ & $0$ \\ 
-    $p(v_{n+1} = 0)$  & $0$ & $1$ & $0$ \\ 
-    $p(v_{n+1} = 1)$  & $0$ & $0$ & $1$ \\
-    \hline
-  \end{tabular}
-\end{center}
-We introduce a parameter $k \in [0,1]$ to linearly interpolate between this extreme case and the memoryless model.
-The rest of the panels in the figure show individual runs, 5000 molecule simulations, and mass action approximations for $k=0.5$.
-
-\subsection*{Model of bulk/mass-action transport}
+\subsection*{Microtubule Transport Model (Fig. 1)}
 Transport in an unbranched cable (equation 1) leads to the following system of differential equations:
@@
 $$
-Similar systems result from branched mass-action models.
-The steady-state ratio of cargo in two neighboring compartments equals the ratio of transport rate constants (equation 2).
-This can be immediately verified at either end of the cable:
+Similar systems result from branched mass-action models. The steady-state relationship in equation 5 can be immediately verified at either end of the cable:
 $$
@@
 $$
-Successively applying the same logic down the cable confirms the condition in equation 2 holds globally.
-A similar procedure (starting at the tips and moving in) can be applied to branched morphologies to prove the more general condition (equation 4).
-
-% The same result can be shown in a branched tree morphology.
+The same procedure can be iteratively applied down the cable to show that equation 5 holds globally.
+The same result can be shown in a branched tree morphology.
 Here, each compartment has exactly one parent, but can have multiple children at branch points.
@@
 At steady-state, there is no net flux between $u_c$ and its children:
-% $$
-% \dot{u}_c = a u_p - b u_c + \underbrace{\sum_j (b_j u_j - a_j u_c)}_{= 0 \text{ , at ss}}
-% $$
-% Thus, we have:
-% $$
-% \dot{u}_c = a u_p - b u_c = 0 ~\Rightarrow~ \frac{u_p}{u_c} \Bigg |_{ss} = \frac{b}{a}
-% $$
-
-It is helpful to re-express the model as a matrix differential equation, $\mathbf{\dot{u}} = A \mathbf{u}$, where $\mathbf{u} = \left[ u_1, u_2, ...
-u_N \right]^T$ is the state vector, and $A$ is the state-transition matrix.
-For a general branched morphology, $A$ will be nearly tridiagonal, with off-diagonal elements corresponding to branch points; matrices in this form are called Hines matrices \citep{Hines_1984}.
+$$
+\dot{u}_c = a u_p - b u_c + \underbrace{\sum_j (b_j u_j - a_j u_c)}_{= 0 \text{ , at ss}}
+$$
+Thus, we have:
+$$
+\dot{u}_c = a u_p - b u_c = 0 ~\Rightarrow~ \frac{u_p}{u_c} \Bigg |_{ss} = \frac{b}{a}
+$$
+To study how the system converges to steady-state, we can re-express the model as a matrix differential equation, $\mathbf{\dot{u}} = A \mathbf{u}$, where $\mathbf{u} = \left[ u_1, u_2, ...
+u_N \right]^T$ is the state vector, and $A$ is a matrix.
+For a general branched morphology, the matrix $A$ will be nearly tridiagonal, with off-diagonal elements corresponding to branch points; matrices in this form are called Hines matrices \citep{Hines_1984}.
 For the simpler case of an unbranched cable, $A$ is tridiagonal:
@@
 
-The desired steady-state distribution, $\mathbf{\tilde{u}}$, is an eigenvector that spans the nullspace of $A$.
-It is simple to show that all other eigenvalues $A$ are negative using the Gershgorin circle theorem; thus, the fixed point described by equations 2 and 4 is stable.
+The desired distribution, $\mathbf{\tilde{u}}$, is an eigenvector that spans the nullspace of $A$.
+All other eigenvalues $A$ are negative, which can be shown using the Gershgorin circle theorem.
 The convergence rate is determined by the non-zero eigenvalue with smallest magnitude of $A$.
-%We can increase the convergence rate (while still achieving $\mathbf{\tilde{u}}$) by multiplying all rate constants by some common value.
+We can increase the convergence rate (while still maintaining $\mathbf{\tilde{u}}$) by multiplying all rate constants by some common value.
 However, this trivial strategy ignores the fact that there are biophysical limits on how fast molecular motors can move.
 
-\subsection*{Stochastic Interpretation of Mass-Action Model}
+\subsection*{Stochastic Model of Transport}
 
-The mass-action model described in figure 2 is a deterministic dynamical system.
-However, this determinism only holds in the limit of having a very large number of transported particles.
-Cargoes with small copy numbers (e.g.
-mitocondria) will operate in a stochastic regime.
-We evoke a standard assumption that the system is \textit{ergodic}, meaning that position of one particle averaged over very long time intervals is the same as the ensemble steady-state distribution.
+We model the stochastic transport of a single molecule with a discrete-time Markov chain model.
+Let the vector $\mathbf{p}^{(k)} = [p_1^{(k)}, p_2^{(k)}, ..., p_N^{(k)}]^T$ denote the probability of finding the molecule in each of the $N$ compartments on the $k$th time step.
+For example, $p_1^{(0)}$ is the initial probability that the molecule is in the first compartment (which is the soma in our implementation).
+The state-transition matrix $S$ describes the probabilistic anterograde/retrograde transport of the molecule between neighboring compartments in each discrete time step:
+$$
+\mathbf{p}^{(k+1)} = S\mathbf{p}^{(k)}
+$$
+The state-transition matrix is related to the mass-action system matrix $A$ by the following relation:
+$$
+S = \Delta t A + I
+$$
+where $\Delta t$ is the length of a time step (assumed to be very small), and $I$ is the identity matrix.
+The columns of $S$ sum to one, and, since $\Delta t$ is small, all elements of $S$ lie on the interval $[0,1]$.
+This transformation shifts and scales the eigenvalues of $A$ to lie on the interval $(0,1]$, without modifying the eigenvectors of the system.
+The steady-state probability distribution is given by the eigenvector of $S$ with eigenvalue 1 (CITE), which is identical to the vector spanning the nullspace of $A$ and therefore the steady-state concentration distribution of the mass-action model.
 
-Thus, in addition to modeling how the spatial distribution of cargo changes over time, the mass-action model equivalently models the spatial probability distribution of a single cargo.
-That is, imagine we track a single cargo and ask its position after a long period of transport.
-The probability ratio between of finding this particle in any parent-child pair of compartments converges to:
-$$
-\frac{p_p}{p_c} \bigg|_{ss} = \frac{b}{a}
-$$
-which mirrors our analysis of the deterministic model.
+\subsection{Transport Model With Detachment and Degradation (Fig. 4)}
 
-At steady-state, the number of molecules in any single compartment follows a binomial distribution; the coefficient of variation in each compartment is given by:
-$$
-\sqrt{\frac{1-p_i^{(ss)}}{n~p_i^{(ss)}}}
-$$
-This suggests that there are two ways of decreasing noise in the system.
-First, increasing the number of transported molecules, $n$, decreases the noise by a factor of $1/\sqrt{n}$.
-Additionally, transport is more reliable to compartments with a high steady-state occupation probability.
-
-\subsection*{Detachment and Degradation Reactions and Quasi-Steady-State Approximation}
-
-Introducing detachment and degradation reactions into the transport model is straightforward. For an arbitrary compartment in a cable, the differential equations become:
-$$
-\begin{array}{lcl}
-\dot{u}_i & = & a_{i-1} u_{i-1} - (a_i+b_{i-1}+c_i) u_i + b_i u_{i+1} \\
-\dot{u}_i^\star & = & c_i u_i - d_i u_i^\star
-\end{array}
-$$
-
-When $a_i,b_i \gg c_i \gg d_i$, then the variables $u_i$ and $u_i^\star$ approach a quasi-steady-state, which we denote $\tilde{u}_i$ and $\tilde{u}_i^\star$.
-For simplicity we assume $d_i = 0$ in our simulations.
-We present two strategies for achieving a desired distribution for $\tilde{u}_i^\star$ in figure 4C and 4D.
-To interpolate between these strategies, let $F$ be a scalar between 0 and 1, and let $\tilde{u}^\star$ be normalized to sum to one.
+We can also interpolate between these two strategies to achieve the target distribution.
+Let $F$ be a scalar between 0 and 1, and let $\tilde{u}^\star$ be normalized to sum to one.
 We choose $a_i$ and $b_i$ to achieve:
@@
 Setting $F=1$ results in the simulation in figure 4C, while setting $F=0$ results in the simulation in figure 4D.
-An interpolated strategy is shown in figure 4E ($F=0.3$).
+Setting $F=0.3$ results in the simulation shown in figure 4E, which uses an interpolated strategy.
 

### 2015-12-09 latex/paper-v5.tex

--- 2015-10-20 latex/paper-v3.tex
@@
 \usepackage{setspace}
-\doublespacing
+%\doublespacing
 
@@
 \begin{abstract}
-Nervous system function depends on the appropriate development, maintenance, and plasticity of synaptic connectivity.
-In order to form and modify synaptic connections, organelles and molecular cargo need to be trafficked from the site of synthesis to the vicinity of the synapse.
-An open question is how synaptic cargo can be delivered to appropriate synapses in spite of the complex dendritic arbors and thousands of postsynaptic sites typical of many neurons.
-We develop a biophysically-rooted yet general model of microtubule transport that captures known mechanistic properties of intracellular transport.
-In spite of the assumption that molecular transport responds only to local chemical cues, we show that arbitrarily complex distributions of cargo can be achieved.
-However, the model reveals important tradeoffs that can be tested experimentally.
-We find that precise and flexible delivery of synaptic cargo requires the capture of synaptic cargo to occur on a slower timescale than the movement of cargo across the microtubule network.
-Tuning the transport parameters reveals that optimal solutions exist for specific distributions of synapses, but these solutions sensitively depend on the location as well as the number of synapses, suggesting that biological neurons face a compromise between flexibility of connectivity and efficacy in regulating synaptic function.
+Neurons form, maintain, and modify complex connectivity patterns by regulating the spatial distribution of organelles and macromolecules throughout their dendritic arbors.
+Previous work suggests that localized biochemical signals influence the trafficking, delivery and expression of molecular cargo along microtubules.
+However, it remains unclear whether purely local mechanisms can be orchestrated to provide adequate transport.
+We mathematically formalized a previously proposed ``sushi belt'' model of microtubule transport \citep{Doyle_2011} and showed that arbitrarily complex spatial distributions of cargo can indeed be achieved by localized mechanisms.
+However, this model predicts an unavoidable tradeoff between speed and precision of cargo delivery that can be tested experimentally.
+Reliable cargo delivery required that cargo transport along microtubules occur on a faster timescale than cargo dissociation from the microtubules.
+Increasing the cargo dissociation rate provided faster transport, but required complex, global re-tuning of the trafficking rates to maintain precision.
+Additionally, these solutions tended to be fragile in the sense that small changes in the target distribution led to large changes in the optimal delivery strategy.
+Together, these results suggest that macromolecules with stereotyped expression patterns might be tuned for fast and precise transport, but cargoes requiring plastic expression patterns face a tradeoff in the speed and precision of transport.
 
@@
 Neurons often have complex dendritic trees, reflecting the dense and structured synaptic connectivity that supports nervous system function.
-In order to maintain appropriate connectivity, or to alter it in response to changes in circuit activity, numerous enzymes and macromolecules must be repeatedly replenished and redistributed amongst a staggering number of synaptic contacts.
-Although the molecular machinery that solves this logistical problem is known in increasing detail [REFS], there are few attempts to quantify broadly how subcellular transport processes might constrain a neuron's ability to regulate its connectivity and synaptic function.
+In order to maintain appropriate connectivity, or to alter it in response to changes in circuit activity, numerous enzymes and macromolecules must be continually replenished and distributed among a large number of synaptic contacts.
+Although the molecular machinery that solves this logistical problem has been characterized in increasing detail \citep{Doyle_2011,Buxbaum_2014b,Hancock_2014}, there are few attempts to formalize how subcellular transport processes constrain a neuron's ability to regulate its connectivity and synaptic function.
 
-Transport along dendrites is mediated by motor proteins (kinesins and dyneins) that walk along microtubules, carrying cargo at a rate that far exceeds passive diffusion \citep{Smith_2001}\hl{Others?}.
-The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \citep{Mironov_2007,Wang_2009}, that are caused by synaptic activity or locally released growth factors from other cells.
-In this way, the proteins, scaffolding molecules and receptors that make up a postsynaptic site can be made available to alter an existing synapse or assemble a new synapse in the vicinity of a presynaptic partner.
-Not all aspects of synaptic plasticity require delivery of cargo from the soma.
-For example, some forms of long-term potentiation (LTP) depend on local protein synthesis and can function in isolated dendrites [REFS].
+Not all aspects of neurite metabolism require delivery of cargo from the soma.
+For example, some forms of long-term potentiation (LTP) depend on local protein synthesis and can function in isolated dendrites \citep{Kang1996,Aakalu:2001aa,vickers2005induction,Sutton:2006aa}.
 Nonetheless, components originating in the soma need to find their way to synapses in the first place, and in the long run, the mRNAs and the machinery that supports local biosynthesis needs to be replenished.
@@
 
-The distribution of molecular cargo is partially controlled by a coarse addressing system in the localization sequences of 3$'$-untranslated regions of mRNAs -- which, for example, control whether mRNA is sequestered in the nucleus or into dendrites \citep{Andreassi2009}.
-However, it is unclear whether a fine-scale, centralized addressing system, as exemplified by human-designed transport systems, is feasible or even desirable for neurons to implement.
-Other biological systems (e.g. ant colonies) utilize decentralized transport strategies, which emerge from simple, local decisions made by a distributed population of agents \citep{Deneubourg_1990}.
-Such self-organizing systems often enjoy a number of advantageous properties -- including scalability, flexibility, and fault-tolerance -- and are therefore a current topic of substantial interest to engineers \citep{Werfel2014,Rubenstein2014}.
+Kinesin and dyenin motor proteins mediate transport along microtubules at rates that far exceed passive diffusion \citep{Block_1990,Smith_2001,Hirokawa_2010,Gagnon_2011,park2014visualization}.
+In many cases, the movement of individual cargoes is stochastic and bidirectional \citep{Hancock_2014}, leading to the hypothesis that motor proteins ``search'' the dendritic tree for dropoff locations, instead of following a pre-determined path \citep{Welte2004,Bressloff_2009,Doyle_2011}.
+Thus, the local rate of transport and the decision to release cargo are thought to be controlled by localized signaling pathways, rather than a centralized addressing system.
+These localized mechanisms are not fully understood, but are believed to involve transient elevations in second-messengers like $[Ca^{2+}]$ and ADP \citep{Mironov_2007,Wang_2009,Buxbaum_2014a}, and changes in microtubule-associate proteins \citep{Soundararajan_2014}.
+These pathways are, in turn, influenced by the spatial pattern of synaptic activity, spontaneous release of calcium from internal stores, and locally released factors from other cells \citep{Wong2002,Parrish2007,Park2013,Zagrebelsky2014}.
+The composition and expression of molecular cargo is also influenced by global factors, such as the cell's average activity level \citep{Spitzer2006,Puthanveettil_2008,Turrigiano2011} and localization sequences within 3$'$-untranslated regions of mRNA, which act as a coarse addressing system \citep{Andreassi2009}.
 
-%From simple, experimentally verifiable assumptions about the dynamics of active dendritic transport we develop a minimal biophysical model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies.
-We develop a minimal biophysical model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies, and show how local biochemical signals can modify the movement and/or release of cargo to produce complex spatial patterns in a self-organizing fashion.
-However, the decentralized transport strategies we explore face unavoidable tradeoffs between the speed and precision of cargo delivery.
-Tuning the transport parameters reveals that while optimal solutions exist to balance this tradeoff, these solutions sensitively depend on the location as well as the number of synapses, suggesting that biological neurons must compromise between flexibility in connectivity and their ability to precisely regulate synaptic function.
+%However, it is not know how intracellular cargo can be targeted on a finer scale in a way that responds to varying demand.
+
+Here, we aim to express and examine existing conceptual models of molecular transport \citep{Doyle_2011} in a mathematical framework.
+We develop a minimal biophysical model that can account for activity-dependent accumulation of molecular cargo at synaptic sites in realistic neuronal morphologies, and show that biochemical signals can indeed produce complex spatial expression patterns by locally modifying the movement and release of cargo.
+However, we find that decentralized transport strategies face unavoidable tradeoffs between the speed and precision of cargo delivery.
+Tuning the transport parameters reveals that while optimal solutions exist to circumvent this tradeoff, these solutions sensitively depend on the location as well as the number of synapses, suggesting that biological neurons may face a compromise between flexibility in connectivity and their ability to precisely regulate synaptic function.
 
@@
 
-\hl{Activation of synaptic receptors triggers downstream signalling cascades that can alter global gene expression [ref Greenberg, Bading, others] as well as modulating the trafficking and metabolism of molecular cargo locally [REFS].
-[more on this] \textbf{move to intro?}}
-
 Transport along microtubules is mediated by kinesin and dynein motors, which mediate anterograde and retrograde transport, respectively \citep{Hirokawa_2010,Gagnon_2011}.
-Cargo is often simultaneously bound to both forms of motor protein, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Hancock_2014,Buxbaum_2014b} (Fig.
+Cargo is often simultaneously bound to both forms of motor protein, resulting in stochastic back-and-forth movements with a net direction determined by the balance of opposing movements \citep{Welte2004,Hancock_2014,Buxbaum_2014b} (Fig.
 1A).
 
-To obtain a general model that can accommodate variations in the biophysical details, we consider microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006,Bressloff_2009,Newby_2010}.
+To obtain a general model that can accommodate variations in the biophysical details, we consider microtubule-based transport as a biased random walk along a one-dimensional cable \citep{Bressloff_2006,Bressloff_2009,Newby_2010,Bressloff_2013}.
 For each time step, the cargo moves forwards, backwards, or remains in the same place with different probabilities that together sum to 1.
@@
 1B, top panel).
-A potentially more realistic model (see, e.g., \cite{Soundararajan_2014}) incorporates hysteresis into the biased random walk (see Methods).
+A potentially more realistic model (see, e.g., \cite{Muller_2008}) incorporates hysteresis into the biased random walk (see Methods).
 In this case, the cargo is more likely to continue in the same direction as it moved during the previous time step, leading to extended runs in one direction along the microtubule (Fig.
@@
 \caption{Model of microtubular transport.
-\textbf{(A)} Synaptic cargo, $u$, undergoes stochastic back-and-forth movements driven by opposing motor proteins.
+\textbf{(A)} Molecular cargo, $u$, undergoes stochastic back-and-forth movements driven by opposing motor proteins.
 \textbf{(B)} Three example random walks on a cable representing the movement of individual cargoes.
@@
 \textbf{(D)} The concentration profile of transported cargo along a cable over time, simulated as 1,000 independent random walks. Simulations with (bottom) and without (top) history-dependence.
-\textbf{(E)} In the limit of many individual particles, the concentration of $u$ is modeled by the convection-diffusion partial differential equation.
-The parameters, $a$ and $b$, respectively scale the anterograde and retrograde rate of transport (see equation 1).
-\textbf{(F)} The convection-diffusion model provides a good fit for the simulations in panel D.
+\textbf{(E)} In the limit of many individual particles, the concentration of $u$ is described by a mass-action model (equation 1).
+The parameters $a$ and $b$ respectively scale the anterograde and retrograde rate of transport.
+\textbf{(F)} The mass-action model provides a good fit for the simulations in panel D.
 }
@@
 
-While the position of individual cargoes can be highly stochastic, the net movement of a population of cargoes (Fig. 1C) is predictable.
+While the position of individual cargoes is highly stochastic, the net movement of a population of cargoes (Fig. 1C) is predictable.
 Figure 1D shows the distribution of 1000 molecules over time with (top panel) and without (bottom panel) hysteresis.
-For the simple biased random walk and for the random walk with hysteresis, these simulations can be well-fit by an advection-diffusion equation (Fig.
-1E-F), which is easier to analyze because it is deterministic and contains fewer variables \citep{Smith_2001}.
-
-We model transport using the advection-diffusion equation with spatially non-uniform drift and diffusion coefficients.
-As an approximation, we discretized a dendritic tree into small compartments, and modeled the movement of cargo between neighboring compartments as reactions with first order kinetics.
-In an unbranched cable with $N$ compartments, the mass-action model is:
+Thus, the bulk trafficking of cargo can be modeled as a deterministic process, which we refer to as the ``mass-action model'' of transport.
+The model discretizes the dendritic tree into small compartments, and describes the transfer of cargo between neighboring compartments as reactions with first order kinetics.
+In a cable with $N$ compartments, the mass-action model is (Fig.
+1E):
 \begin{equation}
@@
 \end{equation}
-where $u_i$ is the amount of cargo in each compartment, and $a_i$ and $b_i$ respectively denote local rate constants for anterograde and retrograde transport; these parameters determine the local diffusion and drift coefficients as shown in figure 1E (see Methods).
-Similar mass-action schemes can be constructed to model transport in branched morphologies (Fig.
-2A).
-The mass-action scheme provides a flexible way to model local changes in transport rates, and is very tractable to mathematical analysis and numerical simulation.
+where $u_i$ is the amount of cargo in each compartment, and $a_i$ and $b_i$ respectively denote local rate constants for anterograde and retrograde transport.
+The mass-action model with spatially uniform transport rates (Fig.
+1F) reproduces the dynamics of the ensemble simulations (Fig.
+1D).
+In this case, the mass-action model maps onto the well-known drift-diffusion equation (see \textit{Methods}).
 
-A central assumption of mass-action description of this model is that the net movement of molecules between neighboring compartments is a stochastic and memoryless process.
+The mass-action model makes two important assumptions.
+It first assumes that the net movement of molecules between neighboring compartments is a stochastic and memoryless process.
 This assumption is reasonable for cargoes that change direction often; specifically, on a length scale comparable to the size of the compartments.
 This appears to be the case under many \citep{Muller_2008,Verbrugge_2009}, though not necessarily all \citep{Dynes_2007,Soundararajan_2014} circumstances.
-In simulations, we observed that this model was not very sensitive to violations of this assumption; the population dynamics of cargoes with substantial run lengths could still be well-fit by this class of models (Fig.
-1F, lower panel; Supplementary Fig?).
+However, we observed that the mass-action model could still be well-fit to simulated data where this assumption was violated (Fig.
+1F, lower panel).
+In fact, the mass-action model only breaks down in the limit of very large run lengths (i.e.
+unidirectional, non-stochastic transport; see \textit{Methods}).
+
+The second assumption of the mass-action model is that there are many transported particles distributed throughout the dendritic tree.
+Many types of dendritic cargo are present in high numbers \hl{(CITE)}, and a deterministic model can provide a good approximation in this regime (Fig.
+1D).
+The model also provides insight into the stochastic dynamics of transport for cargoes with fewer copy numbers.
+Instead of interpreting $u$ as the amount of cargo in each compartment, this variable (when appropriately normalized) can be interpreted as the probability that a single particle lies within a particular compartment.
+The mass-action model captures average, or expected, behavior of the ensemble, with noise inversely proportional to the square root of the number of copies of cargo (see \textit{Methods}).
 
@@
 
-We next show how the mass-action model can be easily solved to produce complex distributions in the concentration of cargo along a dendrite
-The exchange of $u$ between neighboring compartments approaches an equilibrium/steady-state ($ss$) distribution over time. In an unbranched dendrite, this occurs precisely when:
+We used the mass-action model for our simulations because it is easy to extend it to branched morphologies (Fig.
+2A), and to cases where the trafficking rate constants ($a_i$ and $b_i$) are spatially non-uniform.
+This corresponds to the kinetics of motor proteins depending on local biochemical signals \citep{Mironov_2007,Wang_2009,Soundararajan_2014}.
+
+In the model, the exchange of cargo between compartments approaches a equilibrium, or steady-state ($ss$), distribution over time (see \textit{Methods}).
+The equilibrium occurs when no net movement of cargo occurs between connected compartments.
+Mathematically, this occurs when:
 \begin{equation}
-\frac{u_i}{u_{i+1}} \Bigg|_{ss} = \frac{b_i}{a_i}
+\frac{u_p}{u_c} \Bigg|_{ss} = \frac{b}{a}
+%\frac{b}{a} = \frac{\tilde{u}_p}{\tilde{u}_c}
 \end{equation}
-(see Methods).
-Thus, the local trafficking rates, $a_i$ and $b_i$, can be tuned to produce a desired spatial distribution of cargo.
-Let $\tilde{u}$ denote the desired steady-state level of $u$ in each compartment.
-For example, $\tilde{u}_i$ might refer to the local concentration of biochemical signal that ``tags'' synapses for plasticity \citep{Frey_1997}; such a tag might be positively correlated to the desired level of delivered cargo.
+where $u_p$ is the level in the ``parent" compartment (closer to soma) and $u_c$ is the level in the ``child" compartment (closer to periphery); $b$ and $a$ refer to the trafficking rate constants between this pair of compartments.
+
+Intuitively, in the mass-action model, the rate of cargo transfer is proportional to the concentration of cargo and the trafficking rate constant.
+Thus, the flow of cargo is equal and opposite when the ratio of cargo matches the reciprocal ratio of the rate constants between a pair of connected compartments.
+
+The above result means that the trafficking rates can be locally tuned to produce a desired spatial distribution of cargo.
+Denote the desired steady-state level of cargo in each compartment by $\tilde{u}$ (we will soon show how this can be encoded by a localized biochemical signal).
 To match this desired distribution, the ratio of local trafficking rates should satisfy:
 \begin{equation}
-\frac{b_i}{a_i} = \frac{\tilde{u}_i}{\tilde{u}_{i+1}}
+\frac{b}{a} = \frac{\tilde{u}_p}{\tilde{u}_c}
 \end{equation}
@@
 %The initial distribution of $u$ is uniform (t=0); over time the system achieves the desired linear gradient (steady-state occurs around t=5, in this example).
-\textbf{(C)} The slope of the linear gradient shown in panel B is determined by the total amount of $u$ present in the model; the slope increases as more of $u$ is present, but the linear profile is preserved.
-\textbf{(D)} A model of a CA1 pyramidal cell with 742 compartments based on \cite{Migliore_2012}; excitatory synapses were added at the locations marked by red dots. 
+\textbf{(C)} The slope of the linear gradient shown in panel B is directly proportional to the total amount of cargo in the model ($\sum_i u_i$); the slope increases with increasing cargo levels, but the linear profile is preserved.
+\textbf{(D)} A model of a CA1 pyramidal cell with 742 compartments adapted from \cite{Migliore_2012}; excitatory synapses were added at the locations marked by red dots. 
 \textbf{(E)} The average membrane potential in each compartment of the CA1 model cell was used to define a desired spatial distribution, and transport rate constants were chosen according to equation (4).
 The desired spatial distribution of cargo emerges over time, after starting in the soma.
-\textbf{(F)} The desired and steady-state profile of $u$ for each compartment in the simulation shown in panel E.
+\textbf{(F)} The desired and steady-state profile of cargo for each compartment in the simulation shown in panel E.
 }
@@
 
-For example, a linear expression pattern emerges when $\tilde{u}_i \propto i$, resulting in $b_i / a_i = i / i + 1$ (Fig. 2B).
-This rule produces the expected linear expression gradient with the slope controlled by tuning the total amount of cargo in the cable (Fig. 2C).
+For example, we can produce a linear expression gradient \citep{Magee_1998,Hoffman_1997} by setting $\tilde{u}$ directly proportional to the distance from the soma.
+This produces trafficking rate constants that satisfy $b_i / a_i = i / i + 1$ (where $i$ indexes on increasing distance to the soma).
+Figure 2B-C shows that this rule produces the expected profile, with the slope of the linear gradient controlled by tuning the total amount of cargo in the cable (Fig. 2C).
 
-These results extend directly to branched morphologies (see Methods). For any pair of connected compartments:
-\begin{equation}
-%\frac{u_p}{u_c} \Bigg|_{ss} = \frac{b}{a}
-\frac{b}{a} = \frac{\tilde{u}_p}{\tilde{u}_c}
-\end{equation}
-where $u_p$ is the level in the ``parent" compartment (closer to soma) and $u_c$ is the level in the ``child" compartment (closer to periphery); $b$ and $a$ refer to the local transport rate constants between this pair of compartments.
-
-Together, this analysis shows that by slowing or biasing local trafficking rates, arbitrary distributions of cargo can be achieved over time.
+Together, this analysis shows that by manipulating local trafficking rates, arbitrary distributions of cargo can be achieved over time.
 Local trafficking rates, in turn, can be modulated by a simple biochemical reaction resulting from synaptic activation or local release of a growth factor.
 We can consider the local cytoplasmic calcium concentration, $[ca]_i$, as an candidate second messenger.
-Increases in $[ca]_i$ simultaneously arrest anterograde and retrograde microtubular transport \citep{Wang_2009}.
-That is, for any pair of compartments, the anterograde rate constant is determined by calcium in the parent compartment, $a = f([ca]_p)$,  and the retrograde rate constant is determined by calcium in the child compartment, $b = f([ca]_c)$, where $f$ is a function that describes how calcium alters the transport rates.
+Increases in $[ca]_i$ simultaneously arrest anterograde and retrograde microtubular transport for certain cargoes \citep{Wang_2009}.
+Thus, for any pair of compartments, the anterograde rate constant is determined by calcium in the parent compartment, $a = f([ca]_p)$,  and the retrograde rate constant is determined by calcium in the child compartment, $b = f([ca]_c)$, where $f$ is a function that describes how calcium alters the transport rates.
 This results in:
@@
 
-Thus, in principle, local calcium transients that serve to arrest transport could provide a mechanism for matching cargo concentration to an arbitrarily complicated distirbution over a dendritic tree.
-To test the plausibility of this model in a complex morphology, we extended an existing multi-compartment model of a CA1 pyramidal neuron \citep{Migliore_2012}.
+Thus, in principle, local calcium transients that serve to arrest transport could provide a mechanism for distributing cargo to an arbitrary target profile.
+To demonstrate the plausibility of this model in a complex morphology, we extended an existing multi-compartment model of a CA1 pyramidal neuron \citep{Migliore_2012}.
 Excitatory synaptic input was delivered to 120 locations within three dendritic regions (red dots, Fig.
-2D), and the average membrane potential in each electrical compartment determined the target level $\tilde{u}_i$ in each compartment (Methods).
+2D), and the average membrane potential in each electrical compartment determined the target level ($\tilde{u}_i$) in each compartment (Methods).
 This models how molecular cargo could be selectively trafficked to active synaptic sites.
@@
 For example, newly synthesized proteins must be delivered to synapses within $\sim$1 hour to support long-term potentiation in CA1 pyramidal cells \citep{Frey_1997,Frey_1998}.
-It is therefore important to know what factors influence the rate at which the distribution of cargo matches its demand profile across the whole dendritic tree.
+We therefore examined how quickly the spatial pattern of cargo converged to its target distribution.
 
-In equations (4) and (5), we implicitly required each $\tilde{u}_i > 0$ in order to avoid division by zero.
+In equations (3) and (4), we implicitly required each $\tilde{u}_i > 0$ in order to avoid division by zero.
 Intuitively, if $\tilde{u}_i = 0$ for some compartment, then no cargo can flow through that compartment, cutting of more peripheral compartments from the transport system.
@@
 
-Figure 3 illustrates and analyzes a bottleneck in a simple three compartment model.
+Figure 3A-C illustrates and analyzes a bottleneck in a simple three compartment model.
 The two compartments on the end of the cable have the same desired level, $\tilde{u}_1 = \tilde{u}_3$; the middle compartment acts as a bottleneck when $\tilde{u}_2$ is very small (Fig. 3A).
@@
 Figure 3B shows that the convergence rate slows dramatically as $\epsilon$ decreases.
-This can be can be solved by analysing the corresponding system of ordinary differential equations.
-The convergence rate is determined by the non-zero eigenvalue with smallest magnitude, which can be thought of as a rate-limiting step or process for the system (Methods, Supp.
-Fig.
-1).
+The convergence rate is determined by the smallest magnitude, non-zero eigenvalue of the system (see Methods), which can be thought of as a rate-limiting step or process for the system.
 Simulations confirmed this analysis and showed that the convergence rate diverges to infinity as $\epsilon$ approaches zero (Fig. 3C).
-\hl{I think the epsilon goes to zero stuff can be omitted, or at the very least stated more tersely - if the transport rate is zero anywhere it is obvious that it takes forever to converge}
 
@@
 \textbf{(A)} A three-compartment transport model, with the middle compartment acting as a bottleneck.
-The vertical bars represent the desired steady-state level of $u$ in each compartment.
+The vertical bars represent the desired steady-state level of cargo in each compartment.
 The rate of transport into the middle compartment is small ($\epsilon$, dashed harpoons) relative to transport out of the middle compartment.
@@
 \textbf{(E)} For all compartments that reach a threshold level ($u_i = 0.001$), the simulated time it takes to reach threshold is plotted against the distance of that compartment to the soma.
-\textbf{(F)} Predicted convergence times for various target distributions (str. rad., stratum radiatum; str. lac., stratum lacunosum/moleculare).}
+\textbf{(F)} Predicted convergence times for various target distributions (\textit{str. rad.}, stratum radiatum; \textit{str. lac.}, stratum lacunosum/moleculare).}
 \end{center}
@@
 
-Qualitatively similar results were obtained in the multi-compartment CA1 neuron model.
-The model converged to a uniform target distribution more quickly than to a ``bottleneck" target distribution, in which the middle third of the apical dendrite had low steady-state levels of cargo (Fig.
+We then asked whether the intuition from this three-compartment model extended to a cell with realistic morphology.
+We obtained qualitatively similar results.
+The CA1 model converged to a uniform target distribution more quickly than to a ``bottleneck" target distribution, in which the middle third of the apical dendrite had low steady-state levels of cargo (Fig.
 3D).
@@
 In addition to this global view of convergence (Fig. 3D), we considered how the transport bottleneck affected transport to individual dendritic compartments.
-Consider a scenario where transported cargo produces a local chemical reaction after a critical concentration threshold is reached; for example, a recently potentiated synapse might be stabilized after enough plasticity-related factors are delivered from the soma.
-Figure 3E plots the transport delay, or duration of time it took for $u_i$ to reach a pre-defined threshold for each compartment.
-We observed qualitatively similar results for different threshold values (data not shown).
+Consider a scenario where transported cargo produces a local chemical reaction after a certain quantity of cargo accumulates; for example, a recently potentiated synapse might be stabilized after enough plasticity-related factors are delivered from the soma.
+Figure 3E plots the duration of time it took for $u_i$ to reach a pre-defined threshold for each compartment as a measure of the local transport delay.
+As expected, introducing a bottleneck caused much longer delays to compartments distal to that bottleneck (Fig. 3E, upper right portion of plot).
+The presence of a bottleneck \textit{shortens} the transport delay to proximal compartments, compared to the uniform target distribution (Fig. 3E, lower left portion of plot).
+This occurs because cargo delayed by the bottleneck spreads throughout the proximal compartments, reaching higher levels earlier in the simulation.
+We observed qualitatively similar results for different local threshold values (data not shown).
 
-As expected, introducing a bottleneck caused much longer delays to compartments distal to that bottleneck (Fig. 3E, upper right portion of plot).
-Interestingly, the presence of a bottleneck also \textit{shortens} the transport delay to proximal compartments, compared to the uniform target distribution (Fig. 3E, lower left portion of plot).
-This occurs because cargo delayed by the bottleneck spreads throughout the proximal compartments, reaching higher levels earlier in the simulation.
-
-One experimentally testable prediction of this analysis is that transport to distal compartments should be quickened by allowing higher levels of $u$ into the proximal compartments at steady-state (Fig.
-3E).
-This might be tested by characterizing the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\citet{Steward_1998}, see discussion).
+The model predicts that transport to distal compartments is quickened by increasing the steady-state level of cargo in the proximal compartments (Fig. 3E).
+This might be experimentally tested by measuring the convergence time of a retrogradely transported molecule that aggregates at recently activated synapses, such as \textit{Arc} mRNA (\citet{Steward_1998}, see discussion).
 To illustrate this in the model CA1 cell, we characterized the time course of transport to the distal apical dendrite (stimulating stratum lacunosum/moleculare), proximal apical dendrite (stimulating stratum radiatum), entire apical dendrite (stimulating both layers), and entire cell (seizure).
@@
 
-So far we have considered how local signals can generate a specific distribution of molecular cargo along a dendrite by modulating the rate of molecular motors. However,
-while certain types of molecular cargo stay on the microtubule network (e.g. mitocondria), many kinds of cargo must detach from the microtubules in order to be used at their final location.
+We have so far considered how a target distribution of cargo can be generated by modulating the local rates of molecular motors.
+However, while certain types of molecular cargo stay on the microtubule network (e.g. mitocondria), many kinds of cargo must detach from the microtubules in order to be used at their final location.
 For example, dendritic mRNAs are transported along microtubules within densely-packed granules, and are released following granule disassembly \citep{Krichevsky_2001,Buxbaum_2014a}.
-In this case, and in others where the cargo is disassembled or sequestered, it is reasonable to model detachment from the microtubule as an irreversible process, followed by an eventual degradation.
-We therefore model the detachment from the microtubule in the mass-action scheme as having a unidirectional rate constant, and include a compartment-specific degradation reaction.
-This results in the following scheme:
+In this case, and in other cases where the cargo is disassembled or sequestered, it is reasonable to model detachment from the microtubule as an irreversible process, followed by an eventual degradation.
+
+This conceptual picture, in which local mechanisms of transport and delivery conspire to determine the expression pattern of cargo, has been called the ``sushi-belt model'' of transport \citep{Doyle_2011}.
+We study this idea formally with the following mass-action scheme:
 \begin{equation}
@@
 As before, a molecule $u$ is transported along a network of microtubules (top row, in equation 6).
-In each compartment, molecules can irreversibly detach from the microtubules in a reaction $u_i \xrightarrow{c_i} u_i^\star$, where $u^\star$ denotes the biochemically active form of $u$, which is assumed to be inactive during transport.
+In each compartment, molecules can irreversibly detach from the microtubules in a reaction $u_i \xrightarrow{c_i} u_i^\star$, where $u^\star$ denotes the biochemically active or released form of cargo.
 The final reaction, $u_i^\star \xrightarrow{d_i} \varnothing$, models degradation in each compartment.
@@
 \includegraphics[width=0.9\columnwidth]{04_sushi_belt.png}
+
 \caption{Multiple strategies for transport in a model including nonuniform microtubular detachment/activation.
 \textbf{(A)} Schematic of microtubular transport model with irreversible detachment in a branched morphology.
-The localized degradation reactions ($u^{\star}_i \xrightarrow{d_i} \varnothing$) is omitted.
-\textbf{(B)} Multiple strategies for producing a desired distribution of activated biomolecules ($\tilde{u}^{\star}$).
+The localized degradation reactions ($u^{\star}_i \xrightarrow{d_i} \varnothing$) are omitted for clarity.
+\textbf{(B)} Multiple strategies for producing a desired distribution of detached cargo ($\tilde{u}^{\star}$).
 When the timescale of detachment/delivery is sufficiently slow, the distribution of cargo on the microtubules approaches a quasi-steady-state (transport step).
@@
 As long as these two steps are appropriately matched (blends of blue), then the desired distribution will be achieved (CA1 cell, right).
-\textbf{(C-E)} Normalized distributions of $u$ (red), $u^\star$ (blue), and $\tilde{u}^\star$ (black) as $t \rightarrow \infty$ for various strategies diagrammed in panel B (see circled red numbers).
-}
+\textbf{(C-E)} Quasi-steady-state distributions of $u$ (red), $u^\star$ (blue), and $\tilde{u}^\star$ (black) for the various strategies diagrammed in panel B (see circled red numbers). }
 \end{center}
@@
 One way to analyze this system is to assume that these three processes --- trafficking, detachment, and degradation --- occur on separate timescales.
-If trafficking is sufficiently faster than detachment ($a,b \gg c$), then $u$ approaches a quasi-steady state distribution defined by our previous analysis (equation 4).
+If trafficking is sufficiently faster than detachment ($a,b \gg c$), then $u$ approaches a quasi-steady state distribution defined by our previous analysis (equation 3).
 We then choose detachment rate constants that transform the microtubular distribution into our desired distribution for $u^\star$:
@@
 Here, $\tilde{u}$ and $\tilde{u}^\star$ respectively denote the quasi-steady state distributions for $u$ and $u^\star$, respectively.
-Due to the degradation reaction, the system no longer approaches a steady-state; however, as long as degradation is sufficiently slow ($c \gg d$) the desired distribution is transiently achieved.
+As long as degradation is sufficiently slow ($c \gg d$) the desired distribution is transiently achieved.
 
-This model has a continuum of strategies for controlling the eventual distribution of molecular cargo (Fig. 4B).
-At one extreme of this continuum (Fig.
-4C), microtubular trafficking rates are constrained such that $\tilde{u}$ exactly matches $\tilde{u}^\star$, and the detachment rate constants are spatially uniform ($c_i =$ constant).
-In this case, Figure 4C shows that the desired spatial distribution is achieved both along the microtubules (red line) and for the detached/activated cargo (blue line).
+The addition of spatially varied detachment rates ($c_i$) produces new strategies for achieving a desired distribution of cargo (Fig. 4B).
+First, the strategy introduced in figure 2 can be reproduced in this expanded model: the transport rates ($a_i$,$b_i$) are chosen according to equation (3) and the detachment rate constants are spatially uniform ($c_i =$ constant, with $c \ll a,b$).
+In this case, the desired spatial distribution is first achieved both along the microtubules (red line, Fig. 4C) and then for the detached/activated cargo (blue line, Fig. 4C).
 
-The other extreme case is where trafficking rates are fixed along the microtubules, but cargo detaches in response to local signals at a rate proportional ($c_i \propto \tilde{u}^\star_i$).
-Figure 4D shows this strategy.
+A second strategy begins by choosing uniform transport rates ($a_i = b_i$).
+This evenly distributes cargo throughout the dendritic tree.
+The desired distribution is then achieved by locally delivering cargo at a rate proportional to the desired level ($c_i \propto \tilde{u}^\star_i$; Fig 4D).
 Unlike the first solution, this strategy avoids the transport bottlenecks examined in Figure 3, and can achieve target patterns with $\tilde{u}^\star$ equal to zero in certain compartments by setting $c_i = 0$.
 
+We refer to the first strategy (Fig. 4C) as the ``specific'' trafficking model, because cargo is selectively transported to target sites.
+We refer to the second strategy (Fig. 4D) as the ``uniform'' trafficking model, because cargo is uniformly distributed throughout the dendrite.
+These two strategies represent extremes on a spectrum of possible models (Fig. 4B).
 Figure 4E shows the behavior of an intermediate model, whose parameters are a linear interpolation between the extreme strategies shown in Figure 4C and 4D.
-Thus, effective trafficking systems can be achieved by a spectrum of strategies, which may be suited to different situations and purposes (see Discussion).
+Thus, effective trafficking systems can be described as a spectrum of strategies that may be suited to different situations and purposes (see Discussion).
 
@@
 
-So far we have considered models that distribute cargo to high precision across a dendritic tree and found that high precision can be achieved when detachment is sufficiently slow relative to trafficking.
+We have demonstrated possible strategies for neurons to achieve precise and flexible transport of cargo by assuming that cargo detachment is sufficiently slow relative to trafficking.
 However, biological neurons are unlikely to require perfect matching between demand and distribution of cargo and may therefore tolerate loss of precision in order to speed up delivery globally.
@@
 \textbf{(A)} Delivery of cargo to the distal apical zone with slow \textit{(left)} and fast detachment rates \textit{(right)}.
-The steady-state cargo distribution does not match the stimulated pattern when detachment is fast.
+The achieved pattern does not match the target distribution when detachment is fast, since some cargo is erroneously delivered to proximal sites.
 \textbf{(B)} Tradeoff curves between non-specificity and convergence rate for two trafficking strategies (blue line, see Fig 4D; red line, see Fig 4C).
-\textbf{(C-D)} Same as \textbf{(A-B)} but for cargo delivery to the entire apical tuft.
+\textbf{(C-D)} Same as \textbf{(A-B)} but for intended cargo delivery to the entire apical tuft.
 }
@@
 We refer to this as a ``non-specific'' delivery of cargo, since cargo is not selectively delivered to the stimulated sites.
-Thus, although speeding up detachment relative to transport improves the overall rate at which cargoes are delivered to synapses, but this comes at the cost of decreased accuracy of delivery.
-\hl{For this stimulation pattern, non-specificity might induce on-the-path synaptic plasticity; a possibility that has some experimental evidence} \citep{Han_2013}.
+Thus, speeding up detachment relative to transport improves the overall rate at which cargoes are delivered to synapses, but this comes at the cost of decreased accuracy of delivery.
+%For this stimulation pattern, non-specificity might induce on-the-path synaptic plasticity; a possibility that has some experimental evidence \citep{Han_2013}.
 
@@
 Importantly, this tradeoff exists for both trafficking strategies we examined in figure 4 --- the selective transport strategy (see Fig 4D) and uniform transport strategy (see Fig. 4C).
-The uniform trafficking strategy (Fig. 5B, blue line) outperforms the specific trafficking strategy (Fig. 5B, red line) since the latter suffers from bottleneck in the proximal apical zone.
+For this stimulation pattern, the uniform trafficking strategy (Fig.
+5B, blue line) outperforms the specific trafficking strategy (Fig.
+5B, red line) since the latter suffers from bottleneck in the proximal apical zone.
 
@@
 This is due to the lack of a bottleneck, and the fact that the uniform trafficking strategy initially sends cargo to the basal dendrites where it is not released.
+
 Together, these results show that an increase in the efficiency of synaptic cargo delivery comes at the cost of loss of specificity and that the final destination of mis-trafficked cargo depends on the pattern of stimulation.
@@
 
-We examined this possibility in a simpler model --- an unbranched cable --- so that we could develop simple heuristics that precisely achieve a desired distribution of cargo while minimizing the convergence time.
-In the reduced model, cargo begins on the left end of the cable and is transported to a number of synaptic sites, each of which is modeled as a double-exponential curve.
+We examined this possibility in a reduced model --- an unbranched cable --- so that we could develop simple heuristics that precisely achieve a desired distribution of cargo while minimizing the convergence time.
+In this model, cargo begins on the left end of the cable and is transported to a number of synaptic delivery sites, each of which is modeled as a double-exponential curve.
+We also restricted ourselves to investigating the uniform trafficking strategy (Fig. 4D); a similar analysis could in principle be done for the specific trafficking strategy.
 
@@
 \includegraphics[width=0.9\columnwidth]{06_heterosynaptic_cable.png}
-\caption{Producing speed and specificity for particular stimulation patterns does not extend to other patterns. Cargo begins on the left end and is transported to the right.
-\textbf{(A-C)} Steady-state cargo profiles (red) for three stimulation patterns (black arrows) along an unbranched cable.
-The dotted black line corresponds to the `target' steady-state level at each synapse.
+\caption{Tuning the model for speed and specificity is sensitive to the target distribution of cargo.
+\textbf{(A-C)} Cargo begins on the left end of an unbranched cable, and is ideally distributed equally amongst a number recently stimulated synaptic sites (black arrows).
+Steady-state cargo profiles (red) for three stimulation patterns (black arrows) along an unbranched cable.
+The dotted black line corresponds to the `target' steady-state level at each delivery site.
 \textbf{(A)} When the timescale of detachment is sufficiently slow, cargo can be evenly distributed to the synapses regardless of their number and position.
@@
 6B).
-This bias is qualitatively exponential.
 
@@
 Specifically, we increased the anterograde rate constants ($a_i$) and decreased the retrograde rate constants ($b_i$) by a decreasing linear function of position so that $a_{N-1} = b_{N-1}$ at the right side of the cable.
-On the left end of the cable, we set $a_1 = 0.5 + \beta$ and $b_1 = 0.5 - \beta$, where $\beta$ is the parameter controlling anterograde bias
-Intuitively, this pushes cargo past the proximal synaptic sites more quickly, canceling out the exponential delivery bias induced by fast detachment.
+On the left end of the cable, we set $a_1 = 0.5 + \beta$ and $b_1 = 0.5 - \beta$, where $\beta$ is the parameter controlling anterograde bias.
+Intuitively, the profile of the proximal delivery bias is roughly exponential (Fig.
+6B, top pattern), and therefore the anterograde rates need to be tuned more aggressively near the soma (where the bias is most pronounced), and more gently tuned as the distance to the soma increases.
 
-However, this tuned transport model does not precisely deliver cargo for other stimulation patterns.
-When the number of synapses on the cable is decreased, a distal delivery bias is observed because too little cargo is released on the proximal portion of the cable (middle row, Fig. 6C).
-Even when the number of synapses is held constant, changing the position of the synapses can disrupt equal distribution of cargo.
-This is shown in the bottom row of figure 6C, where a distal bias again develops when the majority of activated synapses are positioned proximally.
+However, this tuned model does not precisely deliver cargo for other stimulation patterns.
+For example, when the number of synapses on the cable is decreased, a distal delivery bias develops because too little cargo is released on the proximal portion of the cable (middle row, Fig. 6C).
+Even when the number of synapses is held constant, changing the position of the synapses can disrupt equitable delivery of cargo to synapses.
+This is shown in the bottom row of figure 6C, where a distal bias again develops after the majority of activated synapses are positioned proximally.
 Thus, within the simple framework we've developed, the delivery of cargo can be tuned to achieve both precision and speed for a specified target distribution.
@@
 As before, a hard tradeoff between specifity and delivery speed exists for the untuned model (blue line in Fig. 6D, same transport rate constants as Fig. 6A and 6B).
-As the transport rate constants are tuned to increase anterograde movement, the optimal points along the tradeoff curve move to the left, representing faster transport times.
-However, the tradeoff curves also become nonmonotonic: the error (non-specificity) initially decreases as the detachment rate decreases, but begins to increase after a certain well-matched point.
+As the anterograde transport bias is introduced and increased, the optimal points along the tradeoff curve move to the left, representing faster transport times.
+The tradeoff curves also become nonmonotonic: the error (non-specificity) initially decreases as the detachment rate decreases, but begins to increase after a certain well-matched point.
 Points on the descending left branch of the curve represent cargo distributions with proximal bias (detachment is too fast); points on the ascending right branch correspond to distal bias (detachment is too slow).
@@
 6F).
-There is substantial variability in the tradeoff curves in both cases, but particularly when randomizing the number of synaptic inputs.
+There is substantial variability in the tradeoff curves in both cases, but particularly when randomizing the number of synaptic inputs (Fig.
+6F).
 Notably, the untuned transport model (blue curves) always converge to zero error as the detachment rate decreases.
-Thus, for this model, it appears that the only way to achieve very precise and flexible transport is to have a slow detachment rate.
+Thus, for this model, it appears that the only way to achieve very precise, reliable and flexible transport is to have a slow detachment rate.
 
@@
 
-A microscope image of a typical neuronal dendritic tree hints at the complex logistical task that the neuron must solve to maintain synapses and alter them, as appropriate, during development and learning.
+A microscope image of a typical dendritic tree hints at the complex logistical task that the neuron must solve to maintain synapses and alter them during development and learning.
 Synapses, such as the extensively-studied excitatory synapses of the mammalian nervous system, comprise hundreds of different proteins, including receptors, structural and anchoring proteins, and cytosolic signaling enzymes \citep{Liu2014,Lassek2015}.
@@
 
-A large and diverse corpus of research speaks to this question, and many reviews have crystallized, in words, a two-step model in which molecular cargo first samples the dendritic arbor by a noisy walk, before its eventual release or capture \citep{Welte2004,Doyle_2011,Buxbaum_2014b,Buxbaum2015}.
-Both stages of transport are thought to be influenced by localized signaling pathways, rather than being pre-determined by a precise molecular address tagged in the soma.
+A large experimental literature addresses the molecular mechanisms underlying this question, and several reviews have outlined a two-step model in which molecular cargo first samples the dendritic arbor by a noisy walk, before its eventual release or capture \citep{Welte2004,Buxbaum_2014b,Buxbaum2015}.
+Both stages of transport are thought to be influenced by localized signaling pathways, rather than being pre-determined by a precise molecular address.
 The signaling pathways affecting transport require further characterization and discovery; candidate second-messengers include calcium \citep{Wang_2009}, ADP \citep{Mironov_2007}, and microtubule-associated proteins \citep{Soundararajan_2014}.
 
-We aimed to examine the validity and biological consequences of these conceptual models in computational and theoretical detail, while remaining agnostic to biophysical parameters that require further study.
+Our goal was to formulate conceptual accounts of activity-dependent transport as mathematical models to test their feasibility and examine relationships between the speed, flexibility and specificity of cargo delivery.
+%We aimed to examine the validity and biological consequences of these conceptual models in computational and theoretical detail, while remaining agnostic to biophysical parameters that require further study.
 A primary question we asked was whether a transport system based on purely local rules was feasible, or whether a complex global addressing system was required.
-One might na\"ively expect that elaborately branched dendritic morphologies obfuscate the relationship between local mechanisms and the global distribution of molecular cargo.
-However, we showed that local rules can produce arbitrarily precise and flexible cargo delivery provided that the release of cargo occurs on a slow enough timescale.
-Intuitively, this requirement means that the cargo have time to sample the dendritic tree for potential delivery sites \citep{Welte2004}.
+%One might na\"ively expect that elaborately branched dendritic morphologies obfuscate the relationship between local mechanisms and the global distribution of molecular cargo. However, 
+We showed that local rules can produce arbitrarily precise and flexible cargo delivery provided that the release of cargo occurs on a slow enough timescale.
+Intuitively, this requirement means that the cargo has time to sample the dendritic tree for potential delivery sites \citep{Welte2004}.
+Similar decentralized strategies are utilized by other biological systems, such as ant colonies, which converge onto a common path during exploration based on localized trail-laying and -following decisions made by a distributed population of agents \citep{Deneubourg_1990}.
+Such self-organizing systems often enjoy a number of advantageous properties -- including scalability, flexibility, and fault-tolerance -- and are therefore a current topic of substantial interest to engineers \citep{Werfel2014,Rubenstein2014}.
 
-Importantly, the spatial sampling of cargo need not occur in a uniform or unbiased manner.
-We showed that the same distribution of cargo could be achieved by (a) nonuniform microtubular transport followed by uniform release, (b) from uniform transport followed by nonuniform release, or (c) a combination of these strategies (Fig.
+Cargo does not need to search the dendritic tree for target sites in a uniform or unbiased manner.
+We showed that the same distribution of cargo could be achieved by (a) specific microtubular transport followed by uniform release, (b) from uniform transport followed by specific release, or (c) a combination of these strategies (Fig.
 4).
-Biologists should consider that dendritic transport may be better understood as a family of strategies, rather than a single mechanism or procedure.
+Experimental findings are variable across systems and span these possibilities.
 For example, \cite{Kim_2015} identified three mRNAs that were uniformly distributed throughout cultured \textit{Aplysia} sensory neurons, but were targeted to synapses at the level of protein expression by localized translation.
-In contrast, the nonuniform expression of \textit{Arc} mRNA is closely matched to the pattern of Arc protein \citep{Farris_2014, Steward_2015}.
-Even the same molecular cargo can show diverse movement statistics in single-particle tracking experiments \citep{Dynes_2007} \hl{Others?}.
+In contrast, the nonuniform expression of \textit{Arc} mRNA is closely matched to the pattern of Arc protein in granule cells of the dentate gyrus \citep{Steward_1998,Farris_2014, Steward_2015}.
+Even the same type of molecular cargo can show diverse movement statistics in single-particle tracking experiments \citep{Dynes_2007}.
 
-Different transport strategies might be tailored for different constraints or purposes.
-One experimentally testable prediction of the model is that bottlenecks can arise when cargo is transported nonuniformly; specifically when distal regions require high levels of cargo, while proximal regions require low levels (Fig.
+Given that different strategies are feasible and appear to be represented in biological neurons, it is important to know the pros and cons of a given strategy, and the general tradeoffs that exist in a transport mechanism that uses local signals.
+One experimentally testable phenomenon seen in the model is the emergence of bottlenecks that arise when cargo is trafficked nonuniformly; for example, when distal regions require high levels of cargo and proximal regions require low levels (Fig.
 3).
-Uniformly distributing cargo and relying on local capture circumvents this problem, leading to faster convergence for certain target distributions of cargo.
-An additional consideration, not examined in detail here, is whether the distribution of cargo needs to be stable over long time periods or be dynamic and responsive to changes in synaptic input.
-We also focused our analysis on the transport of transiently expressed cargo (e.g.
+Other forms of trafficking bottlenecks can be experimentally induced by expressing kinesin at high densities to induce molecular crowding \citep{leduc2012molecular}.
+An important open question is whether trafficking bottlenecks and crowding events occur as part of normal physiology, and whether severe activity-induced bottlenecks might underlie pathophysiological states.
+%Uniformly distributing cargo and relying on local capture can circumvent activity-induced bottlenecks, leading to faster convergence for certain target distributions of cargo.
+%An additional consideration, not examined in detail here, is whether the distribution of cargo needs to be stable over long time periods or be dynamic and responsive to changes in synaptic input.
+%We also focused our analysis on the transport of transiently expressed cargo (e.g.
 factors produced in response to high synaptic input), rather than cargo that is constitutively expressed and, in some cases, differentially captured or synthesized across the dendritic tree \hl{(CITE)}.
-However, much of our analysis would extend to this case.
 
-The slow delivery/capture of cargo can produce a well-behaved and predictable transport system that can be flexibly tuned by simple local mechanisms and is not sensitive to the complex geometry of the neuron.
-Mathematically, this regime occurs when the system contains two separated timescales, and the distribution of cargo along the microtubules approaches a quasi-steady-state.
-However, because the transport of certain cargoes is time-sensitive \citep{Frey_1997,Frey_1998}, we asked whether the model could maintain precise delivery while relaxing the restriction of slow detachment.
-We found that increasing the rate of detachment produces a proximal bias in the delivery of cargo; this behavior, while intuitive at a high level, is complex and difficult to analytically characterize in complex morphologies.
-Thus, the family of models based on quasi-steady-state approximation predicts a tradeoff between the speed of cargo delivery and the specificity of transport.
+We showed that having sufficiently slow capture of cargo can produce a well-behaved transport system that matches demand using local mechanisms and is not sensitive to the complex geometry of the neuron.
+Mathematically, this regime occurs when the system contains two separated timescales, so that the distribution of cargo along the microtubules approaches a quasi-steady-state that matches the long-term average of local demand.
+However, because the transport of certain cargo is time-sensitive \citep{Frey_1997,Frey_1998}, we asked whether the model could maintain precise delivery while relaxing the restriction of slow detachment.
+We found that increasing the rate of detachment produces a proximal bias in the delivery of cargo, leading to a mismatch between supply and demand across a population of synapses.
+%; this behavior, while intuitive at a high level, is complex and difficult to analytically characterize in complex morphologies.
+Thus, models with separated timescales between transport and detachment face a tradeoff between the speed and specificity of cargo delivery.
 
 We then asked whether a different family of models might circumvent this tradeoff by globally tuning the anterograde and retrograde movement rates.
-Inspired by studies showing that a directional bias in transport can be induced by changing the complement of motor proteins \citep{Kanai2004,Amrute2012}, and that such a change might be induced at the soma in response to synaptic activity \citep{Puthanveettil_2008}, we increased the anterograde transport rates in a simple model to precisely overcome the proximal bias in cargo delivery, and therefore provide both fast and precise transport for a particular target distribution of cargo (Fig.
+Studies show that a directional bias in transport can be induced by changing the complement of motor proteins \citep{Kanai2004,Amrute2012}, and that such a change might be induced at the soma in response to synaptic activity \citep{Puthanveettil_2008}.
+We showed, in a simple unbranched model, that increasing the anterograde transport rate can precisely overcome the proximal bias in cargo delivery, and therefore provide both fast and precise transport for a particular target distribution of cargo (Fig.
 6).
 
-There are three important facts to emphasize about this globally tuned solution.
-First, we achieved precise delivery when the anterograde rate constants were tuned non-uniformly over the cable; specifically, we used a linearly decreasing profile (see \textit{Methods}).
-Simply changing the composition of motor proteins \citep{Amrute2012} may be insufficient to induce a spatial profile in transport bias; non-uniform modulation of the microtubule network or expression of microtubule-associated proteins provide potential mechanisms \citep{Kwan2008,Soundararajan_2014}.
-While these biophysical details remain speculative, single-particle tracking studies could empirically test the existence of spatial gradients in anterograde movement bias.
+However, tuning trafficking bias to counterbalance leakage does not provide a completely general solution to the speed/specificity tradeoff in a biologically realistic situation.
+First, anterograde rate constants need to be tuned non-uniformly over the cable.
+In the cases we studied, we used a linearly decreasing profile (see \textit{Methods}).
+It is unclear whether real neurons are capable of globally tuning their trafficking rates in a non-uniform manner.
+Simply changing the composition of motor proteins \citep{Amrute2012} is unlikely induce a spatial profile in transport bias.
+On the other hand, non-uniform modulation of the microtubule network or expression of microtubule-associated proteins provide potential mechanisms \citep{Kwan2008,Soundararajan_2014}.
+It would therefore be intriguing to experimentally test the existence of spatial gradients in anterograde movement bias, for example, using single-particle tracking in living neurons.
 
-Secondly, it should be emphasized that the linear, decreasing gradient in anterograde bias used in figure 6 is not a general prediction for all neuronal morphologies or detachment/capture profiles.
-Introducing an anterograde bias can cause the accumulation of cargo at the tips of short branches, proximal to the soma (data not shown).
-While the optimal re-tuning of transport rate constants is be morphology-dependent, the qualitative prediction that anterograde bias should decrease as a function of distance to the soma is likely general.
-Intuitively, the anterograde bias should be low near the tips of the dendritic branches to prevent the accumulation of cargo.
+Secondly, tuning transport bias can provide fast and rapid cargo delivery for a specific density and arrangement of synapses along a dendrite, but we showed that this tuned solution will not be optimal for different densities and spatial distributions of synapses, as seen in Figure 6.
+The overall morphology of the neurites may also need to be taken into account, as introducing an anterograde bias can cause the accumulation of cargo at the tips of short branches, proximal to the soma (data not shown).
 However, other mechanisms, not modeled in this study, might prevent this accumulation \citep{Soundararajan_2014}.
-
-Finally, and perhaps most importantly, the optimal re-tuning of anterograde transport bias depends on the number and pattern of delivery sites (see Fig.
-6).
-If neurons are able to consistently circumvent the tradeoff between delivery speed and precision, then the model predicts that they must globally re-tune transport rates in a pattern-specific manner.
-
-\hl{Need a nice final paragraph to tie it all together}
+Certain neuron types in specific brain regions may nonetheless have morphology and synaptic connectivity that is sufficiently stereotyped to permit some degree of tuning.
+In such cases the qualitative prediction that anterograde bias should decrease as a function of distance to the soma can be tested.
+Such tuning, while providing improved efficiency in trafficking intracellular cargo, would also constitute a site of vulnerability to perturbations that alter synapse density and reflect an additional constraint on the possibilities for wiring and re-wiring neural circuits.
 
@@
 Let $x_n$ denote the position of a particle along a 1-dimensional cable at timestep $n$.
-Let $v_n$ denote the velocity of the particle at timestep $n$; for simplicity, we assume the velocity can take on three discrete values, $v_n = \{-1,0,1\}$, corresponding to a discrete retrograde movement, pause, or anterograde movement.
+Let $v_n$ denote the velocity of the particle at timestep $n$; for simplicity, we assume the velocity can take on three discrete values, $v_n = \{-1,0,1\}$, corresponding to a retrograde movement, pause, or anterograde movement.
 As a result, $x_n$ is constrained to take on integer values.
@@
 We introduce a parameter $k \in [0,1]$ to linearly interpolate between this extreme case and the memoryless model.
-The rest of the panels in the figure show individual runs, 5000 molecule simulations, and mass action approximations for $k=0.5$.
+The bottom plots of figure 1B, 1D were simulated with $k=0.5$; in the bottom plot of figure 1F, a mass-action model was fit to these simulations.
 
-\subsection*{Model of bulk/mass-action transport}
-Transport in an unbranched cable (equation 1) leads to the following system of differential equations:
+\subsection*{Relationship of single-particle transport to the mass-action model}
+
+The mass-action model (equation 1, in the \textit{Results}) simulates the bulk movement of cargo $u$ across discrete compartments.
+The rate of cargo transfer is modeled as elementary chemical reactions \citep{Keener_1998}.
+For an unbranched cable, the change in cargo in compartment $i$ is given by:
+\begin{equation}
+\dot{u}_i = a u_{i-1} + b u_{i+1} - (a+b)u_i
+\end{equation}
+For now, we assume that the anterograde and retrograde trafficking rate constants ($a$ and $b$, respectively) are spatially uniform.
+
+The mass-action model approximates the drift-diffusion partial differential equation (Fig.
+1E) by discretizing $u$ into spatial compartments.
+This can be seen by Taylor expanding around some position $u(x)$:
 $$
-\begin{array}{lcl}
-\dot{u}_1 & = & -a_1 u_1 + b_1 u_2 \\
-\dot{u}_2 & = & a_1 u_1 - (a_2+b_1) u_2 + b_2 u_3 \\
-~ & \vdots & ~ \\
-\dot{u}_i & = & a_{i-1} u_{i-1} - (a_i+b_{i-1}) u_i + b_i u_{i+1} \\
-~ & \vdots & ~ \\
-\dot{u}_N & = & a_{N-1} u_{N-1} - b_{N-1} u_N 
-\end{array}
+\begin{align}
+\dot{u}(x) &
+\approx a\left[u(x) - \Delta \frac{\partial u}{\partial x} + \frac{\Delta^2}{2} \frac{\partial^2 u}{\partial x^2} \right] + b\left[u(x) + \Delta \frac{\partial u}{\partial x} + \frac{\Delta^2}{2} \frac{\partial^2 u}{\partial x^2} \right] - (a+b)~u(x) \\
+ & = a\left[- \Delta \frac{\partial u}{\partial x} + \frac{\Delta^2}{2} \frac{\partial^2 u}{\partial x^2} \right] + b\left[\Delta \frac{\partial u}{\partial x} + \frac{\Delta^2}{2} \frac{\partial^2 u}{\partial x^2} \right]
+\end{align}
 $$
-Similar systems result from branched mass-action models.
-The steady-state ratio of cargo in two neighboring compartments equals the ratio of transport rate constants (equation 2).
-This can be immediately verified at either end of the cable:
+where $\Delta$ is the compartment size. In the limit $\Delta \rightarrow 0$, we arrive precisely at the drift-diffusion equation.
 $$
-\dot{u}_1 = 0 ~\Rightarrow~ -a_{1} u_{1} + b_{1} u_2 = 0 ~\Rightarrow~ \frac{u_1}{u_2} \Bigg |_{ss} = \frac{b_1}{a_1}
+\dot{u}(x) = \frac{\partial u}{\partial t} = \underbrace{(b-a)}_{\text{drift coefficient}} \frac{\partial u}{\partial x} + \underbrace{\left(\frac{a+b}{2}\right)}_{\text{diffusion coefficient}} \frac{\partial^2 u}{\partial x^2}
+$$
+When all cargo starts in one location (i.e.
+the initial condition is a delta function), then the distribution after some elapsed time will be a Gaussian function.
+The mean of this Gaussian function changes in direct proportion to the drift coefficient over time, while the variance is inversely proportional to the diffusion coefficient \hl{(CITE?)}.
+
+How does this equation relate to the model of single-particle transport (Fig.
+1A-B)?
+For a memoryless biased random walk, the expected position of a particle after $n$ time steps is $E[x_n] = n(p_+ - p_-)$ and the variance in position after $n$ steps is $n \left( p_+ + p_- - (p_+ - p_-)^2 \right)$.
+For large numbers of independently moving particles (i.e.
+assuming \textit{ergodicity}), the ensemble of cargo will approach a Gaussian distribution by the Central Limit Theorem.
+This means that the mean and variance calculations for a single particle can be directly related to the ensemble statistics outlined in the previous paragraph.
+We find:
+$$
+a = \frac{2p_+ - (p_+ - p_-)^2}{2}
+$$
+$$
+b = \frac{2p_- - (p_+ - p_-)^2}{2}
+$$
+
+The above analysis changes slightly when the single-particle trajectories contain long, unidirectional runs.
+The expected position for any particle is the same $E[x_n] = n(p_+ - p_-)$; the variance, in contrast, increases as run lengths increase.
+However, the mass-action model can often provide a good fit in this regime with appropriately re-fit parameters (see Fig.
+1F).
+As long as the single-particles have stochastic and identically distributed behavior, the ensemble will be well-described by a normal distribution by the central limit theorem.
+This only breaks down in the limit of very long unidirectional runs, as the system is no longer stochastic.
+
+\subsection*{Steady-state analysis of the mass-action model}
+
+Many of our results take advantage of the fact that the steady-state ratio of cargo in two neighboring compartments equals the ratio of trafficking rate constants (equation 3).
+We prove this result for a cable with non-uniform anterograde and retrograde rate constants.
+Examining the left end of the cable at steady-state ($\dot{u}_i = 0$), we immediately verify our result:
+$$
+-a_{1} u_{1} + b_{1} u_2 = 0 ~\Rightarrow~ \frac{u_1}{u_2} \Bigg |_{ss} = \frac{b_1}{a_1}
 $$
 Successively applying the same logic down the cable confirms the condition in equation 2 holds globally.
-A similar procedure (starting at the tips and moving in) can be applied to branched morphologies to prove the more general condition (equation 4).
+A similar procedure (starting at the tips and moving in) can be applied to branched morphologies to prove the more general condition.
 
@@
 The desired steady-state distribution, $\mathbf{\tilde{u}}$, is an eigenvector that spans the nullspace of $A$.
-It is simple to show that all other eigenvalues $A$ are negative using the Gershgorin circle theorem; thus, the fixed point described by equations 2 and 4 is stable.
+It is simple to show that all other eigenvalues $A$ are negative using the Gershgorin circle theorem; thus, the fixed point described by equation 3 is stable.
 The convergence rate is determined by the non-zero eigenvalue with smallest magnitude of $A$.
@@
 
-\subsection*{Stochastic Interpretation of Mass-Action Model}
+\subsection*{Stochastic interpretation of the mass-action model}
 
 The mass-action model described in figure 2 is a deterministic dynamical system.
-However, this determinism only holds in the limit of having a very large number of transported particles.
+However, this determinism only holds in the limit of having a large number of transported particles.
 Cargoes with small copy numbers (e.g.
@@
 
-\subsection*{Detachment and Degradation Reactions and Quasi-Steady-State Approximation}
+\subsection*{Incorporating detachment and degradation into the mass-action model}
 
@@
 $$
+
 Here, $N$ is the number of compartments in the model.
-Setting $F=1$ results in the simulation in figure 4C, while setting $F=0$ results in the simulation in figure 4D.
+Setting $F=1$ results in the simulation in the ``specific'' trafficking model (Fig.
+4C), while setting $F=0$ results in the ``uniform'' trafficking model (Fig.
+4D).
 An interpolated strategy is shown in figure 4E ($F=0.3$).
+
+\subsection*{Globally tuning transport rates to circumvent the speed-specificity tradeoff}
+
+We investigated the ``uniform'' trafficking model with fast detachment rates in an unbranched cable with equally spaced synapses and $N = 100$ compartments.
+Multiplicatively increasing the detachment rates across the cable produced a proximal bias in cargo delivery which could be corrected by setting the anterograde and retrograde trafficking rates to be:
+$$
+a_i = 0.5 + \beta \cdot \frac{N-1-i}{N-2}
+$$
+$$
+b_i = 0.5 - \beta \cdot \frac{N-1-i}{N-2}
+$$
+where $i = \{1,2,...N-1\}$ indexes the trafficking rates from the soma ($i=1$) to the other end of the cable ($i=N-1$).
+Faster detachment rates require larger values for the parameter $\beta$; note that $\beta < 0.5$ is a constraint to prevent $b_i$ from becoming negative.
+This heuristic qualitatively improved, but did not precisely correct for, fast detachment rates in the ``specific'' trafficking model (data not shown).
 
